### 2017-04-11 BOS/BOS.tex
First Document

\documentclass{article}
\usepackage{geometry}
\usepackage{standalone}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{siunitx}
\usetikzlibrary{patterns,snakes}

\graphicspath{{./Figures/}}

\begin{document}

\section{Ray Tracing}

\subsection{Derivation from Fermat's Principle}
Fermat's principle or the principle of least time states that the path that a ray of light takes between two points minimizes the time it takes to traverse this path. The time needed to traverse between two points is
\begin{equation}
	T = \int \! \, \mathrm{d}t = \int \! \frac{c}{c} \frac{d s / d t}{d s / d t} \, \mathrm{d}t = \frac{1}{c} \int \! \frac{c}{v} \, \mathrm{d}s = \frac{1}{c} \int \! n \, \mathrm{d}s,
	\end{equation}
where $c$ is the speed of light in a vacuum, $s$ the traversed distance, $v = d s / d t$ the speed of light in a medium and $n = c / v$ the refractive index. According to Fermat's principle the first variation of this integral must vanish,
\begin{equation}
	\delta \int \! n \, \mathrm{d} s = 0.
\end{equation}

\vspace{1cm}
To be completed 
\vspace{1cm}

\subsection{Application to the Water Tank}
Figure \ref{fig:schviepalira} shows a schematic view of a path of a light ray. The intensity of light measured at a pixel on the ccd originates from a location on the screen. We are going to construct the path of the light ray from the ccd to the screen.

\begin{figure}[hpbt]
	\includestandalone{schematicsetup}
	\caption{A schematic view of a path of a light ray (not to scale). The numbers indicate the planes through which the light ray propagates: 0, the ccd sensor inside the camera; 1, the camera lens; 2, the start of the first glass plate; 3, the end of the first glass plate; 4, the start of the second glass plate; 5, the end of the second glass plate; 6, the screen from which the light rays originate.}	
	\label{fig:schviepalira}
\end{figure}

For a given ccd sensor, we know the physical size corresponding to a pixel. When the location of the optical axis of a camera system is know, we can determine the distance to the optical axis of a pixel: $x_0$. The focal length $f$ is fixed for a given camera lens. Assuming the camera system acts as an ideal pinhole camera, the angle with which the light ray entered lens is
\begin{equation}
	\tan \phi_x = \frac{x_0}{f}.
\end{equation}
The light ray exits the camera with a position $x_1 = 0$ and an angle $\phi_x$. The index of refraction of air $n_0$ is constant. The light ray hits the first glass plate with a position
\begin{equation}
	x_2 = L_c \tan \phi_x.
\end{equation}
The index of refraction of the glass plate $n_1$ is constant. The angle under which the light ray propagates changes instantaneously, obeying Snell's law
\begin{equation}
	n_0 \sin \phi_x = n_1 \sin \phi_2.
\end{equation}

For a constant index of refraction in the water tank $n_2$ the position $x_6$ is
\begin{equation}
	x_6 (\phi_x, n_2) = (L_c+L_s) \tan \phi_x + 2 L_g \tan \arcsin \frac{n_0}{n_1} \sin \phi_x + L_t \tan \arcsin \frac{n_0}{n_2} \sin \phi_x
\end{equation}
The displacement $\Delta x$ is the difference in position $x_6$ between the constant reference state, $n_2 = n_0$, and the unknown state $n_2$, 
\begin{equation}
	\label{eq:dexcon2}
	\Delta x = x_6 (n_2 = n_0) - x_6 (n_2 = n_2) = L_t \left[ \tan \phi_x - \tan \arcsin \frac{n_0}{n_2} \sin \phi_x\right].
\end{equation}

For a varying index of refraction in the water tank $n_2 = n_2(\underline{x})$, the position $x_6$ is

\vspace{1cm}
To be completed 
\vspace{1cm}

\subsection{Displacements expected from Theory}
Substituting some characteristic values into (\ref{eq:dexcon2}) we obtain the displacements expected from theory. Figure \ref{fig:1} shows the expected displacements for fresh water $n_2 = 1.333$ compared to a reference state of air $n_2 = 1.0$. The water acts as a magnification glass: all the displacements are away from the optical axis, located in the middle of each figure.

Figure \ref{fig:2} shows the expected displacements for water with a maximum of salt added $n_2 = 1.4$. The displacement pattern looks the same as the fresh water pattern. The magnitude of displacement is slightly larger.

Comparing \ref{fig:1} and \ref{fig:2}, which show the minimum and maximum index of refraction obtainable for water with salts, the displacements have the same pattern and their maximum magnitudes are similar: around \SI{7}{\milli\metre} for $n_2 = 1.333$ and around \SI{8}{\milli\metre} for $n_2 = 1.4$.

Figure \ref{fig:3} shows the expected displacement for salt water with $n_2 = 1.4$ compared to a reference state of fresh water $n_2 = 1.333$.

\begin{figure}
\begin{subfigure}[b]{.5\linewidth}
\centering \includegraphics[width=\linewidth]{hordispnmin.png}
\caption{Horizontal Displacements.}\label{fig:1a}
\end{subfigure}%
\begin{subfigure}[b]{.5\linewidth}
\centering\large \includegraphics[width=\linewidth]{verdispnmin.png}
\caption{Vertical Displacements.}\label{fig:1b}
\end{subfigure} \\
\begin{subfigure}[b]{\linewidth}
\centering \includegraphics[width=\linewidth]{magndispnmin.png}
\caption{Magnitude of Displacements.}\label{fig:1c}
\end{subfigure}%
\caption{Displacements expected from theory for $n_2 = 1.333$ and $L_t = \SI{0.2}{m}$.}\label{fig:1}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.5\linewidth}
\centering \includegraphics[width=\linewidth]{hordispnmax.png}
\caption{Horizontal Displacements.}\label{fig:2a}
\end{subfigure}%
\begin{subfigure}[b]{.5\linewidth}
\centering\large \includegraphics[width=\linewidth]{verdispnmax.png}
\caption{Vertical Displacements.}\label{fig:2b}
\end{subfigure} \\
\begin{subfigure}[b]{\linewidth}
\centering \includegraphics[width=\linewidth]{magndispnmax.png}
\caption{Magnitude of Displacements.}\label{fig:2c}
\end{subfigure}%
\caption{Displacements expected from theory for $n_2 = 1.4$ and $L_t = \SI{0.2}{m}$.}\label{fig:2}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{.5\linewidth}
\centering \includegraphics[width=\linewidth]{hordispnmaxrefstatenmin.png}
\caption{Horizontal Displacements.}\label{fig:3a}
\end{subfigure}%
\begin{subfigure}[b]{.5\linewidth}
\centering\large \includegraphics[width=\linewidth]{verdispnmaxrefstatenmin.png}
\caption{Vertical Displacements.}\label{fig:3b}
\end{subfigure} \\
\begin{subfigure}[b]{\linewidth}
\centering \includegraphics[width=\linewidth]{magndispnmaxrefstatenmin.png}
\caption{Magnitude of Displacements.}\label{fig:3c}
\end{subfigure}%
\caption{Displacements expected from theory using fresh water as the reference state for $n_2 = 1.4$ and $L_t = \SI{0.2}{m}$.}\label{fig:3}
\end{figure}

Looking at (\ref{eq:dexcon2}), we see that there are two main uncertainties when determining the index of refraction $n_2$: (1) uncertainty in the displacements $\Delta x$ and (2) uncertainty in the angles $\phi_x$. To get a feeling for these uncertainties, we chose an $n_2$, computed a displacement field using (\ref{eq:dexcon2}), added an uncertainty and computed $n_2$ by inverting (\ref{eq:dexcon2}).

First, we added white noise to the displacement field. Figure \ref{fig:nfromhordispnoise} shows the index of refraction obtained from the horizontal displacements when adding this noise. Around the center line, where both the displacements $\Delta x$ and the angles $\phi_x$ are near zero, the errors are largest. This error band around the center line also exists for the index of refraction obtained from the vertical displacements. There, the error band is horizontal. When combining the horizontal and vertical displacements into a magnitude of displacements the horizontal and vertical error bands disappear, except for where they overlap: near the centerpoint we are left with a region of large errors due noise: both the displacements and the angles are near zero.

Second, we added a shift in the optical axis. Figure \ref{fig:nfrommagndispnoiseshift} shows the index of refraction obtained from a small shift (both horizontal and vertical) in the optical axis. A very recognizable pattern appears: a figure eight. The orientation of the eight is determined by the shift in the optical axis.

\begin{figure}
\centering \includegraphics[width=\linewidth]{nfromhordispnoise.png}
\caption{Index of Refraction determined from Computed Horizontal Displacements with Noise.}
\label{fig:nfromhordispnoise}
\end{figure}

\begin{figure}
\centering \includegraphics[width=\linewidth]{nfrommagndispshift.png}
\caption{Index of Refraction determined from Computed Displacements with a Shift in the Optical Center.}
\label{fig:nfrommagndispnoiseshift}
\end{figure}

Last, we combine white noise with a shift in optical axis, shown in Figure \ref{fig:nfrommagndispnoiseshift} with data obtained in the lab, shown in Figure \ref{fig:nfrommdataexample}. In the lab data, we see the figure eight appearing, indicating an error in the determination of the optical axis.

\begin{figure}
\centering \includegraphics[width=\linewidth]{nfrommagndispnoiseshift.png}
\caption{Index of Refraction determined from Computed Displacements with Noise and a Shift in the Optical Center.}
\label{fig:nfrommagndispnoiseshift}
\end{figure}

\begin{figure}
\centering \includegraphics[width=\linewidth]{nfrommagndata.png}
\caption{Example of Index of Refraction determined Data.}
\label{fig:nfrommdataexample}
\end{figure}

\clearpage
\section{Experimental Set-up}

\subsection{Equipment}

\subsection{Error Sources}

\subsection{Corrections}

\section{Experimental Results}

\subsection{Constant Density, Single Layer Fluids}

\subsection{Constant Density, Multiple Layers Fluids}

\subsection{Stratified Fluids}

\end{document}

### 2017-04-11 BOS/BOS.tex
Error Magnitudes Table

@@
 \usepackage{geometry}
+%\usepackage[table]{xcolor}
+\usepackage{booktabs}
 \usepackage{standalone}
@@
 
+\begin{table}[htbp]
+\caption{Estimated Error Magnitudes for a \SI{100}{\milli\metre} field of view. Copied from MatchID.}
+\label{tab:esterrmagn}
+\begin{tabular}{@{}llr@{}} \toprule
+2D Error	& Estimated Error (pixels)	& Notes \\ \midrule 
+Contrast/Noise & 0.01 & Easiest to determine and minimize. \\
+Interpolant Bias & 0.01 to 0.001 & Depends on noise and interpolant. \\
+Lighting Variation & 0.005 & If using ZNNSD. \\
+Subset size / Shape & linear fit to  &  Depends on underlying \\
+ \hspace{.3cm} function & displacement field & displacement field.  \\
+Optical distortions & 1+ & Depends on lens and distance moved.\\
+ \hspace{.3cm} without corrections	&	& \\
+Image Blur	& 0.001 & If blur is constant for all frames.\\
+Turbulence/Shockwaves & $\sim$ 0.01 to 2+ & Depends on lightning and lab environment. \\
+Out-of-Plane	& $\sim$ 0.5	& Depends on magnification and motion. \\
+Lack of Perpendicularity	& $\sim$ 0.5	& Depends on tilt and motion. \\
+System Resolution	& Small	& Increases subset size.\\
+Aliasing	& $\sim$ 0.005	& Adds noise to the image.\\ \bottomrule
+\end{tabular}
+\end{table}
+
 \subsection{Corrections}

### 2017-04-18 BOS/BOS.tex
Derivation from Fermat's principle added

@@
 \usepackage{siunitx}
+\usepackage{amsmath}
+\usepackage{amssymb}
 \usetikzlibrary{patterns,snakes}
@@
 \subsection{Derivation from Fermat's Principle}
-Fermat's principle or the principle of least time states that the path that a ray of light takes between two points minimizes the time it takes to traverse this path.
-The time needed to traverse between two points is
+Fermat's principle states: \\
+\textit{``The path between two points taken by a ray of light leaves the optical length stationary under variations in a family of nearby paths."} \\
+
+The optical length $\mathcal{A}$ of a path $\underline{r}(s)$ taken by a ray of light passing from point $A$ to point $B$ in three-dimensional space is defined by
 \begin{equation}
-	T = \int \! \, \mathrm{d}t = \int \! \frac{c}{c} \frac{d s / d t}{d s / d t} \, \mathrm{d}t = \frac{1}{c} \int \! \frac{c}{v} \, \mathrm{d}s = \frac{1}{c} \int \! n \, \mathrm{d}s,
+	\mathcal{A} = \int_A^B \! n(\underline{r}(s)) \, \mathrm{d}s,
 \end{equation}
-where $c$ is the speed of light in a vacuum, $s$ the traversed distance, $v = d s / d t$ the speed of light in a medium and $n = c / v$ the refractive index.
-According to Fermat's principle the first variation of this integral must vanish,
+where $n(\underline{r})$ is the index of refraction at the spatial point $\underline{r} \in \mathbb{R}^3$ and $\mathrm{d}s^2 = \mathrm{d}\underline{r}(s) \cdot \mathrm{d}\underline{r}(s)$ is the element of arc length $\mathrm{d}s$ along the ray path $\underline{r}(s)$ through that point.
+
+Applying Fermat's principle to a ray of light between points $A$ and $B$ leaves the optical length stationary under variations in a family of nearby paths $\underline{r}(s,\epsilon)$ depending smoothly on a parameter $\epsilon$.
+The path $\underline{r}(s)$ satisfies
 \begin{equation}
-	\delta \int \! n \, \mathrm{d} s = 0.
+	\label{eq:ferray}
+	\delta \mathcal{A} = 0 \mbox{ with } \delta \mathcal{A} = \delta \int_A^B \!
+n(\underline{r}(s)) \, \mathrm{d}s = \left.\frac{d}{d \epsilon}\right|_{\epsilon=0} \int_A^B \!
+n(\underline{r}(s)) \, \mathrm{d}s,
+\end{equation}
+where the deviations of the ray path $\underline{r}(s,\epsilon)$ are assumed to vanish when $\epsilon=0$, and to leave its endpoints fixed.
+Performing the variational derivative in (\ref{eq:ferray}) yields
+\begin{equation}
+	\begin{aligned}
+		0 &= \delta \int_A^B \! n(\underline{r}(s)) \sqrt{\dot{\underline{r}} \cdot \dot{\underline{r}}} \, \mathrm{d}s \\
+		&= \int_A^B \!
+\left|\dot{\underline{r}}\right| \frac{\partial n}{\partial \underline{r}} \cdot \delta\underline{r} + n(\underline{r}(s)) \frac{\dot{\underline{r}}}{\left|\dot{\underline{r}}\right|} \cdot \delta \dot{ \underline{r}} \, \mathrm{d}s \\
+		&= \int_A^B \!
+\left[ \left|\dot{\underline{r}}\right| \frac{\partial n}{\partial \underline{r}} - \frac{d}{ds} \left(n(\underline{r}(s)) \frac{\dot{\underline{r}}}{\left|\dot{\underline{r}}\right|}\right) \right] \cdot \delta \underline{r} \, \mathrm{d}s,
+	\end{aligned}
+\end{equation}
+where we used integration by parts with respect to $s$ and used the homogeneous end points.
+We choose the arc-length variables $\mathrm{d}s^2 = \mathrm{d}r\cdot\mathrm{d}r$, so that $|\dot{\underline{r}}|=1$ for $\dot{\underline{r}} = \mathrm{d}\underline{r}/\mathrm{d}s$.
+The eikonal equation for the ray path $\underline{r}$ emerges
+\begin{equation}
+	\label{eq:axialrayequation}
+	\frac{\partial n}{\partial \underline{r}} = \frac{d}{ds} \left(n(\underline{r}) \frac{\mathrm{d}\underline{r}}{\mathrm{d} s} \right).
 \end{equation}
 
-\vspace{1cm}
-To be completed 
-\vspace{1cm}
+Most optical instruments are designed to posses a line of sight (or primary direction of propagation of light) called the optical axis.
+Choosing a Cartesian coordinate system such that the $z$-axis coincides with this optical axis, expresses the arc-length $\mathrm{d}s$ in terms of the increment along the optical axis, $\mathrm{d}z$, as
+\begin{align}
+	\mathrm{d}s &= \sqrt{(dx)^2 + (dy)^2 + (dz)^2} \\
+	&= \sqrt{1+\dot{x}^2 +\dot{y}^2} d z = \frac{1}{\gamma} d z,
+\end{align}
+where $\dot{x} = d x / dz$ and $\dot{y} = dy/dz$ and 
+\begin{equation}
+	\label{eq:gamma}
+	\gamma = \frac{d z}{d s} = \frac{1}{\sqrt{1+\dot{x}^2+\dot{y}^2}} = \cos \theta\leq 1,
+\end{equation}
+where $\theta$ is the angle the ray makes with the $z$-axis.
+The position of a ray at a fixed value of $z$ is denoted by $[x,y]^T$.
+In our Cartesian coordinate system, $\underline{r}=\underline{x}(z) = [x(z),y(z),z]^T$.
+Using (\ref{eq:gamma}) in (\ref{eq:axialrayequation}) yields
+\begin{equation}
+	\gamma \frac{d}{dz} \left(n(\underline{x}) \gamma \frac{d \underline{x}}{d z} \right)  = \frac{\partial n(\underline{x})}{\partial \underline{x}}.
+\end{equation}
+This yields three equations, one for each coordinate direction,
+\begin{equation}
+	\label{eq:axraycoord}
+	\begin{aligned}
+		\ddot{x}  &= \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial x} - \dot{x} \frac{\partial n}{\partial z} \right), \\
+		\ddot{y} &= \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial y} - \dot{y} \frac{\partial n}{\partial z} \right), \\
+		\frac{\partial n}{\partial z} &= \gamma \frac{d}{dz}\left(n  \gamma\right).
+	\end{aligned}
+\end{equation}	
+Suppose the index of refraction $n$ is independent of the $z$-coordinate. (\ref{eq:axraycoord}) reduce to
+\begin{equation}
+	\label{eq:axraycoord2}
+		\ddot{x}  = \frac{1}{\gamma^2} \frac{1}{n} \frac{\partial n}{\partial x}, \qquad
+		\ddot{y} = \frac{1}{\gamma^2} \frac{1}{n} \frac{\partial n}{\partial y}, \qquad n\gamma = \mbox{ constant}.
+\end{equation}
+The constant $n\gamma$ appears as an invariant of the ray path.
+
+\bigskip
+We solve (\ref{eq:axraycoord2}) for three cases:
+\begin{enumerate}
+\item $n=$ constant,
+\item $\dot{x} \ll 1$ and $\dot{y} \ll 1$, $n=n(x,y)$,
+\item $n=n(x,y)$.
+\end{enumerate}
+\bigskip
+
+1. $n=$ constant: (\ref{eq:axraycoord2}) reduces to
+\begin{equation}
+	\ddot{x} = 0, \qquad \ddot{y} = 0, \qquad \gamma = \mbox{ constant},
+\end{equation}
+with solution
+\begin{equation}
+	x = A+Bz, \qquad y=C+Dz, \qquad \cos \theta = \mbox{ constant }
+\end{equation}
+where constants $A,B, C$ and $D$ are determined by initial conditions.
+\bigskip
+
+2. $\dot{x} \ll 1$ and $\dot{y} \ll 1$, $n=n(x,y)$: $\gamma \approx 1$ and (\ref{eq:axraycoord2}) reduces to
+\begin{equation}
+	\ddot{x} = \frac{1}{n} \frac{\partial n}{\partial x}, \qquad
+		\ddot{y} = \frac{1}{n} \frac{\partial n}{\partial y}, \qquad n \approx \mbox{ constant},
+\end{equation}
+with solution
+\begin{equation}
+	x = A + B z + \frac{z^2}{2 n} \frac{\partial n}{\partial x}, \qquad y = C + D z + \frac{z^2}{2 n} \frac{\partial n}{\partial y}, \qquad n \approx \mbox{ constant}, \qquad \cos \theta \approx 1
+\end{equation}
+where constants $A,B, C$ and $D$ are determined by initial conditions.
+\bigskip
+
+3. $n=n(x,y)$: no additional assumptions are made. Dividing the first two equations of (\ref{eq:axraycoord2}) we obtain
+\begin{equation}
+	\frac{\ddot{x}}{\ddot{y}} = \frac{\partial n / \partial x}{\partial n / \partial y}.
+\end{equation}
 

### 2020-02-05 Article/articleBOS.tex
Add files via upload

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}
\usepackage{subcaption}
\usepackage{standalone}
\usepackage{xcolor}
\usepackage{enumitem}
%\setlist{noitemsep}
%\setlist[1]{labelindent=\parindent}
%\setlist[1]{itemsep=0pt,topsep=0pt}
\setlist{nosep}
\usepackage{tikz}
\usetikzlibrary{patterns,snakes}

\usepackage{footnote}
\usepackage{csquotes}
\usepackage[USenglish]{babel}
\usepackage[backend=biber]{biblatex}

\addbibresource{articleBOS.bib}
\begin{document}
\today
\section{Abstract}

\section{Introduction}

\section{Simple Model}
Consider the experimental set up as shown in Figure \ref{fig:schviepalira}. Light rays travel from a camera, through a water tank onto a background with a random dot pattern.  We describe the camera as a pinhole camera. We place the origin of the Cartesian coordinate system at the pinhole, the location where all light rays falling on the ccd sensor pass through. The $z$-axis is perpendicular to the experimental setup, i.e. such that a light ray traveling along the z-axis will not be refracted by the set-up. We want to determine the position where the light rays ends up, $x_6$. The light ray exits the camera with a position $x_1 = 0$ and an angle $\theta_x$. %The $x$-axis points opposite to gravity.

%\begin{figure}[hpbt]
%	\includestandalone{simplesetup}
%	\caption{A schematic view of a path of a light ray (not to scale). The numbers indicate the planes through which the light ray propagates: 1, the camera lens; 2, the start of the first glass plate; 3, the end of the first glass plate; 4, the start of the second glass plate; 5, the end of the second glass plate; 6, the screen from which the light rays originate. $n_0$, $n_1$ and $n_2$ are the index of refraction of, respectively, air, material of the tank and the fluid. The lengths are: $L_c$, the distance from camera to the first glass plate; $L_g$, the width of the glass plates; $L_t$ the width of the tank; $L_s$, the distance from the second glass plate to the screen.}
%	\label{fig:schviepalira}
%\end{figure}

\begin{figure}[hpbt]
	\includestandalone{schematicsetupangle}
	\caption{A schematic view of a path of a light ray (not to scale). The light ray in the reference state is indicated by a solid line, the light ray after filling the tank with water by a dashed line. The numbers indicate the planes through which the light ray propagates: 0, the ccd sensor inside the camera; 1, the camera pinhole; 2, the start of the first glass plate; 3, the end of the first glass plate; 4, the start of the second glass plate; 5, the end of the second glass plate; 6, the screen from which the light rays originate.  $n_0$, $n_1$ and $n_2$ are the index of refraction of, respectively, air, material of the tank and the fluid. The lengths (in the $z$-direction)  	are: $L_c$, the distance from camera to the first glass plate; $L_g$, the width of the glass plates; $L_t$ the width of the tank; $L_s$, the distance from the second glass plate to the screen.}	
\label{fig:schviepalira}	
\end{figure}

Assuming the refractive index in each section of the set up is constant, we can write for the light path,
\begin{equation}
	\label{eq:simpleline}
x(z) = x_i + z \tan \theta_i, \qquad i = 1, ... , 5,
\end{equation}
where $x_i$ is the $x$-position of the light ray at the start of each section and $\theta_i$ is the angle between the direction the ray is propagating and the $z$-axis. When encountering a discontinuous change in refractive index (when passing between the sections), we invoke Snell's laws
\begin{equation}
	\label{eq:snellslaw}
n_i \sin \theta_i = \mbox{ constant},
\end{equation}
where $n_i$ is the refractive index for the $i^{th}$ section. The position $x_6$ is
\begin{align}
\label{eq:simplex6}
x_6 (\theta_x, n_2) & =  (L_c+L_s) \tan \theta_x + 2 L_g \tan \arcsin \frac{n_0}{n_1} \sin \theta_x + L_t \tan \arcsin \frac{n_0}{n_2} \sin \theta_x \nonumber \\
& =  (L_c+L_s) \tan \theta_x + \frac{2 L_g n_0 \sin \theta_x}{\sqrt{n_1^2 - n_0^2 \sin^2 \theta_x}} + \frac{L_t n_0 \sin \theta_x}{\sqrt{n_2^2 - n_0^2 \sin^2 \theta_x}}.
\end{align}
The displacement $\Delta x$ is the difference in position $x_6$ between the constant reference state, $n_2 = n_0$, and the unknown state $n_2=n$, 
\begin{align}
\label{eq:dexcon2}
\Delta x = x_6 (n_2 = n_0) - x_6 (n_2 = n) & = L_t \left[ \tan \theta_x - \tan \arcsin \frac{n_0}{n} \sin \theta_x\right] \nonumber \\
& = L_t \left[ \tan \theta_x - \frac{n_0 \sin \theta_x}{\sqrt{n^2 - n_0^2 \sin^2 \theta_x}} \right] .
\end{align}
Inverting this relation we obtain the unknown refractive index $n$ as a function of the displacement
\begin{equation}
\label{eq:invdexcon2}
n = \frac{n_0 \sin \theta_x}{\sin \arctan \left( \tan \theta_x - \frac{\Delta x}{L_t} \right)} = \frac{n_0 \sin(\theta_x)}{\tan(\theta_x)-\frac{\Delta x}{L_t}} \sqrt{1+\left(\tan(\theta_x)-\frac{\Delta x}{L_t}\right)^2}.
\end{equation}
The angle $\theta_x$, the displacement $\Delta x$ and unknown index of refraction $n$ are functions of the coordinate $x$. % Equation (\ref{eq:invdexcon2}) holds for each point.

%The index of refraction of air $n_0$ is constant. The light ray hits the first glass plate with a position
%\begin{equation}
%\label{eq:tanlaw}
%x_2 = L_c \tan \theta_x.
%\end{equation}
%The index of refraction of the glass plate $n_1$ is constant. The angle under which the light ray propagates changes instantaneously, obeying Snell's law
%\begin{equation}
%\label{eq:snelllaw}
%n_0 \sin \theta_x = n_1 \sin \theta_2.
%\end{equation}
%For a constant index of refraction in the water tank $n_2$ the position $x_6$ is
%\begin{equation}
%x_6 (\theta_x, n_2) = (L_c+L_s) \tan \theta_x + 2 L_g \tan \arcsin \frac{n_0}{n_1} \sin \theta_x + L_t \tan \arcsin \frac{n_0}{n_2} \sin \theta_x
%\end{equation}
%The displacement $\Delta x$ is the difference in position $x_6$ for two different values of $n_2$. We take one known value, the %tank is filled with air, $n_0$, and one unknown value $n_2 = n$. 
%\begin{equation}
%\label{eq:dexcon2}
%\Delta x = x_6 (n_2 = n_0) - x_6 (n_2 = n) = L_t \left[ \tan \theta_x - \tan \arcsin \frac{n_0}{n} \sin \theta_x\right].
%\end{equation}
%We can invert this relation to obtain the unknown $n$,
%\begin{equation}
%\label{eq:nfromdxsimple}
%	n = \frac{n_0 \sin(\theta_x)}{\tan(\theta_x)-\frac{\Delta x}{L_t}} \sqrt{1+\left(\tan(\theta_x)-\frac{\Delta x}{L_t}\right)^2}.
%\end{equation}

Figure \ref{fig:simmod} shows the results when using (\ref{eq:invdexcon2}) to obtain the index of refraction $n$. We have two frontal images of the experimental setup; (1) Figure \ref{fig:air0simplefrontal}, without water, and (2) Figure \ref{fig:fresh0simplefrontal}, with water.  Applying a Digital Image Correlation (DIC) method we obtain (1) the correlation coefficient, a measure of the reliability of the method, (2) the horizontal displacements $\Delta x$, and (3) the vertical displacements $\Delta y$. Where coordinates where $\Delta x = 0$ and $\Delta y = 0$ are the location of the $z-axis$. We calculate the angles $\theta_x$ and $\theta_y$ with respect to this $z$-axis. Using (\ref{eq:invdexcon2}) we can compute the index of refraction $n$. Figure \ref{fig:nfromdxsimplefrontal} shows $n$ obtained from the horizontal displacements $\Delta x$.  Figure \ref{fig:nfromdysimplefrontal} shows $n$ obtained from the vertical displacements $\Delta y$. In Figure \ref{fig:nfrontal} we combine the horizontal and vertical displacements to obtain $n$.

\begin{figure}[htbp]
\begin{subfigure}{.5\linewidth}
		\centering \includegraphics[width = \textwidth]{Refsimplefrontal}
		\subcaption{Reference Image: Filled with air}\label{fig:air0simplefrontal}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{deformedsimplefrontal}
	\subcaption{Deformed Image: Filled with water}\label{fig:fresh0simplefrontal}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{CCsimplefrontal}
	\subcaption{Correlation Coefficient from DIC}\label{fig:CCsimplefrontal}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{DXsimplefrontal}
	\subcaption{$\Delta x$ from DIC}\label{fig:DXsimplefrontal}
\end{subfigure}\\
	\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{DYsimplefrontal}
	\subcaption{$\Delta y$ from DIC}\label{fig:DYsimplefrontal}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{nfromdxsimplefrontal}
	\subcaption{$n$ from $\Delta x$}\label{fig:nfromdxsimplefrontal}
\end{subfigure}\\
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{nfromdysimplefrontal}
	\subcaption{$n$ from $\Delta y$}\label{fig:nfromdysimplefrontal}
\end{subfigure}%
\begin{subfigure}{.5\linewidth}
	\centering \includegraphics[width = \textwidth]{nsimplefrontal}
	\subcaption{$n$ from $\sqrt{\Delta x^2+\Delta y^2}$}\label{fig:nfrontal}
\end{subfigure}
\caption{Simple Model Result. When the angle $\theta_x$ is near zero, large errors in $n$ appear. }
\label{fig:simmod}
\end{figure}

We see that when the displacements approach zero, we have very large errors in $n$. Figure \ref{fig:nfrontal} looks best, but is still unacceptable. Around the location of the $z-axis$, where the angles and displacements approach zero, the errors are very large. The entire figure should have a constant value of $n = 1.333$. This is not the case.

Equations (\ref{eq:dexcon2}) and (\ref{eq:invdexcon2}) reveal a problem when determining $n$: When the angle $\theta_x$ goes to zero, (\ref{eq:dexcon2}) shows $\Delta x$ goes to zero. Then the numerator in the fraction in (\ref{eq:invdexcon2}) goes to zero, while the two terms in the denominator both go to zero. So we get large errors in the magnitude of $n$ since we are dividing $0/0$ and we get possibly negative values of $n$ since both terms in the denominator can go to zero. In any measurement we have noise, resulting in uncertainties in $\Delta x$ and $\theta_x$. These uncertainties have a large effect on the value of $n$ since the expected values of $\Delta x$ and $\theta_x$ are small. %The Signal-to-Noise Ratio is very bad because our signal is very small.

To solve this, we want $\theta_x$ to not approach zero. Then, according to (\ref{eq:dexcon2}), $\Delta x$ does not approach zero and our calculation of $n$ is not plagued by a fraction that approaches $0/0$. To achieve this, we place our camera at an angle $\alpha$ with respect to the water tank. The angle $\theta_x$ is replaced by $\alpha+\phi_x$, where $\phi_x$ is the angle of the light ray relative to the principal axis of the camera, which is at an angle $\alpha$. For example, we position our camera at an angle of $\alpha=30^\circ$ relative to the tank. The camera has a viewing range of $[-4,4]$ degrees. Then $\phi_x$ varies from $-4^\circ$ to $4^\circ$.

\begin{figure}[hpbt]
	\includegraphics[width=\textwidth, keepaspectratio]{dndx.png}
	\caption{Derivative of $n$ with respect to $\Delta x / L_t$ as a function of $\theta_x$.}	
	\label{fig:dndx}
\end{figure}

\begin{figure}[hpbt]
	\includegraphics[width=\textwidth, keepaspectratio]{dndt.png}
	\caption{Derivative of $n$ with respect to $\theta_x$ as a function of $\theta_x$.}		
	\label{fig:dndt}
\end{figure}

We want $\Delta x$ to vary with $n$ as much as possible. So, we want $n$ to vary with $\Delta x$ as little as possible.  To find the best angle $\theta_x$ to achieve this, we take the derivative of (\ref{eq:invdexcon2}) with respect to $\Delta x/L_t$ \cite{nemoto1992measurement}. Figure \ref{fig:dndx} show this derivative: $\partial n/\partial (\Delta x/L_t)$ decreases with increasing $\theta_x$. The worst possible angle to measure $\Delta x$ is $0^\circ$.

Since there is also an uncertainty in the angle, we want $n$ to vary with $\theta_x$ as little as possible. Figures \ref{fig:dndt} show this derivative. The magnitude of this derivative $\left|\partial n/\partial \theta_x\right|$ first decreases with increasing $\theta_x$, reaches a minimum, then increases again. The worst possible angles to measure at are $0^\circ$ and $90^\circ$. This minimum is reached at $31^\circ$. Any angle between $15^\circ$ and $60^\circ$ yields approximately the same sensitivity of $n$.

Viewing at too large an angle (e.g. $70^\circ$) makes it hard to see through the water tank. 
%As an example, we take an index of refraction $n=1.333$, an index of refraction $n_0 = 1$, a tank width $L_t=0.2[m]$ and an angle $\theta_x=30^\circ$. (\ref{eq:dexcon2}) yields a $\Delta x = 0.0345[m]$. From Figure (\ref{fig:dndx}), $\partial n/\partial (\Delta x/L_t) = 2.831$  at $\theta_x = 30^\circ$. Hence an error of $1[mm]$ in $\Delta x$ causes an error of $0.014$ in $n$. From Figure (\ref{fig:dndt}), $\partial n/\partial \theta_x = -1.466$  at $\theta_x = 30^\circ$. Hence an error of $0.1^\circ$ in $\theta_x$ causes an error of $-0.15$ in $n$.

%To perform accurate measurements we want to determine $n$ with at least 5 significant digits. To achieve this, we place our camera under an angle to minimize the effect of errors in $\Delta x$ and $\theta_x$ on the index of refraction.

%To reduce

Concluding, Figures \ref{fig:dndx} and \ref{fig:dndt} indicate that the worst angles to measure are close to zero. Angles between $15^\circ$ and $60^\circ$ result in small errors in $n$.

\clearpage 
\section{Forward Model}
In this section we build a forward model, relating an index of refraction field $n$, position on the ccd-sensor $\underline{x}$ and parameters $\underline{\alpha}$ to the coordinates $\underline{X}$ where the light rays hits the screen. We seek a model $\underline{X}(n, \underline{\alpha}, \underline{x})$. This is an extension of (\ref{eq:simplex6}).

In Subsection \ref{subsec:rayequ} we derive the equations governing 3-dimensional ray optics in an inhomogeneous medium. In Subsection \ref{subsec:RayPath} we use these equations to construct the full ray path from the camera through the tank to the screen.

\subsection{Ray Equation} 
\label{subsec:rayequ}
In this section we derive equations describing the paths light rays follow in inhomogeneous media. Inhomogeneous media have a index of refraction $n$ that varies with position.

A curved ray path is a space curve, which we can describe by a parametric representation, $\underline{r}(\sigma) = ( x(\sigma), y(\sigma), z(\sigma))$, where $\sigma$ is an arbitrary parameter. The two most used parameters are (1) the path length long the ray $s$ and (2) the axial position $z$. We denote derivatives with respect to the parameter by dots, so $\dot{\underline{x}}(\sigma) = d\underline{x}(\sigma)/d\sigma$. All parameters are functions of $s$.

The optical length $\mathcal{A}$ of a path $\underline{r}(s)$ taken by a ray of light passing from point $A$ to point $B$ in three-dimensional space is defined by
\begin{equation}
	\label{eq:defAA}
	\mathcal{A} = \int_A^B \! n(\underline{r}(s)) \, \mathrm{d}s,
\end{equation}
where $n(\underline{r})$ is the index of refraction at the spatial point $\underline{r} \in \mathbb{R}^3$. We choose the element of arc length $\mathrm{d}s$ along the ray path $\underline{r}(s)$ through that point as $\mathrm{d}s^2 = \mathrm{d}\underline{r}(s) \cdot \mathrm{d}\underline{r}(s)$, so that $|\dot{\underline{r}}|=1$.

Applying Fermat's principle \cite{holm2011geometric} yields the eikonal equation for ray optics
\begin{equation}
	\label{eq:axialrayequation}
	\frac{\partial n}{\partial \underline{r}} = \frac{d}{ds} \left(n(\underline{r}) \frac{\mathrm{d}\underline{r}}{\mathrm{d} s} \right).
\end{equation}
%Another way to write this ray equation is
%\begin{equation}
	%\label{eq:axialrayequationvector}
	%\nabla n = n \ddot{\underline{r}} + (\nabla n \cdot \dot{\underline{r}}) \dot{\underline{r}}
%\end{equation}
Only two of the component equations are independent, since $|\dot{\underline{r}}| = 1$.

To find the equations used in Synthetic Schlieren \cite{weyl1954analysis,dalziel2000whole}, we first derive the axial eikonal equation. Most optical instruments are designed to posses a line of sight (or primary direction of propagation of light) called the optical axis. In Synthetic Schlieren this optical axis coincides with the direction in which the refractive index $n$ does not vary. Choosing a Cartesian coordinate system such that the $z$-axis coincides with this optical axis, expresses the arc-length $\mathrm{d}s$ in terms of the increment along the optical axis, $\mathrm{d}z$. Our parametric description is now in terms of $z$: $\underline{r}(z) = (x(z), y(z), z)$. From our definition of $\mathrm{d}s$
\begin{equation}
	\mathrm{d}s(z) = \sqrt{dx^2(z) + dy^2(z) + dz^2} = \sqrt{1+\dot{x}^2 +\dot{y}^2} d z = \frac{1}{\gamma} d z,
\end{equation}
where $\dot{x} = d x / dz$ and $\dot{y} = dy/dz$ and 
\begin{equation}
	\label{eq:gamma}
	\gamma = \frac{d z}{d s} = \frac{1}{\sqrt{1+\dot{x}^2+\dot{y}^2}} = \cos \theta\leq 1,
\end{equation}
where $\theta$ is the angle the ray makes with the $z$-axis. Using (\ref{eq:gamma}) in (\ref{eq:axialrayequation}) yields the axial eikonal equation %The position of a ray at a fixed value of $z$ is denoted by $[x,y]^T$.
\begin{equation}
	\gamma \frac{d}{dz} \left(n(\underline{r}(z)) \gamma \frac{d \underline{r}(z)}{d z} \right)  = \frac{\partial n(\underline{r}(z))}{\partial \underline{r}}.
\end{equation}
This yields three equations, one for each coordinate direction,
\begin{equation}
	\label{eq:axraycoord}
	\begin{aligned}
		\ddot{x}  &= \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial x} - \dot{x} \frac{\partial n}{\partial z} \right), \\
		\ddot{y} &= \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial y} - \dot{y} \frac{\partial n}{\partial z} \right), \\
		\frac{\partial n}{\partial z} &= \gamma \frac{d}{dz}\left(n  \gamma\right).
	\end{aligned}
\end{equation}	
Indeed, this system of equations shows that only two equations are independent. In Synthetic Schlieren the variation in $n$ in the $z$-direction, the optical axis, is assumed to be zero. Then (\ref{eq:axraycoord}) reduce to
\begin{equation}
	\label{eq:SSeq}
		\ddot{x} = \left(1+\dot{x}^2+\dot{y}^2\right) \frac{1}{n} \frac{\partial n}{\partial x}, \qquad
		\ddot{y} = \left(1+\dot{x}^2+\dot{y}^2\right) \frac{1}{n} \frac{\partial n}{\partial y},
\end{equation}
which are the starting point for the derivation of Synthetic Schlieren in \cite{dalziel2000whole}.  \footnote{The third equation in (\ref{eq:axraycoord}) reduces to $n \gamma = constant$.  To integrate (\ref{eq:SSeq}) we do not need to assume $\dot{x}$ and $\dot{y}$ are small. Experimentally, this means we can apply Synthetic Schlieren even when the angles of the light rays are large. }

In the application presented in this paper, the optical axis does not coincide with the direction in which the refractive index $n$ does not vary. Our parametric description is in the arc-length $s$ and not in $z$.  We cannot solve (\ref{eq:axialrayequation}) analytically, so we solve it numerically. We first write our system of three second-order differential equations as a system of 6 first-order differential equations by introducing a quantity $\underline{T}$ \cite{southwell1982ray} such that (\ref{eq:axialrayequation}) becomes
\begin{equation}
	\label{eq:sys6foeq}
		\frac{d \underline{r}}{d s} = \frac{\underline{T}}{n}, \qquad
		\frac{d \underline{T}}{d s} = \nabla n.
\end{equation}
We apply a Runge–Kutta fourth-order method to solve this system. Appendix \ref{app:RKS} gives the details.

\subsection{Relating Refractive Index to Ray Path}
\label{subsec:RayPath}
To give our method flexibility and not making assumption on the relative configuration in our experimental setup, we model the light rays as traversing in a three-dimensional space and allow the different elements in the experimental setup to have any alignments.

We place our origin again at the pinhole. The $z$-axis aligns with the optical axis of the camera, i.e. the viewing direction of the camera. All the light entering the camera travels through the pinhole and falls on the ccd-sensor. The $x$- and $y$-axes span a plane through the origin parallel to this ccd-sensor.

\subsubsection{Plane Definition}
The mathematical definition of a plane is
\begin{equation}
	\label{def:plane}
	\underline{\hat{n}} \cdot (\underline{x}-\underline{x}_0) = 0,
\end{equation}
where $\underline{\hat{n}} = (a,b,c)$ is the unit normal vector of the plane, $\underline{x}$ a random vector within the plane and $\underline{x}_0$ a random point on the plane. Expanding (\ref{def:plane}) yields
\begin{equation}
	a(x-x_0) + b(y-y_0) + c(z-z_0) = 0, 
\end{equation}
or 
\begin{equation}
	\label{eq:planedef2}
	ax+by+cz + d = 0 \qquad \mbox{ with } \qquad d = - a x_0 - b y_0 - c z_0.
\end{equation}
For each of the planes 2 to 6 in Figure \ref{fig:schviepalira}, we can write an equation of the form (\ref{eq:planedef2}). We assume all planes are parallel to each other. Then the parameters $a$, $b$ and $c$ are the same for each plane; only $d$ changes. The distances in the normal direction of each plane are known, e.g. $L_s$, $L_g$, etc. Given the equation describing plane 6, 
\begin{equation}
\label{eq:planedef6}
	a x + b y + c z + d = 0,
\end{equation}
we can compute the equations describing the other planes
\begin{align}
a x + b y + c z + d_i = 0, \qquad  
& d_5 = d + (a+b+c) L_s, \\
& ..., \nonumber \\ 
& d_2 = d + (a+b+c) (L_s+2L_g+L_t), \\
\label{eq:planedef1}
& d_1 = d + (a+b+c) (L_s+2L_g+L_t+L_c) = 0 
\end{align}

\subsubsection{Direction Cosines}
Each pixel in our image corresponds to a physical location on the ccd-sensor with coordinates $\underline{x} = (x,y, -L_f)$, where $L_f$ is the distance from the ccd-sensor to the pinhole in the $z$-direction. We calculate this distance with the thin lens equation
\begin{equation}
 \frac{1}{L_f} + \frac{1}{L_m} = \frac{1}{f},
\end{equation}
where $f$ is the focal length of the camera and $L_m$ is the distance from the pinhole to screen (plane 6) along the $z$-axis. This distance is found from (\ref{eq:planedef6}) for $x=y=0$. Then $d = - c L_m$.

The physical coordinates $x$ and $y$ are obtained from the pixel locations $x_p, y_p$, the pixel locations at $(x,y)=(0,0)$ $x_p^0$ and $y_p^0$ and the physical size of each pixel on the ccd-sensor. Assuming each pixel on the ccd-sensor is square, we call the physical size of each sensor $S^2$. $S$ has units $\mu m/pixel$. The physical coordinates are then found from the pixel locations by
\begin{equation}
	x = S (x_p-x_p^0), \qquad  y = S (y_p-y_p^0).
\end{equation}

Each light ray travels in a straight line from these coordinates $\underline{x}$, through the pinhole, to the experimental setup. We describe each of these light rays with direction cosines: the cosines of the angles between the light ray and the three coordinate axes:
\begin{align}
\label{eq:directioncosines}
	\alpha &= \cos \theta_x = \frac{x}{\sqrt{x^2+y^2+L_f^2}} \nonumber \\
	\beta &= \cos \theta_y = \frac{y}{\sqrt{x^2+y^2+L_f^2}} \\
	\gamma &= \cos \theta_z = \frac{L_f}{\sqrt{x^2+y^2+L_f^2}} \nonumber
\end{align}
At the pinhole, all light rays pass through the origin and have coordinates (0,0,0). Each light ray has direction cosines $(\alpha, \beta, \gamma)$.

\subsubsection{Intersection Light Rays and Planes: Homogeneous medium}
The equation governing light rays in homogeneous media is
\begin{equation}
	\label{eq:linedef}
   \underline{p} = \underline{s} + \underline{I} l,
\end{equation}
where $\underline{s} = (s_x, s_y, s_z)$ is the initial position, $\underline{I} = (\alpha, \beta, \gamma)$ the direction cosines, $p = (p_x, p_y, p_z)$ the final position and $l$ the length traveled along the light ray. %This is the extension of (\ref{eq:simpleline}) in three-dimensions.

To intersect with a plane, the final position $\underline{p}$ must lie on that plane. Substituting (\ref{eq:planedef2}) into (\ref{eq:linedef}) and solving for $l$ yields 
\begin{equation}
	l = - \frac{d + a s_x + b s_y + c s_z}{a \alpha + b \beta + c \gamma}
\end{equation}
Substituting this $l$ into (\ref{eq:linedef}) yields the location where each light rays intersects with the plane.

\subsubsection{Snell's Law}
To find the angle of incidence, $\theta_1$, between the incoming light ray and the plane, we compute
\begin{equation}
	\cos \theta_1 = \underline{\hat{n}} \cdot \underline{I}.
\end{equation}
We apply Snell's law (\ref{eq:snellslaw}) to find the angle of refraction, $\theta_2$. The index of refraction of the medium through which the incoming ray travels is $n_I$, the index of refraction of the medium through wich the outgoing ray travels is $n_T$. To find the direction cosines of the outgoing ray, $\underline{T}$, we calculate 
\begin{align}
	S &= sign \cos \theta_1, \\
	\sin \theta_2 &= \frac{n_I}{n_T} \sqrt{1-\cos^2 \theta_1}, \\
	\cos \theta_2 &= \sqrt{1-\left(\frac{n_I}{n_T}\right)^2(1-\cos^2 \theta_1)} \\
	\underline{T} &= \frac{n_I}{n_T} \underline{I} + \left(\frac{n_I}{n_T} \cos \theta_1 - S \cos\theta_2\right)\underline{\hat{n}},	
\end{align}
where $S$, the sign of $\cos\theta_1$ ensures we stay in the right quadrant.

\subsubsection{Rotation Matrix}
\label{subsubsec:rotmat}
{\color{red} Work in Progress, you can skip this} \\
A rotation through an angle of $\theta$ around an axis defined by the unit vector $\underline{\hat{r}} = r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}}$ can be represented by a quaternion
\begin{equation}
	\underline{q} = \cos\frac{\theta}{2} + (r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}} ) \sin \frac{\theta}{2}.
\end{equation} 
A unit quaternion has norm one. The rotation matrix $Q$ for a unit quaternion $\underline{q} = q_0 + q_1 \underline{\hat{i}} + q_2 \underline{\hat{j}} + q_3 \underline{\hat{k}}$ is
\begin{equation}
	Q = \left[ \begin{array}{ccc} 1-2(q_2^2+q_3^2) & 2(q_1 q_2 - q_0 q_3) & 2(q_1 q_3 + q_0 q_2) \\ 2 (q_1 q_2 + q_0 q_3) & 1-2(q_1^2+q_3^2) & 2( q_2 q_3 - q_0 q_1) \\ 2(q_1 q_3-q_0 q_2) & 2 (q_2 q_3 + q_0 q_1) & 1 - 2 (q_1^2+q_2^2) \end{array} \right]
\end{equation}

The rotation angle is
\begin{equation}
	\cos \theta = a \cdot 0 + b \cdot 0 + c \cdot 1
\end{equation}
and the rotation vector
\begin{equation}
	\underline{\hat{r}} = - \frac{b}{\sqrt{a^2+b^2}} \underline{\hat{i}} + \frac{a}{\sqrt{a^2+b^2}}  \underline{\hat{j}} + 0  \underline{\hat{k}}.
\end{equation}

\subsubsection{Intersection Light Rays and Planes: Inhomogeneous medium}
{\color{red} Work in Progress, you can skip this} \\
A light ray traveling through an inhomogeneous medium does not travel in a straight line. The path is governed by (\ref{eq:sys6foeq}). To simplify (\ref{eq:sys6foeq}), we can use that there is a direction in the experimental setup that has no variation in index of refraction $n$, which is the direction of the unit normal of the different planes. To use this simplification, we want to transform our direction cosines in our original coordinate system, $xyz$ into direction cosines in a new coordinate system, $XYZ$. In this new coordinate system, the $Z$-axis is opposite to the unit normal vector $\underline{\hat{n}}$. To find this transformation matrix, we use quaternions.

\subsubsection{Procedure Varying n}
{\color{red} Work in Progress, you can skip this} \\
Given $n(x,y)$. Old coordinates: x,y,z. New coordinates u,v,w.
\begin{enumerate}
	\item Determine Coordinate Transformation according to \ref{subsubsec:rotmat}. \\
	\item Transform Initial Position to new coordinates u,v  \\
	\item Initiate n field in new coordinates u,v \\
	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
	\item Transform Refracted Rays to new coordinates u, v, w \\
	\item  Runge-Kutta \\
	\item  Obtain grad n = ( dn/du, dn/dv, dn/dw) \\
	\item  Transform incoming rays back to coordinates x y z \\
	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
	\item Transform Final Positions to new old coordinates x, y, z \\
\end{enumerate}

\subsection{Displacements}
Previous subsections combine to give the forward model: $\underline{X}(n,\underline{\alpha}, \underline{x})$. Given an index of refraction field $n$, parameters $\underline{\alpha}$ and coordinates $\underline{x} = (x,y)$, we can calculate the location on the screen where the light rays end up. $\underline{\alpha}$ are the parameters that define the planes $a$, $b$, $c$ and $L_m$. We use $L_m$ instead of $d$ since we want our parameters to be (linearly) independent. Also, $L_m$ has a clear geometric meaning.

We take our forward model twice, once for a known index of refraction (typically constant) $n_0$ and once for an unknown index of refraction field $n$. The light rays originating from the same location on the screen end up on different locations on the ccd sensor:
\begin{equation}
\label{eq:ForwardModel}
	 \underline{X}(n, \underline{\alpha}, \underline{x}+\underline{\Delta x}) - \underline{X}(n_0, \underline{\alpha}, \underline{x}) = 0, \qquad \underline{X} = (X, Y, Z).
\end{equation}
This equation holds for each measured displacement $\underline{\Delta x} = (\Delta x, \Delta y)$. From (\ref{eq:directioncosines}) we see that light rays with different locations on the ccd-sensor have different angles with which they leave the camera. Due to the different index of refraction in the tank, they do end up in the same location on the screen.

\section{Calibration}
In our forward model in Section \ref{subsec:RayPath}, we have used the parameters describing a plane $a$, $b$ and $c$ and $L_m$. However, when setting up a new experiment, these are not known. To obtain these, we perform a calibration step. This calibration determines the parameters very precisely and gives us a lot of experimental freedom. For example, we do not have to align the camera, or even measure the position of the camera relative to the water tank. We use calibration for this.

The calibration consists of performing one extra measurement (two in total): we take a reference image, the tank without water (filled with air) and a deformed image, the tank filled with water with a known index of refraction. The easiest is water without any salts. Performing DIC yields us the displacements $\Delta \underline{x}$. This allows us to determine the parameters $\underline{\alpha}.$

In our simple model, this calibration is the equivalent of (\ref{eq:dexcon2}). We know $n$, $n_0$ and $\Delta x$ and we want to determine $\alpha$ (from $\theta_x = \alpha+\phi_x$).

Looking at our Forward Model (\ref{eq:ForwardModel}), we know
\begin{enumerate}
	\item $n=n_0$ and $n=n_1$, the index of refraction of reference image (filled with air) and the deformed image (filled with water); 
	\item $\underline{x}$, the coordinates on our ccd-sensor; 
	\item $\underline{\Delta x}$, the measured displacement (after DIC). 
\end{enumerate}
The unknowns are the parameters $\underline{\alpha} = (a, b, c, L_m)$. Since we have only four parameters to estimate and many measurements (each grid point yields a separate equation), we have an over-determined system. We use a least-squares approach to find those $\underline{\alpha}$ that minimize the sum of squares of the residuals. The forward model depends nonlinearly on the parameters $\alpha$ and the measurements $\underline{\Delta x}$. For each measurement $\underline{\Delta x}$ we have a measure of reliability, the correlation coefficient, which we use as a weight $w$ in the least squares procedure
\begin{equation}
\label{eq:calmin} 
\min_{\underline{\alpha}}  S = \min_{\underline{\alpha}} \sum_i w_i X_{j}(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i)^2, 
\end{equation}
with constraints (1) $L_c > 0$ and (2) $L_m \geq L_c + 2 L_g + L_t + L_s$, the experimental setup is in front of the camera; (3) $c < 0$, the unit normal vector of the planes points in the negative $z$-axis. Combining these constraints implies $d>0$. The sum is over all measured displacements. The weights $w_i$ are $0$ when $CC < 0.8$ and $1$ otherwise. We use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal.

The distance $L_c$ between the camera and the front of water tank (plane 2) along the $\underline{\hat{n}}$ direction is obtained from the total distance $d$ between the camera and the screen along the $z$-direction and the distances $L_g, L_t$ and $L_s$. This ensures internal consistency in our model. We obtain $L_c$ from (\ref{eq:planedef1}).

To find the best way to solve (\ref{eq:calmin}), Figures \ref{fig:Sab} to \ref{fig:ScLm} show $S$ as a function of $\underline{\alpha}$ for a typical experiment. For each figure, we have fixed two parameters of $\underline{\alpha}$ and varied the other two. The blue lines indicate the constraint $L_c >0$ and the red lines indicate the constraint $L_m \geq L_c + 2 L_g + L_t + L_s$. The black cross indicates the global minimum in the allowable region.

All figures show very nice behavior of $S$. Figures \ref{fig:Sab}, \ref{fig:Sac} and \ref{fig:SbLm} show one clear minimum in the allowed region. Figures \ref{fig:Sac}, \ref{fig:SaLm} and \ref{fig:ScLm} show one clear valley in the allowed region.

It seems that when we choose an initial condition that falls in the permissible regions and use a gradient-based optimization scheme we will end up in the minimum. %Only one minimum exists in each of the permissible regions.

\begin{figure}[htbp]
		\centering \includegraphics[width = \textwidth]{leastsquaresab.png}
		\caption{$\log_{10}S(a,b)$}\label{fig:Sab}
\end{figure}
\begin{figure}[htbp]
		\centering \includegraphics[width = \textwidth]{leastsquaresac.png}
		\caption{$\log_{10}S(a,c)$}\label{fig:Sac}
\end{figure}
\begin{figure}[htbp]
		\centering \includegraphics[width = \textwidth]{leastsquaresad.png}
		\caption{$\log_{10}S(a,d)$}\label{fig:SaLm}
\end{figure}
\begin{figure}[htbp]
		\centering \includegraphics[width = \textwidth]{leastsquaresbc.png}
		\caption{$\log_{10}S(b,c)$}\label{fig:Sac}
\end{figure}
\begin{figure}[htbp]
		\centering \includegraphics[width = \textwidth]{leastsquaresbd.png}
		\caption{$\log_{10}S(b,d)$}\label{fig:SbLm}
\end{figure}
\begin{figure}[htbp]
		\centering \includegraphics[width = \textwidth]{leastsquarescd.png}
		\caption{$\log_{10}S(c,d)$}\label{fig:ScLm}
\end{figure}

\clearpage
%\begin{figure}[htbp]
%	\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{leastsquaresab.png}
%		\subcaption{$S(a,b)$}\label{fig:Sab}
%	\end{subfigure}%
%	\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{leastsquaresac.png}
%	\subcaption{$S(a,c)$}\label{fig:Sac}
%	\end{subfigure}\\
%	\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{leastsquaresad.png}
%	\subcaption{$S(a,d)$}\label{fig:SaLm}
%	\end{subfigure}%
%	\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{leastsquaresbc.png}
%		\subcaption{$S(b,c)$}\label{fig:Sac}
%	\end{subfigure}\\
%	\begin{subfigure}{.5\linewidth}
%	\centering \includegraphics[width = \textwidth]{leastsquaresbd.png}
%	\subcaption{$S(b,d)$}\label{fig:SbLm}
%	\end{subfigure}%
%	\begin{subfigure}{.5\linewidth}
%		\centering \includegraphics[width = \textwidth]{leastsquarescd.png}
%		\subcaption{$S(c,d)$}\label{fig:ScLm}
%	\end{subfigure}
%	\caption{Calibration: $S$ as a function of $\underline{\alpha}$.}
%	\label{fig:cal}
%\end{figure}

\section{Gladstone-Dale vs Lorentz-Lorenz}

\section{Digital Image Correlation}
B-splines
2nd order
reliability guided

\section{Experimental}
Best practices to get good quality images

random dot pattern -> grey -> histogram no over/under saturation

\section{Inverse Model}
Looking at our Forward Model (\ref{eq:ForwardModel}), we know
\begin{enumerate}
	\item $\underline{\alpha}$, the parameters of our experimental setup (after calibration), \\
	\item $\underline{x}$, the coordinates on our ccd-sensor, \\
	\item $\underline{\Delta x}$, the measured displacement (after DIC), \\
	\item $n_0$, the index of refraction of the reference state.
\end{enumerate}
The unknown is the index of refraction field $n$. Unlike the simple model (\ref{eq:invdexcon2}), we cannot invert the forward model to obtain an expression for the index of refraction $n$. We treat the problem of finding $n$ as an optimization problem:
\begin{equation}
\label{eq:nmin} 
\min_{n_i}  S = \min_{n_i} (X_{j}(n, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i))^2, 
\end{equation}
with constraints $1.333 \leq n_i \leq 1.4$. For each measurement $\underline{\Delta x}_i$ we solve (\ref{eq:nmin}) to find $n_i$.
\section{Experimental Procedure}
Calibration
\section{Results}

\subsection{Background Density}

WA
\section{Discussion}

definition planes -> doesn't have to be parallel. in particular 6th plane can be different, extra parameters to estimate in $\alpha$ (calibration). \\
non plane water tank: measure without tank, with tank with air -> (calibration) shape of tank, field $L_t$
-> doesn't even have to be planes

\printbibliography[heading=bibintoc]

\appendix

\section{Runge-Kutta Scheme}
\label{app:RKS}
We choose a step size $h$. These are steps over the arc-length $s$. We use an index $p$ to indicate each step: $s^{p+1} = s^{p} + h$.

\end{document}

### 2020-02-05 Article/simplemodelderivatives.m

@@ -1,0 +1,53 @@
+clc;clear;close all;
+
+t = 0:1:80;
+t=deg2rad(t);
+n=1.333;
+Dx1 = tan(t) - sin(t)./(n*sqrt(1 - sin(t).^2/n^2));
+n=1.4;
+Dx2 = tan(t) - sin(t)./(n*sqrt(1 - sin(t).^2/n^2));
+
+figure;
+hold all
+box on
+plot(rad2deg(t),Dx1)
+plot(rad2deg(t),Dx2)
+xlabel('$\theta_x [^{\circ}]$', 'interpreter', 'latex')
+ylabel('$\frac{\Delta x}{L_t}$', 'interpreter', 'latex')
+legend('n = 1.333', 'n = 1.4')
+set(gca,'FontSize',40)
+hold off
+
+%%
+Dx = Dx1;
+dndt1 = -(3 + (Dx.^2 - 2).*cos(t).^2 - 3*Dx.*cos(t).*sin(t)).*cos(t).*Dx./(sqrt((Dx.^2.*cos(t).^2 - 2.*Dx.*cos(t).*sin(t) + 1)./cos(t).^2).*(-2.*Dx.*cos(t).*sin(t) + 1 + (Dx.^2 - 1).*cos(t).^2));
+Dx = Dx2;
+dndt2 = -(3 + (Dx.^2 - 2).*cos(t).^2 - 3*Dx.*cos(t).*sin(t)).*cos(t).*Dx./(sqrt((Dx.^2.*cos(t).^2 - 2.*Dx.*cos(t).*sin(t) + 1)./cos(t).^2).*(-2.*Dx.*cos(t).*sin(t) + 1 + (Dx.^2 - 1).*cos(t).^2));
+
+figure;
+hold all
+box on
+plot(rad2deg(t),dndt1, 'k')
+plot(rad2deg(t),dndt2, 'k--')
+xlabel('$\theta_x [^{\circ}]$', 'interpreter', 'latex')
+ylabel('$\frac{\partial n}{\partial \theta_x}$', 'interpreter', 'latex')
+legend('n = 1.333', 'n = 1.4')
+set(gca,'FontSize',40)
+hold off
+
+%%
+Dx = Dx1;
[…]

### 2020-02-06 Article/articleBOS.tex
DIC references, explanation

@@
 \section{Digital Image Correlation}
-B-splines
-2nd order
-reliability guided
+Digital Image Correlation (DIC) is a well known technique \cite{sutton2009image} to obtain deformation maps from images.
+We use second-order shape functions \cite{lu2000deformation} to handle large nonlinear deformations.
+To attain sub-pixel accuracy we interpolate our images with B-splines \cite{thevenaz2000interpolation, unser1999splines, thevenaz2000image}.
+To obtain the deformations we optimize a Correlation Coefficient [SOURCE].
+We solve this nonlinear least-squares problem  by (1) providing an initial guess and (2) solving an iterative scheme.
+As an initial guess we perform Template Matching \cite{lewis1995industrial,opencv_library} on a limited set of points to obtain rigid deformations with pixel accuracy.
+After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{pan2012incremental} to determine the initial guesses.
+As iterative scheme we use the Levenberg–Marquardt algorithm.
 
@@
 \section{Results}
+In this section we show three applications of the new method: (1) A static two-layer fluid with large nonlinear deformations, (2) A static stratified fluid and (3) a dynamic fluid with wave attractor.
+
+In the first application, in \ref{fig:0side}, we want to measure the background density of a two-layer fluid system.
+We filled the bottom half of a tank with Wadden Sea water (with an index of refraction of 1.338, measured by a refractometer) and the upper half of the tank with tap water (with an index of refraction of 1.333, also measured by the refractometer).
+We kept the interface between the two layers sharp by filling the upper half of the tank through a sponge.
+The observed deformations of the dot pattern through this interface are large.
+Through the use of the second-order shape functions in the DIC procedure, we can still determine these deformations.
+Figure \ref{fig:ndeformed0side} shows the index of refraction field $n$.
 
 \subsection{Background Density}
+\label{subsec:bacden}
+\begin{figure}[htbp]
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{Reference Image: Filled with air}\label{fig:air0side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+	\subcaption{Calibration Image Image: Filled with water with known $n$}\label{fig:fresh0side}
+\end{subfigure}\\
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:twolayer0side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+	\subcaption{Index of Refraction $n$ for Calibration Image}\label{fig:ncalibration0side}
+\end{subfigure}\\
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{$\Delta x$ from DIC}\label{fig:dx0side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+		\subcaption{$\Delta y$ from DIC}\label{fig:dy0side}
+\end{subfigure}\\
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{Index of Refraction $n$ for Deformed Image}\label{fig:ndeformed0side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+		\subcaption{Correlation Coefficient from DIC}\label{fig:C0side}
+\end{subfigure}
+\caption{The procedure for obtaining the index of refraction field $n$.
+We obtain three images: one Reference Image (\ref{fig:air0side}) filled with air, one Calibration Image (\ref{fig:fresh0side}) filled with water without salts and one Deformed Image (\ref{fig:twolayer0side}) filled with water with an unknown $n$-field.
+Applying DIC between the Reference Image and the Correlation image, we find the displacements $D=(\Delta x, \Delta y)$.
+Using these displacements $D$ in (\ref{eq:calmin}), we obtain the parameters $\underline{\alpha}$.
+After calibration, the resulting $n$-field is uniform (\ref{fig:ncalibration0side}).
+Applying DIC between the Reference Image and the Correlation Image, we find the displacements $\Delta x$ (\ref{fig:dx0side}) and $\Delta y$ (\ref{fig:dy0side}) with corresponding Correlation Coefficient (\ref{fig:C0side}).
+Using these displacements in (\ref{eq:nmin}), we obtain the unknown index of refraction field $n$ (\ref{fig:ndeformed0side}).}
+\label{fig:0side}
+\end{figure}
 
-WA
+In the second application, in Reference,
+
 \section{Discussion}

### 2020-02-07 Article/articleBOS.tex
Result Sketch

@@
 \usepackage{amssymb}
+\DeclareMathOperator{\sign}{sign}
 \usepackage{geometry}
@@
 \usepackage{enumitem}
-%\setlist{noitemsep}
-%\setlist[1]{labelindent=\parindent}
-%\setlist[1]{itemsep=0pt,topsep=0pt}
+%\overfullrule=5pt
 \setlist{nosep}
 \usepackage{tikz}
-\usetikzlibrary{patterns,snakes}
+\usetikzlibrary{patterns}
+\usetikzlibrary{decorations.pathreplacing}
 
@@
 \section{Introduction}
+
+Since we are working with fluids we use the Lorentz-Lorenz equation to relate the index of refraction $n$ to the density $\rho$,
+\begin{equation}
+ 	\frac{n^2-1}{n^2+2} \frac{1}{\rho} = \mbox{ constant}.
+\end{equation}
 
@@
 \begin{figure}[htbp]
-\begin{subfigure}{.5\linewidth}
-		\centering \includegraphics[width = \textwidth]{Refsimplefrontal}
+\begin{subfigure}{.45\linewidth}
+		\centering \includegraphics[width = \textwidth,keepaspectratio]{Refsimplefrontal}
 		\subcaption{Reference Image: Filled with air}\label{fig:air0simplefrontal}
 \end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-	\centering \includegraphics[width = \textwidth]{deformedsimplefrontal}
+\begin{subfigure}{.45\linewidth}
+	\centering \includegraphics[width = \textwidth,keepaspectratio]{deformedsimplefrontal}
 	\subcaption{Deformed Image: Filled with water}\label{fig:fresh0simplefrontal}
 \end{subfigure}\\
-\begin{subfigure}{.5\linewidth}
+\begin{subfigure}{.45\linewidth}
 	\centering \includegraphics[width = \textwidth]{CCsimplefrontal}
@@
 \end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-	\centering \includegraphics[width = \textwidth]{DXsimplefrontal}
+\begin{subfigure}{.45\linewidth}
+	\centering \includegraphics[width = \textwidth,keepaspectratio]{DXsimplefrontal}
 	\subcaption{$\Delta x$ from DIC}\label{fig:DXsimplefrontal}
 \end{subfigure}\\
-	\begin{subfigure}{.5\linewidth}
-	\centering \includegraphics[width = \textwidth]{DYsimplefrontal}
+	\begin{subfigure}{.45\linewidth}
+	\centering \includegraphics[width = \textwidth,keepaspectratio]{DYsimplefrontal}
 	\subcaption{$\Delta y$ from DIC}\label{fig:DYsimplefrontal}
 \end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-	\centering \includegraphics[width = \textwidth]{nfromdxsimplefrontal}
+\begin{subfigure}{.45\linewidth}
+	\centering \includegraphics[width = \textwidth,keepaspectratio]{nfromdxsimplefrontal}
 	\subcaption{$n$ from $\Delta x$}\label{fig:nfromdxsimplefrontal}
 \end{subfigure}\\
-\begin{subfigure}{.5\linewidth}
-	\centering \includegraphics[width = \textwidth]{nfromdysimplefrontal}
+\begin{subfigure}{.45\linewidth}
+	\centering \includegraphics[width = \textwidth,keepaspectratio]{nfromdysimplefrontal}
 	\subcaption{$n$ from $\Delta y$}\label{fig:nfromdysimplefrontal}
 \end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-	\centering \includegraphics[width = \textwidth]{nsimplefrontal}
+\begin{subfigure}{.45\linewidth}
+	\centering \includegraphics[width = \textwidth,keepaspectratio]{nsimplefrontal}
 	\subcaption{$n$ from $\sqrt{\Delta x^2+\Delta y^2}$}\label{fig:nfrontal}
@@
 \end{equation}
-We apply a Runge–Kutta fourth-order method to solve this system. Appendix \ref{app:RKS} gives the details.
+We apply a Runge–Kutta fourth-order method to solve this system. %Appendix \ref{app:RKS} gives the details.
 
@@
 \begin{align}
-	S &= sign \cos \theta_1, \\
+	S &= \sign \cos \theta_1, \\
 	\sin \theta_2 &= \frac{n_I}{n_T} \sqrt{1-\cos^2 \theta_1}, \\
@@
 where $S$, the sign of $\cos\theta_1$ ensures we stay in the right quadrant.
-
-\subsubsection{Rotation Matrix}
-\label{subsubsec:rotmat}
-{\color{red} Work in Progress, you can skip this} \\
-A rotation through an angle of $\theta$ around an axis defined by the unit vector $\underline{\hat{r}} = r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}}$ can be represented by a quaternion
-\begin{equation}
-	\underline{q} = \cos\frac{\theta}{2} + (r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}} ) \sin \frac{\theta}{2}.
-\end{equation} 
-A unit quaternion has norm one. The rotation matrix $Q$ for a unit quaternion $\underline{q} = q_0 + q_1 \underline{\hat{i}} + q_2 \underline{\hat{j}} + q_3 \underline{\hat{k}}$ is
-\begin{equation}
-	Q = \left[ \begin{array}{ccc} 1-2(q_2^2+q_3^2) & 2(q_1 q_2 - q_0 q_3) & 2(q_1 q_3 + q_0 q_2) \\ 2 (q_1 q_2 + q_0 q_3) & 1-2(q_1^2+q_3^2) & 2( q_2 q_3 - q_0 q_1) \\ 2(q_1 q_3-q_0 q_2) & 2 (q_2 q_3 + q_0 q_1) & 1 - 2 (q_1^2+q_2^2) \end{array} \right]
-\end{equation}
-
-The rotation angle is
-\begin{equation}
-	\cos \theta = a \cdot 0 + b \cdot 0 + c \cdot 1
-\end{equation}
-and the rotation vector
-\begin{equation}
-	\underline{\hat{r}} = - \frac{b}{\sqrt{a^2+b^2}} \underline{\hat{i}} + \frac{a}{\sqrt{a^2+b^2}}  \underline{\hat{j}} + 0  \underline{\hat{k}}.
-\end{equation}
-
-\subsubsection{Intersection Light Rays and Planes: Inhomogeneous medium}
-{\color{red} Work in Progress, you can skip this} \\
-A light ray traveling through an inhomogeneous medium does not travel in a straight line.
-The path is governed by (\ref{eq:sys6foeq}).
-To simplify (\ref{eq:sys6foeq}), we can use that there is a direction in the experimental setup that has no variation in index of refraction $n$, which is the direction of the unit normal of the different planes.
-To use this simplification, we want to transform our direction cosines in our original coordinate system, $xyz$ into direction cosines in a new coordinate system, $XYZ$.
-In this new coordinate system, the $Z$-axis is opposite to the unit normal vector $\underline{\hat{n}}$.
-To find this transformation matrix, we use quaternions.
-
-\subsubsection{Procedure Varying n}
-{\color{red} Work in Progress, you can skip this} \\
-Given $n(x,y)$. Old coordinates: x,y,z. New coordinates u,v,w.
-\begin{enumerate}
-	\item Determine Coordinate Transformation according to \ref{subsubsec:rotmat}. \\
-	\item Transform Initial Position to new coordinates u,v  \\
-	\item Initiate n field in new coordinates u,v \\
-	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
-	\item Transform Refracted Rays to new coordinates u, v, w \\
-	\item  Runge-Kutta \\
-	\item  Obtain grad n = ( dn/du, dn/dv, dn/dw) \\
-	\item  Transform incoming rays back to coordinates x y z \\
-	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
-	\item Transform Final Positions to new old coordinates x, y, z \\
-\end{enumerate}
 
@@
 		\centering \includegraphics[width = \textwidth]{leastsquaresbc.png}
-		\caption{$\log_{10}S(b,c)$}\label{fig:Sac}
+		\caption{$\log_{10}S(b,c)$}\label{fig:Sbc}
 \end{figure}
@@
 
-\section{Gladstone-Dale vs Lorentz-Lorenz}
-
 \section{Digital Image Correlation}
@@
 \begin{enumerate}
-	\item $\underline{\alpha}$, the parameters of our experimental setup (after calibration), \\
-	\item $\underline{x}$, the coordinates on our ccd-sensor, \\
-	\item $\underline{\Delta x}$, the measured displacement (after DIC), \\
+	\item $\underline{\alpha}$, the parameters of our experimental setup (after calibration), 
+	\item $\underline{x}$, the coordinates on our ccd-sensor, 
+	\item $\underline{\Delta x}$, the measured displacement (after DIC), 
 	\item $n_0$, the index of refraction of the reference state.
@@
 with constraints $1.333 \leq n_i \leq 1.4$. For each measurement $\underline{\Delta x}_i$ we solve (\ref{eq:nmin}) to find $n_i$.
-\section{Experimental Procedure}
-Calibration
+
 \section{Results}
@@
 Figure \ref{fig:ndeformed0side} shows the index of refraction field $n$.
+The expected theoretical density profile is an error function.
+We see this in Figure \ref{fig:ndeformed0side}.
 
-\subsection{Background Density}
-\label{subsec:bacden}
 \begin{figure}[htbp]
@@
 After calibration, the resulting $n$-field is uniform (\ref{fig:ncalibration0side}).
-Applying DIC between the Reference Image and the Correlation Image, we find the displacements $\Delta x$ (\ref{fig:dx0side}) and $\Delta y$ (\ref{fig:dy0side}) with corresponding Correlation Coefficient (\ref{fig:C0side}).
+Applying DIC between the Reference Image and the Deformed Image, we find the displacements $\Delta x$ (\ref{fig:dx0side}) and $\Delta y$ (\ref{fig:dy0side}) with corresponding Correlation Coefficient (\ref{fig:C0side}).
 Using these displacements in (\ref{eq:nmin}), we obtain the unknown index of refraction field $n$ (\ref{fig:ndeformed0side}).}
@@
 
-In the second application, in Reference,
+In the second application, in Reference, we want to measure the background density of a continuously stratified fluid.
+We filled a tank through the double bucket method.
+After taking a Reference Image, a Calibration Image and a Deformed Image, we repositioned the camera for a Synthetic Schlieren measurement.
+After oscillating the tank, we measured the angles of the internal waves propagating in the fluid.
+Table Reference shows the forcing frequencies $\omega$ and angles $\beta$.
+Through
+\begin{equation}
+	N = \omega \cos \beta
+\end{equation}
+we determined the buoyancy frequency $N$, obtained from Synthetic Schlieren. Through
+\begin{equation}
+	N^2 = - \frac{g}{\rho_0}\frac{d \rho_0}{d z}
+\end{equation}
+we determined the buoyancy frequency $N$, obtained from our new method.
+
+\begin{figure}[htbp]
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:strat0side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+		\subcaption{Correlation Coefficient from DIC}\label{fig:stratC0side}
+\end{subfigure} \\
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{$\Delta x$ from DIC}\label{fig:stratdx0side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+		\subcaption{$\Delta y$ from DIC}\label{fig:stratdy0side}
+\end{subfigure}\\
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{Index of Refraction $n$ for Deformed Image}\label{fig:stratndeformed0side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{Background Density $\rho_0$ for Deformed Image}\label{fig:stratrho0deformed0side}
+\end{subfigure}
+\caption{Determining the background density for a continuously stratified fluid.
+After taking three images, with the Deformed Image \ref{fig:strat0side}, we obtain the displacements $\Delta x$ in Figure \ref{fig:stratdx0side} and $\Delta y$ in Figure \ref{fig:stratdy0side} from DIC.
+After calibration we obtain the index of refraction field $n$ in Figure \ref{fig:stratndeformed0side}.
+Using the Lorentz-Lorenz relation we obtain the density profile \ref{fig:stratrho0deformed0side} with buoyancy frequency $N$ of NUMBER.
+}
+\label{figs:strat0side}
+\end{figure}
+
+In the third application, we measured the density field of a wave attractor \cite{maas1997observation}.
+Figure \ref{figs:WA0side} shows the measured density fields over one period of a (1,1) Wave Attractor.
+\begin{figure}[htbp]
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{0}\label{fig:WA0side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+		\subcaption{P/6}\label{fig:WA6side}
+\end{subfigure} \\
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{P/3}\label{fig:WA3side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+		\subcaption{P/2}\label{fig:WA2side}
+\end{subfigure} \\
+\begin{subfigure}{.5\linewidth}
+%		\centering \includegraphics[width = \textwidth]{}
+		\subcaption{2P/3}\label{fig:WA23side}
+\end{subfigure}%
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+		\subcaption{5P/6}\label{fig:WA56side}
+\end{subfigure} 
+\caption{Density Fields over one period of a Wave Attractor. The forcing frequency was NUMBER. }
+\label{figs:WA0side}
+\end{figure}
 
@@
 
-\appendix
+%\appendix
 
-\section{Runge-Kutta Scheme}
-\label{app:RKS}
-We choose a step size $h$. These are steps over the arc-length $s$. We use an index $p$ to indicate each step: $s^{p+1} = s^{p} + h$.
+%\section{Runge-Kutta Scheme}
+%\label{app:RKS}
+%We choose a step size $h$. These are steps over the arc-length $s$. We use an index $p$ to indicate each step: $s^{p+1} = s^{p} + h$.
+
+%\subsubsection{Rotation Matrix}
+%\label{subsubsec:rotmat}
+%{\color{red} Work in Progress, you can skip this} \\
+%A rotation through an angle of $\theta$ around an axis defined by the unit vector $\underline{\hat{r}} = r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}}$ can be represented by a quaternion
+%\begin{equation}
+%	\underline{q} = \cos\frac{\theta}{2} + (r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}} ) \sin \frac{\theta}{2}.
+%\end{equation} 
+%A unit quaternion has norm one. The rotation matrix $Q$ for a unit quaternion $\underline{q} = q_0 + q_1 \underline{\hat{i}} + q_2 \underline{\hat{j}} + q_3 \underline{\hat{k}}$ is
+%\begin{equation}
+%	Q = \left[ \begin{array}{ccc} 1-2(q_2^2+q_3^2) & 2(q_1 q_2 - q_0 q_3) & 2(q_1 q_3 + q_0 q_2) \\ 2 (q_1 q_2 + q_0 q_3) & 1-2(q_1^2+q_3^2) & 2( q_2 q_3 - q_0 q_1) \\ 2(q_1 q_3-q_0 q_2) & 2 (q_2 q_3 + q_0 q_1) & 1 - 2 (q_1^2+q_2^2) \end{array} \right]
+%\end{equation}
+
+%The rotation angle is
+%\begin{equation}
+%	\cos \theta = a \cdot 0 + b \cdot 0 + c \cdot 1
+%\end{equation}
+%and the rotation vector
+%\begin{equation}
+%	\underline{\hat{r}} = - \frac{b}{\sqrt{a^2+b^2}} \underline{\hat{i}} + \frac{a}{\sqrt{a^2+b^2}}  \underline{\hat{j}} + 0  \underline{\hat{k}}.
+%\end{equation}
+
+%\subsubsection{Intersection Light Rays and Planes: Inhomogeneous medium}
+%{\color{red} Work in Progress, you can skip this} \\
+%A light ray traveling through an inhomogeneous medium does not travel in a straight line.
+The path is governed by (\ref{eq:sys6foeq}).
+To simplify (\ref{eq:sys6foeq}), we can use that there is a direction in the experimental setup that has no variation in index of refraction $n$, which is the direction of the unit normal of the different planes.
+To use this simplification, we want to transform our direction cosines in our original coordinate system, $xyz$ into direction cosines in a new coordinate system, $XYZ$.
+In this new coordinate system, the $Z$-axis is opposite to the unit normal vector $\underline{\hat{n}}$.
+To find this transformation matrix, we use quaternions.
+
+%\subsubsection{Procedure Varying n}
+%{\color{red} Work in Progress, you can skip this} \\
+%Given $n(x,y)$. Old coordinates: x,y,z. New coordinates u,v,w.
+%\begin{enumerate}
+%	\item Determine Coordinate Transformation according to \ref{subsubsec:rotmat}. \\
+%	\item Transform Initial Position to new coordinates u,v  \\
+%	\item Initiate n field in new coordinates u,v \\
+%	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
+%	\item Transform Refracted Rays to new coordinates u, v, w \\
+%	\item  Runge-Kutta \\
+%	\item  Obtain grad n = ( dn/du, dn/dv, dn/dw) \\
+%	\item  Transform incoming rays back to coordinates x y z \\
+%	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
+%	\item Transform Final Positions to new old coordinates x, y, z \\
+%\end{enumerate}
 

### 2020-02-07 Article/articleBOS.tex
Small Corrections

@@
 \usepackage{enumitem}
-%\overfullrule=5pt
 \setlist{nosep}
+
 \usepackage{tikz}
@@
 \section{Introduction}
+Synthetic Schlieren \cite{dalziel2000whole} is used to obtain density gradient fields of stratified flows.
+Density fields can be obtained indirectly by Synthetic Schlieren, by solving a Poisson equation.
+
+The two critical steps are: (1) To view the experimental setup under an angle and (2) To calibrate our model.
 
@@
 %\label{eq:snelllaw}
-%n_0 \sin \theta_x = n_1 \sin \theta_2.
+%n_0 \sin \theta_x = n_1 \sin \theta_T.
 %\end{equation}
@@
 \subsubsection{Snell's Law}
-To find the angle of incidence, $\theta_1$, between the incoming light ray and the plane, we compute
+To find the angle of incidence, $\theta_I$, between the incoming light ray and the plane, we compute
 \begin{equation}
-	\cos \theta_1 = \underline{\hat{n}} \cdot \underline{I}.
+	\cos \theta_I = \underline{\hat{n}} \cdot \underline{I}.
 \end{equation}
-We apply Snell's law (\ref{eq:snellslaw}) to find the angle of refraction, $\theta_2$.
+We apply Snell's law (\ref{eq:snellslaw}) to find the angle of refraction, $\theta_T$.
 The index of refraction of the medium through which the incoming ray travels is $n_I$, the index of refraction of the medium through wich the outgoing ray travels is $n_T$.
@@
 \begin{align}
-	S &= \sign \cos \theta_1, \\
-	\sin \theta_2 &= \frac{n_I}{n_T} \sqrt{1-\cos^2 \theta_1}, \\
-	\cos \theta_2 &= \sqrt{1-\left(\frac{n_I}{n_T}\right)^2(1-\cos^2 \theta_1)} \\
-	\underline{T} &= \frac{n_I}{n_T} \underline{I} + \left(\frac{n_I}{n_T} \cos \theta_1 - S \cos\theta_2\right)\underline{\hat{n}},	
+	S &= \sign \cos \theta_I, \\
+	\sin \theta_T &= \frac{n_I}{n_T} \sqrt{1-\cos^2 \theta_I}, \\
+	\cos \theta_T &= \sqrt{1-\left(\frac{n_I}{n_T}\right)^2(1-\cos^2 \theta_I)} \\
+	\underline{T} &= \frac{n_I}{n_T} \underline{I} + \left(\frac{n_I}{n_T} \cos \theta_I - S \cos\theta_T\right)\underline{\hat{n}},	
 \end{align}
-where $S$, the sign of $\cos\theta_1$ ensures we stay in the right quadrant.
+where $S$, the sign of $\cos\theta_I$ ensures we stay in the right quadrant.
 
@@
 \label{eq:calmin} 
-\min_{\underline{\alpha}}  S = \min_{\underline{\alpha}} \sum_i w_i X_{j}(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i)^2, 
+\min_{\underline{\alpha}}  S = \min_{\underline{\alpha}} \sum_i w_i \left(X_{j}(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i)\right)^2,
 \end{equation}
@@
 \clearpage
-%\begin{figure}[htbp]
-%	\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{leastsquaresab.png}
-%		\subcaption{$S(a,b)$}\label{fig:Sab}
-%	\end{subfigure}%
-%	\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{leastsquaresac.png}
-%	\subcaption{$S(a,c)$}\label{fig:Sac}
-%	\end{subfigure}\\
-%	\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{leastsquaresad.png}
-%	\subcaption{$S(a,d)$}\label{fig:SaLm}
-%	\end{subfigure}%
-%	\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{leastsquaresbc.png}
-%		\subcaption{$S(b,c)$}\label{fig:Sac}
-%	\end{subfigure}\\
-%	\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{leastsquaresbd.png}
-%	\subcaption{$S(b,d)$}\label{fig:SbLm}
-%	\end{subfigure}%
-%	\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{leastsquarescd.png}
-%		\subcaption{$S(c,d)$}\label{fig:ScLm}
-%	\end{subfigure}
-%	\caption{Calibration: $S$ as a function of $\underline{\alpha}$.}
-%	\label{fig:cal}
-%\end{figure}
 
@@
 To attain sub-pixel accuracy we interpolate our images with B-splines \cite{thevenaz2000interpolation, unser1999splines, thevenaz2000image}.
-To obtain the deformations we optimize a Correlation Coefficient [SOURCE].
+To obtain the deformations we optimize a Correlation Coefficient, the ZNSSD [SOURCE].
 We solve this nonlinear least-squares problem  by (1) providing an initial guess and (2) solving an iterative scheme.
@@
 		\subcaption{Correlation Coefficient from DIC}\label{fig:C0side}
+\end{subfigure} \\
+\begin{subfigure}{.5\linewidth}
+%	\centering \includegraphics[width = \textwidth]{}
+		\subcaption{$n$ profiles for Calibration and Deformed Images}\label{fig:nprofiles0side}
 \end{subfigure}
@@
 Applying DIC between the Reference Image and the Deformed Image, we find the displacements $\Delta x$ (\ref{fig:dx0side}) and $\Delta y$ (\ref{fig:dy0side}) with corresponding Correlation Coefficient (\ref{fig:C0side}).
-Using these displacements in (\ref{eq:nmin}), we obtain the unknown index of refraction field $n$ (\ref{fig:ndeformed0side}).}
+Using these displacements in (\ref{eq:nmin}), we obtain the unknown index of refraction field $n$ (\ref{fig:ndeformed0side}).
+Horizontally averaging the index of refraction fields $n$ yields the profiles in \ref{fig:nprofiles0side}.}
 \label{fig:0side}

### 2020-02-10 Article/articleBOS.tex
Refractometer

@@
 \section{Introduction}
+
 Synthetic Schlieren \cite{dalziel2000whole} is used to obtain density gradient fields of stratified flows.
@@
 
-Since we are working with fluids we use the Lorentz-Lorenz equation to relate the index of refraction $n$ to the density $\rho$,
+Since we are working with fluids we use the Lorentz-Lorenz equation to relate the index of refraction $n$ to the density $\rho$ \cite{lorentz1916theory, tan2015dependence},
 \begin{equation}
@@
 To attain sub-pixel accuracy we interpolate our images with B-splines \cite{thevenaz2000interpolation, unser1999splines, thevenaz2000image}.
-To obtain the deformations we optimize a Correlation Coefficient, the ZNSSD [SOURCE].
+To obtain the deformations we optimize a Correlation Coefficient, the ZNSSD \cite{sutton2009image}.
 We solve this nonlinear least-squares problem  by (1) providing an initial guess and (2) solving an iterative scheme.
 As an initial guess we perform Template Matching \cite{lewis1995industrial,opencv_library} on a limited set of points to obtain rigid deformations with pixel accuracy.
-After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{pan2012incremental} to determine the initial guesses.
+After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{pan2012incremental} with a propagation function \cite{zhou2012propagation} to determine the initial guesses.
 As iterative scheme we use the Levenberg–Marquardt algorithm.
+
+\begin{table}[htbp]
+\caption{Digital Image Correlation }
+\label{tab:esterrmagn}
+\centering
+\begin{tabular}{ll}
+Noise & \\
+Subset Size & \\
+Grid Size 	& \\
+Measurements Points & \\
+Total Number of Images & \\
+Number of Averaged Images & \\
+Displacements & \\
+\qquad Spatial Resolution & x pixels, x mm \\
+\qquad Resolution & x pixels (x mm) \\
+Index of Refraction & \\
+\qquad Smoothing Method & \\
+\qquad Resolution & x \\
+\end{tabular}
+\end{table}
+
+Table \ref{tab:esterrmagn} shows the typical DIC parameters used in our experiments. Additionally, the accuracy of the obtained displacements is given.
 
@@
 \section{Results}
-In this section we show three applications of the new method: (1) A static two-layer fluid with large nonlinear deformations, (2) A static stratified fluid and (3) a dynamic fluid with wave attractor.
+In this section we show three applications of the new method: (1) A static two-layer fluid with large nonlinear deformations, (2) A static stratified fluid and (3) a dynamic fluid/flow?
+with wave attractor.
 
 In the first application, in \ref{fig:0side}, we want to measure the background density of a two-layer fluid system.
-We filled the bottom half of a tank with Wadden Sea water (with an index of refraction of 1.338, measured by a refractometer) and the upper half of the tank with tap water (with an index of refraction of 1.333, also measured by the refractometer).
+We filled the bottom half of a tank with Wadden Sea water (with an index of refraction of 1.338) \footnote{Measured by a refractometer: The Atago Urine Specific Gravity Refractometer with a refractive index range of 1.333-1.356 and a resolution of 0.0005.} and the upper half of the tank with tap water (with an index of refraction of 1.333).
 We kept the interface between the two layers sharp by filling the upper half of the tank through a sponge.

### 2020-02-11 Article/articleBOS.tex
Introductie

@@
 \section{Introduction}
+The Background Oriented Schlieren technique (BOS) is an optical density visualization technique \cite{meier2002computerized,raffel2015background}.
+First described in \cite{dalziel2000whole}, where it was called Synthetic Schlieren (SS).
+This technique provides whole-field measurements of density gradients.
+One of the strengths of this technique was the simplicity of the experimental setup.
+Parts of the traditional, more extensive optical setups were replaced by digital image analysis.
 
-Synthetic Schlieren \cite{dalziel2000whole} is used to obtain density gradient fields of stratified flows.
-Density fields can be obtained indirectly by Synthetic Schlieren, by solving a Poisson equation.
+In a typical BOS or SS application, we image perturbations, or waves, traveling through a fluid.
+Two or more images are compared using Digital Image Correlation (DIC) [refs].
+This comparison yields the displacements between the images.
+These displacements are related to the changes in the gradients of the index of refraction using a ray tracing model.
+These gradients of the index of refraction are related to the gradients of the density by experimentally determined data [refs], by the Gladstone-Dale relation for gases [refs] or by the Lorentz-Lorenz equation for liquids [refs].
+The density field is sometimes obtained from the gradients of the density perturbations by solving a Poisson equation [refs].
 
-The two critical steps are: (1) To view the experimental setup under an angle and (2) To calibrate our model.
+In this paper we present a modification to the BOS or SS technique to directly measure the density field.
+We take images of static situations:  (1) before filling a tank in the experimental setup with (stratified) fluids, (2) after filling the tank with a calibration fluid and (3) after filling the tank with (stratified) fluids.
+Then we take images of the dynamic situations: we image, as in BOS or SS, the perturbations, or waves, traveling through a fluid.
+We perform DIC to obtain displacements between the static images.
+Using a ray tracing model we relate these displacements to the index of refraction.
+These static images give us the background index of refraction.
+We also perform DIC to obtain the displacements between the dynamic images and a static image.
 
-Since we are working with fluids we use the Lorentz-Lorenz equation to relate the index of refraction $n$ to the density $\rho$ \cite{lorentz1916theory, tan2015dependence},
-\begin{equation}
- 	\frac{n^2-1}{n^2+2} \frac{1}{\rho} = \mbox{ constant}.
-\end{equation}
+The challenge of this new method was to have enough accuracy in our measurements and models to ensure that our results were useful.
+Determining the value of the density is more sensitive to noise than determining the density gradients of perturbations in a BOS or SS application.
+We also wanted to preserve the experimental simplicity of the BOS or SS method.
+In Section \ref{sec:simmod} we perform a naive application of the BOS or SS technique to try to measure the index of refraction of homogeneous water.
+We analyze a simple ray tracing model to determine why our naive approach failed.
+We show that light rays, traveling from the background through the fluid to the camera, should not travel in nearly straight lines (as in BOS or SS) but should have large deflections.
+We should either rotate the fluid tank or rotate (and move) our camera.
+We should not be placing our camera right in front of the fluid tank.
+
+To obtain the required accuracy in determining the density field we optimized all the steps in our method.
+In Section \ref{sec:formod} we derive our ray tracing model relating displacements to the index of refraction.
+We call this our forward model: given an index of refraction field and experimental parameters, we can compute the displacement field of our experimental setup.
+This ray tracing model is a 3D model that allows the camera to be placed under an angle with respect to the fluid tank.
+In Section \ref{sec:cal} we describe our calibration procedure.
+This calibration step allows us to determine very accurately certain parameters in our forward model.
+In Section \ref{sec:DIC} we discuss DIC.
+We provide references to papers that discuss techniques that allowed us to get the most of our DIC procedure.
+We also provide information about our settings for a typical DIC calculation.
+In Section \ref{sec:exp} we briefly discuss the experimental setup.
+We also discuss best practices to get the most out of our experiments.
+In Section \ref{sec:invmod} we discuss how to solve our inverse model: how to obtain the index of refraction from the experimentally obtained displacements and our forward model.
+
+The two novel critical steps are: (1) To view the experimental setup under an angle and (2) To calibrate our model.
 
 \section{Simple Model}
+\label{sec:simmod}
 Consider the experimental set up as shown in Figure \ref{fig:schviepalira}.
@@
 \section{Forward Model}
+\label{sec:formod}
 In this section we build a forward model, relating an index of refraction field $n$, position on the ccd-sensor $\underline{x}$ and parameters $\underline{\alpha}$ to the coordinates $\underline{X}$ where the light rays hits the screen.
@@
 \section{Calibration}
+\label{sec:cal}
 In our forward model in Section \ref{subsec:RayPath}, we have used the parameters describing a plane $a$, $b$ and $c$ and $L_m$.
@@
 \section{Digital Image Correlation}
+\label{sec:DIC}
 Digital Image Correlation (DIC) is a well known technique \cite{sutton2009image} to obtain deformation maps from images.
@@
 \section{Experimental}
+\label{sec:exp}
 Best practices to get good quality images
@@
 \section{Inverse Model}
+\label{sec:invmod}
 Looking at our Forward Model (\ref{eq:ForwardModel}), we know
@@
 with constraints $1.333 \leq n_i \leq 1.4$. For each measurement $\underline{\Delta x}_i$ we solve (\ref{eq:nmin}) to find $n_i$.
+
+Since we are working with liquids we use the Lorentz-Lorenz equation to relate the index of refraction $n$ to the density $\rho$ \cite{lorentz1916theory, tan2015dependence},
+\begin{equation}
+ 	\frac{n^2-1}{n^2+2} \frac{1}{\rho} = \mbox{ constant}.
+\end{equation}
 
@@
 
+\begin{table}[htbp]
+\caption{Angles $\beta$ of internal wave beams as a function of the forcing frequency $\omega$. These were determined by a Synthetic Schlieren setup.}
+\label{tab:SSintwav}
+\centering
+\begin{tabular}{llllll}
+$\omega$ & 1 & 1 & 1 & 1 & 1  \\
+$\beta$  & 1 & 1 & 1 & 1 & 1
+\end{tabular}
+\end{table}
+
 In the second application, in Reference, we want to measure the background density of a continuously stratified fluid.
@@
 After oscillating the tank, we measured the angles of the internal waves propagating in the fluid.
-Table Reference shows the forcing frequencies $\omega$ and angles $\beta$.
+Table \ref{tab:SSintwav} shows the forcing frequencies $\omega$ and angles $\beta$.
 Through
@@
 
+Same experimental equipment as BOS or SS - Can apply this method. All complexity is in the image analysis. \\
+
+Need to say something about paraxial approximation
+
 \printbibliography[heading=bibintoc]

### 2020-02-12 Article/LaTeX_DL_468198_240419/experimentsInFluids.tex
Journal Format

--- 2020-02-11 Article/articleBOS.tex
@@
-\documentclass{article}
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a general template file for the LaTeX package SVJour3
+% for Springer journals.          Springer Heidelberg 2010/09/16
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article. Delete % signs as needed.
+%
+% This template includes a few options for different layouts and
+% content for various journals. Please consult a previous issue of
+% your journal as needed.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\RequirePackage{fix-cm}
+%
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
+%
+\usepackage{graphicx}
+%
+% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
+%
+% insert here the call for the packages your document requires
+%\usepackage{latexsym}
 \usepackage{amsmath}
 \usepackage{amssymb}
-\DeclareMathOperator{\sign}{sign}
 \usepackage{geometry}
@@
 \addbibresource{articleBOS.bib}
+% etc.
+%
+% please place your own definitions here and don't use \def but
+% \newcommand{}{}
+\DeclareMathOperator{\sign}{sign}
+%
+% Insert the name of "your journal" with
+% \journalname{myjournal}
+%
 \begin{document}
-\today
-\section{Abstract}
+
+\title{Insert your title here%\thanks{Grants or other notes
+%about the article that should go on the front page should be
+%placed here. General acknowledgments should be placed at the end of the article.}
+}
+\subtitle{Do you have a subtitle?\\ If so, write it here}
+
+%\titlerunning{Short form of title}        % if too long for running head
+
+\author{Alexander M. van Oers \and
+       Leo R.M. Maas %etc.
+}
+
+%\authorrunning{Short form of author list} % if too long for running head
+
+\institute{Alexander M. van Oers \at
+              first address \\
+              Tel.: +123-45-678910\\
+              Fax: +123-45-678910\\
+              \email{fauthor@example.com}           %  \\
+%             \emph{Present address:} of F. Author  %  if needed
+           \and
+           Leo R.M. Maas \at
+              second address
+}
+
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
+
+\maketitle
+
+\begin{abstract}
+Insert your abstract here. Include keywords, PACS and mathematical
+subject classification numbers as needed.
+\keywords{First keyword \and Second keyword \and More}
+% \PACS{PACS code1 \and PACS code2 \and more}
+% \subclass{MSC code1 \and MSC code2 \and more}
+\end{abstract}
 
 \section{Introduction}
+\label{intro}
 The Background Oriented Schlieren technique (BOS) is an optical density visualization technique \cite{meier2002computerized,raffel2015background}.
@@
 
+\begin{acknowledgements}
+If you'd like to thank anyone, place your comments here
+and remove the percent signs.
+\end{acknowledgements}
+
+\section*{Funding}
+
+\section*{Availability of data and material}
+
+\section*{Code availability}
+% Authors must disclose all relationships or interests that 
+% could have direct or potential influence or impart bias on 
+% the work: 
+%
+ \section*{Conflict of interest}
+ The authors declare that they have no conflict of interest.
+
 \printbibliography[heading=bibintoc]
+% BibTeX users please use one of
+%\bibliographystyle{spbasic}      % basic style, author-year citations
+%\bibliographystyle{spmpsci}      % mathematics and physical sciences
+%\bibliographystyle{spphys}       % APS-like style for physics
+%\bibliography{}   % name your BibTeX data base
 
-%\appendix
-
-%\section{Runge-Kutta Scheme}
-%\label{app:RKS}
-%We choose a step size $h$. These are steps over the arc-length $s$. We use an index $p$ to indicate each step: $s^{p+1} = s^{p} + h$.
-
-%\subsubsection{Rotation Matrix}
-%\label{subsubsec:rotmat}
-%{\color{red} Work in Progress, you can skip this} \\
-%A rotation through an angle of $\theta$ around an axis defined by the unit vector $\underline{\hat{r}} = r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}}$ can be represented by a quaternion
-%\begin{equation}
-%	\underline{q} = \cos\frac{\theta}{2} + (r_x \underline{\hat{i}} + r_y \underline{\hat{j}} + r_z \underline{\hat{k}} ) \sin \frac{\theta}{2}.
-%\end{equation} 
-%A unit quaternion has norm one. The rotation matrix $Q$ for a unit quaternion $\underline{q} = q_0 + q_1 \underline{\hat{i}} + q_2 \underline{\hat{j}} + q_3 \underline{\hat{k}}$ is
-%\begin{equation}
-%	Q = \left[ \begin{array}{ccc} 1-2(q_2^2+q_3^2) & 2(q_1 q_2 - q_0 q_3) & 2(q_1 q_3 + q_0 q_2) \\ 2 (q_1 q_2 + q_0 q_3) & 1-2(q_1^2+q_3^2) & 2( q_2 q_3 - q_0 q_1) \\ 2(q_1 q_3-q_0 q_2) & 2 (q_2 q_3 + q_0 q_1) & 1 - 2 (q_1^2+q_2^2) \end{array} \right]
-%\end{equation}
-
-%The rotation angle is
-%\begin{equation}
-%	\cos \theta = a \cdot 0 + b \cdot 0 + c \cdot 1
-%\end{equation}
-%and the rotation vector
-%\begin{equation}
-%	\underline{\hat{r}} = - \frac{b}{\sqrt{a^2+b^2}} \underline{\hat{i}} + \frac{a}{\sqrt{a^2+b^2}}  \underline{\hat{j}} + 0  \underline{\hat{k}}.
-%\end{equation}
-
-%\subsubsection{Intersection Light Rays and Planes: Inhomogeneous medium}
-%{\color{red} Work in Progress, you can skip this} \\
-%A light ray traveling through an inhomogeneous medium does not travel in a straight line.
-The path is governed by (\ref{eq:sys6foeq}).
-To simplify (\ref{eq:sys6foeq}), we can use that there is a direction in the experimental setup that has no variation in index of refraction $n$, which is the direction of the unit normal of the different planes.
-To use this simplification, we want to transform our direction cosines in our original coordinate system, $xyz$ into direction cosines in a new coordinate system, $XYZ$.
-In this new coordinate system, the $Z$-axis is opposite to the unit normal vector $\underline{\hat{n}}$.
-To find this transformation matrix, we use quaternions.
-
-%\subsubsection{Procedure Varying n}
-%{\color{red} Work in Progress, you can skip this} \\
-%Given $n(x,y)$. Old coordinates: x,y,z. New coordinates u,v,w.
-%\begin{enumerate}
-%	\item Determine Coordinate Transformation according to \ref{subsubsec:rotmat}. \\
-%	\item Transform Initial Position to new coordinates u,v  \\
-%	\item Initiate n field in new coordinates u,v \\
-%	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
-%	\item Transform Refracted Rays to new coordinates u, v, w \\
-%	\item  Runge-Kutta \\
-%	\item  Obtain grad n = ( dn/du, dn/dv, dn/dw) \\
-%	\item  Transform incoming rays back to coordinates x y z \\
-%	\item  Apply Snell's Law in old coordinates (x,y,z) using the new n(u,v) \\
-%	\item Transform Final Positions to new old coordinates x, y, z \\
-%\end{enumerate}
+% Non-BibTeX users please use
+%\begin{thebibliography}{}
+%
+% and use \bibitem to create references. Consult the Instructions
+% for authors for reference list style.
+%
+%\bibitem{RefJ}
+% Format for Journal Reference
+%Author, Article title, Journal, Volume, page numbers (year)
+% Format for books
+%\bibitem{RefB}
+%Author, Book title, page numbers. Publisher, place (year)
+% etc
+%\end{thebibliography}
 
 \end{document}
+% end of file template.tex

### 2020-02-12 Article/experimentsInFluids.tex
Journal Format

--- 2020-02-12 Article/LaTeX_DL_468198_240419/experimentsInFluids.tex
@@
 %
-%\documentclass{svjour3}                     % onecolumn (standard format)
+\documentclass[draft]{svjour3}                     % onecolumn (standard format)
 %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
 %\documentclass[twocolumn]{svjour3}          % twocolumn
@@
 \usepackage{amssymb}
-\usepackage{geometry}
+%\usepackage{geometry}
 \usepackage{subcaption}
-\usepackage{standalone}
-\usepackage{xcolor}
+
+%\usepackage{xcolor}
 \usepackage{enumitem}
 \setlist{nosep}
-
+\usepackage{footnote}
+%%%
+% Remove these when submitting
+% We can turn the standalone tikz figures into regular figure files
+%%%
+\usepackage{standalone}
 \usepackage{tikz}
@@
 
-\usepackage{footnote}
 \usepackage{csquotes}
@@
 % Insert the name of "your journal" with
-% \journalname{myjournal}
+ \journalname{Experiments in Fluids}
 %
@@
 
-\title{Insert your title here%\thanks{Grants or other notes
-%about the article that should go on the front page should be
-%placed here. General acknowledgments should be placed at the end of the article.}
+\title{Whole-field total density measurements by Digital Image Correlation
+\thanks{Grants or other notes
+about the article that should go on the front page should be
+placed here. }
 }
-\subtitle{Do you have a subtitle?\\ If so, write it here}
+
+%\subtitle{Do you have a subtitle?\\ If so, write it here}
 
@@
 \institute{Alexander M. van Oers \at
-              first address \\
-              Tel.: +123-45-678910\\
-              Fax: +123-45-678910\\
-              \email{fauthor@example.com}           %  \\
-%             \emph{Present address:} of F. Author  %  if needed
+             NIOZ Royal Netherlands Institute for Sea Research and Utrecht University, P.O. Box 59, 1790 AB Texel, The Netherlands \\
+             \emph{Present address:} Netherlands Defence Academy, The Netherlands  %  if needed
            \and
            Leo R.M. Maas \at
-              second address
+              Imau, Inst. for Marine and Atmospheric research Utrecht, Utrecht University, Princetonplein 5, 3584 CC, Utrecht, The Netherlands
 }
@@
 \begin{abstract}
-Insert your abstract here. Include keywords, PACS and mathematical
-subject classification numbers as needed.
+An optical method for the quantitative measurement of the total density field of two-dimensional stratified or homogeneous transparent fluids is presented.
+It is based on the Synthetic Schlieren method.
+Application of this method is illustrated by the determination of the static background density of a two-layer fluid and of a stratified fluid.
+Further aspects of the technique are illustrated by considering the dynamic total density field of a wave attractor in a stratified fluid.
 \keywords{First keyword \and Second keyword \and More}
@@
 
-In a typical BOS or SS application, we image perturbations, or waves, traveling through a fluid.
-Two or more images are compared using Digital Image Correlation (DIC) [refs].
+In a typical BOS or SS application, perturbations (waves) in a fluid contained in a tank are imaged.
+Two or more images are compared using Digital Image Correlation (DIC) \cite{sutton2009image}.
 This comparison yields the displacements between the images.
 These displacements are related to the changes in the gradients of the index of refraction using a ray tracing model.
-These gradients of the index of refraction are related to the gradients of the density by experimentally determined data [refs], by the Gladstone-Dale relation for gases [refs] or by the Lorentz-Lorenz equation for liquids [refs].
-The density field is sometimes obtained from the gradients of the density perturbations by solving a Poisson equation [refs].
+These gradients of the index of refraction are related to the gradients of the density by experimentally determined data (e.g.
+\cite{tan2015dependence}), by the Gladstone-Dale relation for gases \cite{born2013principles} or by the Lorentz-Lorenz equation for liquids \cite{lorentz1916theory}.
+The density field is sometimes obtained from the gradients of the density perturbations by solving a Poisson equation \cite{venkatakrishnan2004density, verso2015background}.
 
@@
 These static images give us the background index of refraction.
-We also perform DIC to obtain the displacements between the dynamic images and a static image.
+We follow the same procedure for the dynamic images.
 
-The challenge of this new method was to have enough accuracy in our measurements and models to ensure that our results were useful.
+The challenge of this new method is to have enough accuracy in our measurements and models to ensure that our results are useful.
 Determining the value of the density is more sensitive to noise than determining the density gradients of perturbations in a BOS or SS application.
-We also wanted to preserve the experimental simplicity of the BOS or SS method.
+We also want to preserve the experimental simplicity of the BOS or SS method.
 In Section \ref{sec:simmod} we perform a naive application of the BOS or SS technique to try to measure the index of refraction of homogeneous water.
@@
 
-To obtain the required accuracy in determining the density field we optimized all the steps in our method.
+To obtain the required accuracy in determining the density field we optimize all the steps in our method.
 In Section \ref{sec:formod} we derive our ray tracing model relating displacements to the index of refraction.
@@
 In Section \ref{sec:cal} we describe our calibration procedure.
-This calibration step allows us to determine very accurately certain parameters in our forward model.
+This calibration determines accurately certain parameters in our forward model.
 In Section \ref{sec:DIC} we discuss DIC.
-We provide references to papers that discuss techniques that allowed us to get the most of our DIC procedure.
+We provide references to papers that discuss techniques that allow us to get the most of our DIC procedure.
 We also provide information about our settings for a typical DIC calculation.
@@
 In Section \ref{sec:invmod} we discuss how to solve our inverse model: how to obtain the index of refraction from the experimentally obtained displacements and our forward model.
-
-The two novel critical steps are: (1) To view the experimental setup under an angle and (2) To calibrate our model.
 
@@
 \begin{figure}[hpbt]
-	\includestandalone{schematicsetupangle}
+	\includestandalone[width=\textwidth]{schematicsetupangle}
 	\caption{A schematic view of a path of a light ray (not to scale).
@@
 where $n_i$ is the refractive index for the $i^{th}$ section. The position $x_6$ is
-\begin{align}
+%\begin{align}
+%\label{eq:simplex6}
+%x_6 (\theta_x, n_2) & =  (L_c+L_s) \tan \theta_x + 2 L_g \tan \arcsin \frac{n_0}{n_1} \sin \theta_x + L_t \tan \arcsin \frac{n_0}{n_2} \sin \theta_x \nonumber \\
+%& =  (L_c+L_s) \tan \theta_x + \frac{2 L_g n_0 \sin \theta_x}{\sqrt{n_1^2 - n_0^2 \sin^2 \theta_x}} + \frac{L_t n_0 \sin \theta_x}{\sqrt{n_2^2 - n_0^2 \sin^2 \theta_x}}.
+%\end{align}
+\begin{equation}
 \label{eq:simplex6}
-x_6 (\theta_x, n_2) & =  (L_c+L_s) \tan \theta_x + 2 L_g \tan \arcsin \frac{n_0}{n_1} \sin \theta_x + L_t \tan \arcsin \frac{n_0}{n_2} \sin \theta_x \nonumber \\
-& =  (L_c+L_s) \tan \theta_x + \frac{2 L_g n_0 \sin \theta_x}{\sqrt{n_1^2 - n_0^2 \sin^2 \theta_x}} + \frac{L_t n_0 \sin \theta_x}{\sqrt{n_2^2 - n_0^2 \sin^2 \theta_x}}.
-\end{align}
+x_6 (\theta_x, n_2) =  (L_c+L_s) \tan \theta_x + \frac{2 L_g n_0 \sin \theta_x}{\sqrt{n_1^2 - n_0^2 \sin^2 \theta_x}} + \frac{L_t n_0 \sin \theta_x}{\sqrt{n_2^2 - n_0^2 \sin^2 \theta_x}}.
+\end{equation}
 The displacement $\Delta x$ is the difference in position $x_6$ between the constant reference state, $n_2 = n_0$, and the unknown state $n_2=n$, 
-\begin{align}
+%\begin{align}
+%\label{eq:dexcon2}
+%\Delta x = x_6 (n_2 = n_0) - x_6 (n_2 = n) & = L_t \left[ \tan \theta_x - \tan \arcsin \frac{n_0}{n} \sin \theta_x\right] \nonumber \\
+%& = L_t \left[ \tan \theta_x - \frac{n_0 \sin \theta_x}{\sqrt{n^2 - n_0^2 \sin^2 \theta_x}} \right] .
+%\end{align}
+\begin{equation}
 \label{eq:dexcon2}
-\Delta x = x_6 (n_2 = n_0) - x_6 (n_2 = n) & = L_t \left[ \tan \theta_x - \tan \arcsin \frac{n_0}{n} \sin \theta_x\right] \nonumber \\
-& = L_t \left[ \tan \theta_x - \frac{n_0 \sin \theta_x}{\sqrt{n^2 - n_0^2 \sin^2 \theta_x}} \right] .
-\end{align}
+\Delta x = x_6 (n_2 = n_0) - x_6 (n_2 = n) = L_t \left( \tan \theta_x - \frac{n_0 \sin \theta_x}{\sqrt{n^2 - n_0^2 \sin^2 \theta_x}} \right) .
+\end{equation}
 Inverting this relation we obtain the unknown refractive index $n$ as a function of the displacement
@@
 \label{eq:invdexcon2}
-n = \frac{n_0 \sin \theta_x}{\sin \arctan \left( \tan \theta_x - \frac{\Delta x}{L_t} \right)} = \frac{n_0 \sin(\theta_x)}{\tan(\theta_x)-\frac{\Delta x}{L_t}} \sqrt{1+\left(\tan(\theta_x)-\frac{\Delta x}{L_t}\right)^2}.
+n =\frac{n_0 \sin(\theta_x)}{\tan(\theta_x)-\frac{\Delta x}{L_t}} \sqrt{1+\left(\tan(\theta_x)-\frac{\Delta x}{L_t}\right)^2}.
+% \frac{n_0 \sin \theta_x}{\sin \arctan \left( \tan \theta_x - \frac{\Delta x}{L_t} \right)} =
 \end{equation}
@@
 
-%The index of refraction of air $n_0$ is constant. The light ray hits the first glass plate with a position
-%\begin{equation}
-%\label{eq:tanlaw}
-%x_2 = L_c \tan \theta_x.
-%\end{equation}
-%The index of refraction of the glass plate $n_1$ is constant. The angle under which the light ray propagates changes instantaneously, obeying Snell's law
-%\begin{equation}
-%\label{eq:snelllaw}
-%n_0 \sin \theta_x = n_1 \sin \theta_T.
-%\end{equation}
-%For a constant index of refraction in the water tank $n_2$ the position $x_6$ is
-%\begin{equation}
-%x_6 (\theta_x, n_2) = (L_c+L_s) \tan \theta_x + 2 L_g \tan \arcsin \frac{n_0}{n_1} \sin \theta_x + L_t \tan \arcsin \frac{n_0}{n_2} \sin \theta_x
-%\end{equation}
-%The displacement $\Delta x$ is the difference in position $x_6$ for two different values of $n_2$. We take one known value, the %tank is filled with air, $n_0$, and one unknown value $n_2 = n$. 
-%\begin{equation}
-%\label{eq:dexcon2}
-%\Delta x = x_6 (n_2 = n_0) - x_6 (n_2 = n) = L_t \left[ \tan \theta_x - \tan \arcsin \frac{n_0}{n} \sin \theta_x\right].
-%\end{equation}
-%We can invert this relation to obtain the unknown $n$,
-%\begin{equation}
-%\label{eq:nfromdxsimple}
-%	n = \frac{n_0 \sin(\theta_x)}{\tan(\theta_x)-\frac{\Delta x}{L_t}} \sqrt{1+\left(\tan(\theta_x)-\frac{\Delta x}{L_t}\right)^2}.
-%\end{equation}
-
 Figure \ref{fig:simmod} shows the results when using (\ref{eq:invdexcon2}) to obtain the index of refraction $n$.
 We have two frontal images of the experimental setup; (1) Figure \ref{fig:air0simplefrontal}, without water, and (2) Figure \ref{fig:fresh0simplefrontal}, with water.
-Applying a Digital Image Correlation (DIC) method we obtain (1) the correlation coefficient, a measure of the reliability of the method, (2) the horizontal displacements $\Delta x$, and (3) the vertical displacements $\Delta y$.
-Where coordinates where $\Delta x = 0$ and $\Delta y = 0$ are the location of the $z-axis$.
+Applying DIC we obtain; Figure \ref{fig:CCsimplefrontal} the correlation coefficient, a measure of the reliability of the method; Figure \ref{fig:DXsimplefrontal} the horizontal displacements $\Delta x$; and (3) Figure \ref{fig:DYsimplefrontal} the vertical displacements $\Delta y$.
+Where $\Delta x = \Delta y = 0$ is the location of the $z$-axis.
 We calculate the angles $\theta_x$ and $\theta_y$ with respect to this $z$-axis.
@@
 \end{subfigure}
-\caption{Simple Model Result. When the angle $\theta_x$ is near zero, large errors in $n$ appear. }
+\caption{Simple Model Result.
+Applying DIC to the Reference Image in \ref{fig:air0simplefrontal} and the Deformed Image \ref{fig:fresh0simplefrontal} yields the Correlation Coefficient in \ref{fig:CCsimplefrontal}, the horizontal displacements in \ref{fig:DXsimplefrontal} and the vertical displacements in \ref{fig:DYsimplefrontal}.
+Using (\ref{eq:invdexcon2}) the index of refraction $n$ in \ref{fig:nfromdxsimplefrontal}, \ref{fig:nfromdysimplefrontal} and \ref{fig:nfrontal} are obtained.
+When the displacements $\Delta x$ and $\Delta y$ approach zero, large errors in $n$ appear.
+}
 \label{fig:simmod}
@@
 Figure \ref{fig:nfrontal} looks best, but is still unacceptable.
-Around the location of the $z-axis$, where the angles and displacements approach zero, the errors are very large.
+Around the location of the $z$-axis, where the angles and displacements approach zero, the errors are very large.
 The entire figure should have a constant value of $n = 1.333$.
@@
 The angle $\theta_x$ is replaced by $\alpha+\phi_x$, where $\phi_x$ is the angle of the light ray relative to the principal axis of the camera, which is at an angle $\alpha$.
-For example, we position our camera at an angle of $\alpha=30^\circ$ relative to the tank.
-The camera has a viewing range of $[-4,4]$ degrees.
+%For example, we position our camera at an angle of $\alpha=30^\circ$ relative to the tank.
+The camera has a viewing range of $[-4,4]^\circ$.
 Then $\phi_x$ varies from $-4^\circ$ to $4^\circ$.
@@
 The worst possible angles to measure at are $0^\circ$ and $90^\circ$.
-This minimum is reached at $31^\circ$.
-Any angle between $15^\circ$ and $60^\circ$ yields approximately the same sensitivity of $n$.
+The minimum is reached at $31^\circ$.
+Any angle between $15^\circ$ and $55^\circ$ yields approximately the same sensitivity of $n$.
 
@@
 
-%To reduce
+Concluding, Figures \ref{fig:dndx} and \ref{fig:dndt} indicate that the worst angles to measure are close to zero. Angles between $15^\circ$ and $55^\circ$ result in small errors in $n$.
 
-Concluding, Figures \ref{fig:dndx} and \ref{fig:dndt} indicate that the worst angles to measure are close to zero. Angles between $15^\circ$ and $60^\circ$ result in small errors in $n$.
-
-\clearpage 
 \section{Forward Model}
@@
 We seek a model $\underline{X}(n, \underline{\alpha}, \underline{x})$.
-This is an extension of (\ref{eq:simplex6}).
 
 In Subsection \ref{subsec:rayequ} we derive the equations governing 3-dimensional ray optics in an inhomogeneous medium.
-In Subsection \ref{subsec:RayPath} we use these equations to construct the full ray path from the camera through the tank to the screen.
+In Subsection \ref{subsec:RayPath} give a mathematical description of all the objects our light rays encounter.
+In Subsection \ref{subsec:dis} we construct the full ray path from the camera through the tank to the screen
 
@@
 	\begin{aligned}
-		\ddot{x}  &= \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial x} - \dot{x} \frac{\partial n}{\partial z} \right), \\
-		\ddot{y} &= \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial y} - \dot{y} \frac{\partial n}{\partial z} \right), \\
-		\frac{\partial n}{\partial z} &= \gamma \frac{d}{dz}\left(n  \gamma\right).
+		\ddot{x}  = \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial x} - \dot{x} \frac{\partial n}{\partial z} \right), \quad
+		\ddot{y} = \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial y} - \dot{y} \frac{\partial n}{\partial z} \right), \quad
+		\frac{\partial n}{\partial z} = \gamma \frac{d}{dz}\left(n  \gamma\right).
 	\end{aligned}
@@
 
-\subsection{Relating Refractive Index to Ray Path}
+\subsection{Mathematical description of Geometrical Objects}
 \label{subsec:RayPath}
@@
 \end{equation}
-where $\underline{\hat{n}} = (a,b,c)$ is the unit normal vector of the plane, $\underline{x}$ a random vector within the plane and $\underline{x}_0$ a random point on the plane.
+where $\underline{\hat{n}} = (a,b,c)$ is the unit normal vector of the plane, $\underline{x}$ a random vector within the plane and $\underline{x}_0=(x_0, y_0, z_0)$ a random point on the plane.
 Expanding (\ref{def:plane}) yields
-\begin{equation}
-	a(x-x_0) + b(y-y_0) + c(z-z_0) = 0, 
-\end{equation}
-or 
+%\begin{equation}
+%	a(x-x_0) + b(y-y_0) + c(z-z_0) = 0, 
+%\end{equation}
+%or 
 \begin{equation}
@@
 $L_s$, $L_g$, etc.
-Given the equation describing plane 6,
-\begin{equation}
-\label{eq:planedef6}
-	a x + b y + c z + d = 0,
-\end{equation}
+Given the equation describing plane 6, with $d=d_6$,
+%\begin{equation}
+%\label{eq:planedef6}
+%	a x + b y + c z + d = 0,
+%\end{equation}
 we can compute the equations describing the other planes
@@
 a x + b y + c z + d_i = 0, \qquad  
-& d_5 = d + (a+b+c) L_s, \\
+& d_5 = d + (a+b+c) L_s, \nonumber \\
 & ..., \nonumber \\ 
-& d_2 = d + (a+b+c) (L_s+2L_g+L_t), \\
+& d_2 = d + (a+b+c) (L_s+2L_g+L_t), \nonumber \\
 \label{eq:planedef1}
@@
 where $f$ is the focal length of the camera and $L_m$ is the distance from the pinhole to screen (plane 6) along the $z$-axis.
-This distance is found from (\ref{eq:planedef6}) for $x=y=0$.
+This distance is found from (\ref{eq:planedef2}) for $x=y=0$.
 Then $d = - c L_m$.
 
-The physical coordinates $x$ and $y$ are obtained from the pixel locations $x_p, y_p$, the pixel locations at $(x,y)=(0,0)$ $x_p^0$ and $y_p^0$ and the physical size of each pixel on the ccd-sensor.
-Assuming each pixel on the ccd-sensor is square, we call the physical size of each sensor $S^2$.
-$S$ has units $\mu m/pixel$.
+The physical coordinates $x$ and $y$ are obtained from the pixel locations $x_p, y_p$  and the physical size of each pixel on the ccd-sensor.
+Assuming each pixel on the ccd-sensor is square, we call the physical size of each sensor $S_p^2$.
+$S_p$ has units $\mu m/pixel$.
 The physical coordinates are then found from the pixel locations by
 \begin{equation}
-	x = S (x_p-x_p^0), \qquad  y = S (y_p-y_p^0).
+	x = S_p (x_p-x_p^0), \qquad  y = S_p (y_p-y_p^0),
 \end{equation}
+where $x_p^0$ and $y_p^0$ are the pixel locations at $(x,y)=(0,0)$.
 
@@
 \label{eq:directioncosines}
-	\alpha &= \cos \theta_x = \frac{x}{\sqrt{x^2+y^2+L_f^2}} \nonumber \\
-	\beta &= \cos \theta_y = \frac{y}{\sqrt{x^2+y^2+L_f^2}} \\
-	\gamma &= \cos \theta_z = \frac{L_f}{\sqrt{x^2+y^2+L_f^2}} \nonumber
+	\alpha = \cos \theta_x = \frac{x}{\sqrt{x^2+y^2+L_f^2}} &\qquad
+	\beta = \cos \theta_y = \frac{y}{\sqrt{x^2+y^2+L_f^2}} \\
+	\gamma = \cos \theta_z = &\frac{L_f}{\sqrt{x^2+y^2+L_f^2}} \nonumber
 \end{align}
@@
 \begin{align}
-	S &= \sign \cos \theta_I, \\
-	\sin \theta_T &= \frac{n_I}{n_T} \sqrt{1-\cos^2 \theta_I}, \\
-	\cos \theta_T &= \sqrt{1-\left(\frac{n_I}{n_T}\right)^2(1-\cos^2 \theta_I)} \\
-	\underline{T} &= \frac{n_I}{n_T} \underline{I} + \left(\frac{n_I}{n_T} \cos \theta_I - S \cos\theta_T\right)\underline{\hat{n}},	
+	S = \sign \cos \theta_I, &\qquad
+	\sin \theta_T = \frac{n_I}{n_T} \sqrt{1-\cos^2 \theta_I}, \\
+	\cos \theta_T = \sqrt{1-\left(\frac{n_I}{n_T}\right)^2(1-\cos^2 \theta_I)} &\qquad
+	\underline{T} = \frac{n_I}{n_T} \underline{I} + \left(\frac{n_I}{n_T} \cos \theta_I - S \cos\theta_T\right)\underline{\hat{n}},	
 \end{align}
@@
 \subsection{Displacements}
+\label{subsec:dis}
 Previous subsections combine to give the forward model: $\underline{X}(n,\underline{\alpha}, \underline{x})$.
 Given an index of refraction field $n$, parameters $\underline{\alpha}$ and coordinates $\underline{x} = (x,y)$, we can calculate the location on the screen where the light rays end up.
-$\underline{\alpha}$ are the parameters that define the planes $a$, $b$, $c$ and $L_m$.
+$\underline{\alpha}$ are the parameters that define the planes $a$, $b$, $c$ and the distance to the screen $L_m$.
 We use $L_m$ instead of $d$ since we want our parameters to be (linearly) independent.
@@
 \label{sec:cal}
-In our forward model in Section \ref{subsec:RayPath}, we have used the parameters describing a plane $a$, $b$ and $c$ and $L_m$.
+In our forward model in Section \ref{subsec:RayPath}, we have used the parameters $\underline{\alpha}$.
 However, when setting up a new experiment, these are not known.
@@
 The easiest is water without any salts.
-Performing DIC yields us the displacements $\Delta \underline{x}$.
+Performing DIC yields us the displacements $\underline{\Delta x}$.
 This allows us to determine the parameters $\underline{\alpha}.$
-
-In our simple model, this calibration is the equivalent of (\ref{eq:dexcon2}). We know $n$, $n_0$ and $\Delta x$ and we want to determine $\alpha$ (from $\theta_x = \alpha+\phi_x$).
 
@@
 \begin{enumerate}
-	\item $n=n_0$ and $n=n_1$, the index of refraction of reference image (filled with air) and the deformed image (filled with water); 
+	\item $n=n_0$ and $n=n_1$, the index of refraction of the reference image (filled with air) and the deformed image (filled with water); 
 	\item $\underline{x}$, the coordinates on our ccd-sensor; 
@@
 Since we have only four parameters to estimate and many measurements (each grid point yields a separate equation), we have an over-determined system.
-We use a least-squares approach to find those $\underline{\alpha}$ that minimize the sum of squares of the residuals.
-The forward model depends nonlinearly on the parameters $\alpha$ and the measurements $\underline{\Delta x}$.
+We use least-squares to find those $\underline{\alpha}$ that minimize the sum of squares of the residuals.
+The forward model depends nonlinearly on the parameters $\underline{\alpha}$ and the measurements $\underline{\Delta x}$.
 For each measurement $\underline{\Delta x}$ we have a measure of reliability, the correlation coefficient, which we use as a weight $w$ in the least squares procedure
@@
 \label{eq:calmin} 
-\min_{\underline{\alpha}}  S = \min_{\underline{\alpha}} \sum_i w_i \left(X_{j}(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i)\right)^2,
+	 \min_{\underline{\alpha}} \sum_i w_i \left(X_{j}(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i)\right)^2, 
 \end{equation}
@@
 Combining these constraints implies $d>0$.
-The sum is over all measured displacements.
-The weights $w_i$ are $0$ when $CC < 0.8$ and $1$ otherwise.
-We use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal.
+The sum is over all measured displacements.We use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal.
+% The weights $w_i$ are $0$ when $CC < 0.8$ and $1$ otherwise.
 
@@
 
-To find the best way to solve (\ref{eq:calmin}), Figures \ref{fig:Sab} to \ref{fig:ScLm} show $S$ as a function of $\underline{\alpha}$ for a typical experiment.
-For each figure, we have fixed two parameters of $\underline{\alpha}$ and varied the other two.
-The blue lines indicate the constraint $L_c >0$ and the red lines indicate the constraint $L_m \geq L_c + 2 L_g + L_t + L_s$.
-The black cross indicates the global minimum in the allowable region.
+We use the Levenberg-Marquardt(LM) algorithm to solve (\ref{eq:calmin}).
+Generally, (\ref{eq:calmin}) has one minimum that satisfies the constraints.
+When the initial condition satisfies these constraints, the LM algorithm will find this minimum.
 
-All figures show very nice behavior of $S$.
-Figures \ref{fig:Sab}, \ref{fig:Sac} and \ref{fig:SbLm} show one clear minimum in the allowed region.
-Figures \ref{fig:Sac}, \ref{fig:SaLm} and \ref{fig:ScLm} show one clear valley in the allowed region.
-
-It seems that when we choose an initial condition that falls in the permissible regions and use a gradient-based optimization scheme we will end up in the minimum.
-%Only one minimum exists in each of the permissible regions.
-
-\begin{figure}[htbp]
-		\centering \includegraphics[width = \textwidth]{leastsquaresab.png}
-		\caption{$\log_{10}S(a,b)$}\label{fig:Sab}
-\end{figure}
-\begin{figure}[htbp]
-		\centering \includegraphics[width = \textwidth]{leastsquaresac.png}
-		\caption{$\log_{10}S(a,c)$}\label{fig:Sac}
-\end{figure}
-\begin{figure}[htbp]
-		\centering \includegraphics[width = \textwidth]{leastsquaresad.png}
-		\caption{$\log_{10}S(a,d)$}\label{fig:SaLm}
-\end{figure}
-\begin{figure}[htbp]
-		\centering \includegraphics[width = \textwidth]{leastsquaresbc.png}
-		\caption{$\log_{10}S(b,c)$}\label{fig:Sbc}
-\end{figure}
-\begin{figure}[htbp]
-		\centering \includegraphics[width = \textwidth]{leastsquaresbd.png}
-		\caption{$\log_{10}S(b,d)$}\label{fig:SbLm}
-\end{figure}
-\begin{figure}[htbp]
-		\centering \includegraphics[width = \textwidth]{leastsquarescd.png}
-		\caption{$\log_{10}S(c,d)$}\label{fig:ScLm}
-\end{figure}
-
-\clearpage
+%\begin{figure}[htbp]
+%		\centering \includegraphics[width = \textwidth]{leastsquaresab.png}
+%		\caption{$\log_{10}S(a,b)$}\label{fig:Sab}
+%\end{figure}
+%\begin{figure}[htbp]
+%		\centering \includegraphics[width = \textwidth]{leastsquaresac.png}
+%		\caption{$\log_{10}S(a,c)$}\label{fig:Sac}
+%\end{figure}
+%\begin{figure}[htbp]
+%		\centering \includegraphics[width = \textwidth]{leastsquaresad.png}
+%		\caption{$\log_{10}S(a,d)$}\label{fig:SaLm}
+%\end{figure}
+%\begin{figure}[htbp]
+%		\centering \includegraphics[width = \textwidth]{leastsquaresbc.png}
+%		\caption{$\log_{10}S(b,c)$}\label{fig:Sbc}
+%\end{figure}
+%\begin{figure}[htbp]
+%		\centering \includegraphics[width = \textwidth]{leastsquaresbd.png}
+%		\caption{$\log_{10}S(b,d)$}\label{fig:SbLm}
+%\end{figure}
+%\begin{figure}[htbp]
+%		\centering \includegraphics[width = \textwidth]{leastsquarescd.png}
+%		\caption{$\log_{10}S(c,d)$}\label{fig:ScLm}
+%\end{figure}
 
@@
 We use second-order shape functions \cite{lu2000deformation} to handle large nonlinear deformations.
-To attain sub-pixel accuracy we interpolate our images with B-splines \cite{thevenaz2000interpolation, unser1999splines, thevenaz2000image}.
+To attain sub-pixel accuracy we interpolate our images with B-splines \cite{thevenaz2000interpolation, unser1999splines}.
 To obtain the deformations we optimize a Correlation Coefficient, the ZNSSD \cite{sutton2009image}.
@@
 After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{pan2012incremental} with a propagation function \cite{zhou2012propagation} to determine the initial guesses.
-As iterative scheme we use the Levenberg–Marquardt algorithm.
+As iterative scheme we use the LM algorithm.
 
 \begin{table}[htbp]
-\caption{Digital Image Correlation }
+\caption{Digital Image Correlation parameters.}
 \label{tab:esterrmagn}
@@
 Subset Size & \\
-Grid Size 	& \\
+Grid Size 	& 5 \\
 Measurements Points & \\
@@
 \qquad Spatial Resolution & x pixels, x mm \\
-\qquad Resolution & x pixels (x mm) \\
+\qquad Resolution & 0.0105 pixels (x mm) \\
 Index of Refraction & \\
@@
 \label{sec:exp}
-Best practices to get good quality images
+Best practices to get good quality images \cite{sutton2009image}
 
@@
 \label{eq:nmin} 
-\min_{n_i}  S = \min_{n_i} (X_{j}(n, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i))^2, 
+	\min_{n_i} (X_{j}(n_i, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i))^2, 
 \end{equation}
-with constraints $1.333 \leq n_i \leq 1.4$. For each measurement $\underline{\Delta x}_i$ we solve (\ref{eq:nmin}) to find $n_i$.
+with constraints $1.333 \leq n_i \leq 1.4$.
+For each measurement $\underline{\Delta x}_i$ we solve (\ref{eq:nmin}) to find $n_i$.
+We solve (\ref{eq:nmin}) with the LM algorithm.
+(\ref{eq:nmin}) has one minimum in the range $1.333 \leq n_i \leq 1.4$.
+Picking an initial condition in this range ensures LM finds this minimum.
 
@@
 \end{equation}
-
+We use our calibration measurement to determine the constant: $\rho=1$ for $n=1.333$.
 \section{Results}
@@
 
-In the first application, in \ref{fig:0side}, we want to measure the background density of a two-layer fluid system.
-We filled the bottom half of a tank with Wadden Sea water (with an index of refraction of 1.338) \footnote{Measured by a refractometer: The Atago Urine Specific Gravity Refractometer with a refractive index range of 1.333-1.356 and a resolution of 0.0005.} and the upper half of the tank with tap water (with an index of refraction of 1.333).
+In the first application, Figure \ref{fig:0side}, we measured the background density of a two-layer fluid system.
+We filled the bottom half of a tank with Wadden Sea water (with an index of refraction of 1.338)\footnote{Measured by a refractometer: The Atago Urine Specific Gravity Refractometer with a refractive index range of 1.333-1.356 and a resolution of 0.0005.} and the upper half of the tank with tap water (with an index of refraction of 1.333).
 We kept the interface between the two layers sharp by filling the upper half of the tank through a sponge.
@@
 
-In the second application, in Reference, we want to measure the background density of a continuously stratified fluid.
+In the second application, Figure \ref{fig:0side}, we measured the background density of a continuously stratified fluid.
 We filled a tank through the double bucket method.
@@
 \end{equation}
-we determined the buoyancy frequency $N$, obtained from Synthetic Schlieren. Through
+we determined the buoyancy frequency $N$. Through
 \begin{equation}
@@
 
-definition planes -> doesn't have to be parallel. in particular 6th plane can be different, extra parameters to estimate in $\alpha$ (calibration). \\
+definition planes -> doesn't have to be parallel. in particular 6th plane can be different, extra parameters to estimate in $\alpha$ (calibration). 
 non plane water tank: measure without tank, with tank with air -> (calibration) shape of tank, field $L_t$
@@
 
-Same experimental equipment as BOS or SS - Can apply this method. All complexity is in the image analysis. \\
+Same experimental equipment as BOS or SS - Can apply this method. All complexity is in the image analysis.
 
@@
 
+The two novel critical steps are: (1) To view the experimental setup under an angle and (2) To calibrate our model.
+
+Horizontal viewing $\Rightarrow \Delta x, \theta_x$ large. Use $X \Rightarrow \frac{\partial n}{\partial x} = 0$ in static situation.
 \begin{acknowledgements}
 If you'd like to thank anyone, place your comments here
-and remove the percent signs.
 \end{acknowledgements}
@@
 \section*{Funding}
+NWO
 
@@
 \section*{Code availability}
+
 % Authors must disclose all relationships or interests that 

### 2020-02-13 Article/LaTeX_DL_468198_240419/rayequationsderivation.tex
Der Simple n Combined

--- 2020-02-12 Article/experimentsInFluids.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% This is a general template file for the LaTeX package SVJour3
-% for Springer journals.          Springer Heidelberg 2010/09/16
-%
-% Copy it to a new file with a new name and use it as the basis
-% for your article. Delete % signs as needed.
-%
-% This template includes a few options for different layouts and
-% content for various journals. Please consult a previous issue of
-% your journal as needed.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\RequirePackage{fix-cm}
-%
-\documentclass[draft]{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
-\usepackage{graphicx}
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%\usepackage{geometry}
-\usepackage{subcaption}
-
-%\usepackage{xcolor}
-\usepackage{enumitem}
-\setlist{nosep}
-\usepackage{footnote}
-%%%
-% Remove these when submitting
-% We can turn the standalone tikz figures into regular figure files
-%%%
-\usepackage{standalone}
-\usepackage{tikz}
-\usetikzlibrary{patterns}
-\usetikzlibrary{decorations.pathreplacing}
-
-\usepackage{csquotes}
-\usepackage[USenglish]{babel}
-\usepackage[backend=biber]{biblatex}
-
-\addbibresource{articleBOS.bib}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-\DeclareMathOperator{\sign}{sign}
-%
-% Insert the name of "your journal" with
- \journalname{Experiments in Fluids}
-%
-\begin{document}
-
-\title{Whole-field total density measurements by Digital Image Correlation
-\thanks{Grants or other notes
-about the article that should go on the front page should be
-placed here. }
-}
-
-%\subtitle{Do you have a subtitle?\\ If so, write it here}
-
-%\titlerunning{Short form of title}        % if too long for running head
-
-\author{Alexander M. van Oers \and
-       Leo R.M. Maas %etc.
-}
-
-%\authorrunning{Short form of author list} % if too long for running head
-
-\institute{Alexander M. van Oers \at
-             NIOZ Royal Netherlands Institute for Sea Research and Utrecht University, P.O. Box 59, 1790 AB Texel, The Netherlands \\
-             \emph{Present address:} Netherlands Defence Academy, The Netherlands  %  if needed
-           \and
-           Leo R.M. Maas \at
-              Imau, Inst. for Marine and Atmospheric research Utrecht, Utrecht University, Princetonplein 5, 3584 CC, Utrecht, The Netherlands
-}
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
-
-\begin{abstract}
-An optical method for the quantitative measurement of the total density field of two-dimensional stratified or homogeneous transparent fluids is presented.
-It is based on the Synthetic Schlieren method.
-Application of this method is illustrated by the determination of the static background density of a two-layer fluid and of a stratified fluid.
-Further aspects of the technique are illustrated by considering the dynamic total density field of a wave attractor in a stratified fluid.
-\keywords{First keyword \and Second keyword \and More}
-% \PACS{PACS code1 \and PACS code2 \and more}
-% \subclass{MSC code1 \and MSC code2 \and more}
-\end{abstract}
-
-\section{Introduction}
-\label{intro}
-The Background Oriented Schlieren technique (BOS) is an optical density visualization technique \cite{meier2002computerized,raffel2015background}.
-First described in \cite{dalziel2000whole}, where it was called Synthetic Schlieren (SS).
-This technique provides whole-field measurements of density gradients.
-One of the strengths of this technique was the simplicity of the experimental setup.
-Parts of the traditional, more extensive optical setups were replaced by digital image analysis.
-
-In a typical BOS or SS application, perturbations (waves) in a fluid contained in a tank are imaged.
-Two or more images are compared using Digital Image Correlation (DIC) \cite{sutton2009image}.
-This comparison yields the displacements between the images.
-These displacements are related to the changes in the gradients of the index of refraction using a ray tracing model.
-These gradients of the index of refraction are related to the gradients of the density by experimentally determined data (e.g.
-\cite{tan2015dependence}), by the Gladstone-Dale relation for gases \cite{born2013principles} or by the Lorentz-Lorenz equation for liquids \cite{lorentz1916theory}.
-The density field is sometimes obtained from the gradients of the density perturbations by solving a Poisson equation \cite{venkatakrishnan2004density, verso2015background}.
-
-In this paper we present a modification to the BOS or SS technique to directly measure the density field.
-We take images of static situations:  (1) before filling a tank in the experimental setup with (stratified) fluids, (2) after filling the tank with a calibration fluid and (3) after filling the tank with (stratified) fluids.
-Then we take images of the dynamic situations: we image, as in BOS or SS, the perturbations, or waves, traveling through a fluid.
-We perform DIC to obtain displacements between the static images.
-Using a ray tracing model we relate these displacements to the index of refraction.
-These static images give us the background index of refraction.
-We follow the same procedure for the dynamic images.
-
-The challenge of this new method is to have enough accuracy in our measurements and models to ensure that our results are useful.
-Determining the value of the density is more sensitive to noise than determining the density gradients of perturbations in a BOS or SS application.
-We also want to preserve the experimental simplicity of the BOS or SS method.
-In Section \ref{sec:simmod} we perform a naive application of the BOS or SS technique to try to measure the index of refraction of homogeneous water.
-We analyze a simple ray tracing model to determine why our naive approach failed.
-We show that light rays, traveling from the background through the fluid to the camera, should not travel in nearly straight lines (as in BOS or SS) but should have large deflections.
-We should either rotate the fluid tank or rotate (and move) our camera.
-We should not be placing our camera right in front of the fluid tank.
-
-To obtain the required accuracy in determining the density field we optimize all the steps in our method.
-In Section \ref{sec:formod} we derive our ray tracing model relating displacements to the index of refraction.
-We call this our forward model: given an index of refraction field and experimental parameters, we can compute the displacement field of our experimental setup.
-This ray tracing model is a 3D model that allows the camera to be placed under an angle with respect to the fluid tank.
-In Section \ref{sec:cal} we describe our calibration procedure.
-This calibration determines accurately certain parameters in our forward model.
-In Section \ref{sec:DIC} we discuss DIC.
-We provide references to papers that discuss techniques that allow us to get the most of our DIC procedure.
-We also provide information about our settings for a typical DIC calculation.
-In Section \ref{sec:exp} we briefly discuss the experimental setup.
-We also discuss best practices to get the most out of our experiments.
-In Section \ref{sec:invmod} we discuss how to solve our inverse model: how to obtain the index of refraction from the experimentally obtained displacements and our forward model.
-
-\section{Simple Model}
-\label{sec:simmod}
-Consider the experimental set up as shown in Figure \ref{fig:schviepalira}.
-Light rays travel from a camera, through a water tank onto a background with a random dot pattern.
-We describe the camera as a pinhole camera.
-We place the origin of the Cartesian coordinate system at the pinhole, the location where all light rays falling on the ccd sensor pass through.
-The $z$-axis is perpendicular to the experimental setup, i.e.
-such that a light ray traveling along the z-axis will not be refracted by the set-up.
-We want to determine the position where the light rays ends up, $x_6$.
-The light ray exits the camera with a position $x_1 = 0$ and an angle $\theta_x$.
-%The $x$-axis points opposite to gravity.
-
-%\begin{figure}[hpbt]
-%	\includestandalone{simplesetup}
-%	\caption{A schematic view of a path of a light ray (not to scale).
-The numbers indicate the planes through which the light ray propagates: 1, the camera lens; 2, the start of the first glass plate; 3, the end of the first glass plate; 4, the start of the second glass plate; 5, the end of the second glass plate; 6, the screen from which the light rays originate.
-$n_0$, $n_1$ and $n_2$ are the index of refraction of, respectively, air, material of the tank and the fluid.
-The lengths are: $L_c$, the distance from camera to the first glass plate; $L_g$, the width of the glass plates; $L_t$ the width of the tank; $L_s$, the distance from the second glass plate to the screen.}
-%	\label{fig:schviepalira}
-%\end{figure}
-
-\begin{figure}[hpbt]
-	\includestandalone[width=\textwidth]{schematicsetupangle}
-	\caption{A schematic view of a path of a light ray (not to scale).
-The light ray in the reference state is indicated by a solid line, the light ray after filling the tank with water by a dashed line.
-The numbers indicate the planes through which the light ray propagates: 0, the ccd sensor inside the camera; 1, the camera pinhole; 2, the start of the first glass plate; 3, the end of the first glass plate; 4, the start of the second glass plate; 5, the end of the second glass plate; 6, the screen from which the light rays originate.
-$n_0$, $n_1$ and $n_2$ are the index of refraction of, respectively, air, material of the tank and the fluid.
-The lengths (in the $z$-direction) are: $L_c$, the distance from camera to the first glass plate; $L_g$, the width of the glass plates; $L_t$ the width of the tank; $L_s$, the distance from the second glass plate to the screen.}
-\label{fig:schviepalira}	
-\end{figure}
-
-Assuming the refractive index in each section of the set up is constant, we can write for the light path,
-\begin{equation}
-	\label{eq:simpleline}
-x(z) = x_i + z \tan \theta_i, \qquad i = 1, ... , 5,
-\end{equation}
-where $x_i$ is the $x$-position of the light ray at the start of each section and $\theta_i$ is the angle between the direction the ray is propagating and the $z$-axis.
-When encountering a discontinuous change in refractive index (when passing between the sections), we invoke Snell's laws
-\begin{equation}
-	\label{eq:snellslaw}
-n_i \sin \theta_i = \mbox{ constant},
-\end{equation}
-where $n_i$ is the refractive index for the $i^{th}$ section. The position $x_6$ is
-%\begin{align}
-%\label{eq:simplex6}
-%x_6 (\theta_x, n_2) & =  (L_c+L_s) \tan \theta_x + 2 L_g \tan \arcsin \frac{n_0}{n_1} \sin \theta_x + L_t \tan \arcsin \frac{n_0}{n_2} \sin \theta_x \nonumber \\
-%& =  (L_c+L_s) \tan \theta_x + \frac{2 L_g n_0 \sin \theta_x}{\sqrt{n_1^2 - n_0^2 \sin^2 \theta_x}} + \frac{L_t n_0 \sin \theta_x}{\sqrt{n_2^2 - n_0^2 \sin^2 \theta_x}}.
-%\end{align}
-\begin{equation}
-\label{eq:simplex6}
-x_6 (\theta_x, n_2) =  (L_c+L_s) \tan \theta_x + \frac{2 L_g n_0 \sin \theta_x}{\sqrt{n_1^2 - n_0^2 \sin^2 \theta_x}} + \frac{L_t n_0 \sin \theta_x}{\sqrt{n_2^2 - n_0^2 \sin^2 \theta_x}}.
-\end{equation}
-The displacement $\Delta x$ is the difference in position $x_6$ between the constant reference state, $n_2 = n_0$, and the unknown state $n_2=n$, 
-%\begin{align}
-%\label{eq:dexcon2}
-%\Delta x = x_6 (n_2 = n_0) - x_6 (n_2 = n) & = L_t \left[ \tan \theta_x - \tan \arcsin \frac{n_0}{n} \sin \theta_x\right] \nonumber \\
-%& = L_t \left[ \tan \theta_x - \frac{n_0 \sin \theta_x}{\sqrt{n^2 - n_0^2 \sin^2 \theta_x}} \right] .
-%\end{align}
-\begin{equation}
-\label{eq:dexcon2}
-\Delta x = x_6 (n_2 = n_0) - x_6 (n_2 = n) = L_t \left( \tan \theta_x - \frac{n_0 \sin \theta_x}{\sqrt{n^2 - n_0^2 \sin^2 \theta_x}} \right) .
-\end{equation}
-Inverting this relation we obtain the unknown refractive index $n$ as a function of the displacement
-\begin{equation}
-\label{eq:invdexcon2}
-n =\frac{n_0 \sin(\theta_x)}{\tan(\theta_x)-\frac{\Delta x}{L_t}} \sqrt{1+\left(\tan(\theta_x)-\frac{\Delta x}{L_t}\right)^2}.
-% \frac{n_0 \sin \theta_x}{\sin \arctan \left( \tan \theta_x - \frac{\Delta x}{L_t} \right)} =
-\end{equation}
-The angle $\theta_x$, the displacement $\Delta x$ and unknown index of refraction $n$ are functions of the coordinate $x$. % Equation (\ref{eq:invdexcon2}) holds for each point.
-
-Figure \ref{fig:simmod} shows the results when using (\ref{eq:invdexcon2}) to obtain the index of refraction $n$.
-We have two frontal images of the experimental setup; (1) Figure \ref{fig:air0simplefrontal}, without water, and (2) Figure \ref{fig:fresh0simplefrontal}, with water.
-Applying DIC we obtain; Figure \ref{fig:CCsimplefrontal} the correlation coefficient, a measure of the reliability of the method; Figure \ref{fig:DXsimplefrontal} the horizontal displacements $\Delta x$; and (3) Figure \ref{fig:DYsimplefrontal} the vertical displacements $\Delta y$.
-Where $\Delta x = \Delta y = 0$ is the location of the $z$-axis.
-We calculate the angles $\theta_x$ and $\theta_y$ with respect to this $z$-axis.
-Using (\ref{eq:invdexcon2}) we can compute the index of refraction $n$.
-Figure \ref{fig:nfromdxsimplefrontal} shows $n$ obtained from the horizontal displacements $\Delta x$.
-Figure \ref{fig:nfromdysimplefrontal} shows $n$ obtained from the vertical displacements $\Delta y$.
-In Figure \ref{fig:nfrontal} we combine the horizontal and vertical displacements to obtain $n$.
-
-\begin{figure}[htbp]
-\begin{subfigure}{.45\linewidth}
-		\centering \includegraphics[width = \textwidth,keepaspectratio]{Refsimplefrontal}
-		\subcaption{Reference Image: Filled with air}\label{fig:air0simplefrontal}
-\end{subfigure}%
-\begin{subfigure}{.45\linewidth}
-	\centering \includegraphics[width = \textwidth,keepaspectratio]{deformedsimplefrontal}
-	\subcaption{Deformed Image: Filled with water}\label{fig:fresh0simplefrontal}
-\end{subfigure}\\
-\begin{subfigure}{.45\linewidth}
-	\centering \includegraphics[width = \textwidth]{CCsimplefrontal}
-	\subcaption{Correlation Coefficient from DIC}\label{fig:CCsimplefrontal}
-\end{subfigure}%
-\begin{subfigure}{.45\linewidth}
-	\centering \includegraphics[width = \textwidth,keepaspectratio]{DXsimplefrontal}
-	\subcaption{$\Delta x$ from DIC}\label{fig:DXsimplefrontal}
-\end{subfigure}\\
-	\begin{subfigure}{.45\linewidth}
-	\centering \includegraphics[width = \textwidth,keepaspectratio]{DYsimplefrontal}
-	\subcaption{$\Delta y$ from DIC}\label{fig:DYsimplefrontal}
-\end{subfigure}%
-\begin{subfigure}{.45\linewidth}
-	\centering \includegraphics[width = \textwidth,keepaspectratio]{nfromdxsimplefrontal}
-	\subcaption{$n$ from $\Delta x$}\label{fig:nfromdxsimplefrontal}
-\end{subfigure}\\
-\begin{subfigure}{.45\linewidth}
-	\centering \includegraphics[width = \textwidth,keepaspectratio]{nfromdysimplefrontal}
-	\subcaption{$n$ from $\Delta y$}\label{fig:nfromdysimplefrontal}
-\end{subfigure}%
-\begin{subfigure}{.45\linewidth}
-	\centering \includegraphics[width = \textwidth,keepaspectratio]{nsimplefrontal}
-	\subcaption{$n$ from $\sqrt{\Delta x^2+\Delta y^2}$}\label{fig:nfrontal}
-\end{subfigure}
-\caption{Simple Model Result.
-Applying DIC to the Reference Image in \ref{fig:air0simplefrontal} and the Deformed Image \ref{fig:fresh0simplefrontal} yields the Correlation Coefficient in \ref{fig:CCsimplefrontal}, the horizontal displacements in \ref{fig:DXsimplefrontal} and the vertical displacements in \ref{fig:DYsimplefrontal}.
-Using (\ref{eq:invdexcon2}) the index of refraction $n$ in \ref{fig:nfromdxsimplefrontal}, \ref{fig:nfromdysimplefrontal} and \ref{fig:nfrontal} are obtained.
-When the displacements $\Delta x$ and $\Delta y$ approach zero, large errors in $n$ appear.
-}
-\label{fig:simmod}
-\end{figure}
-
-We see that when the displacements approach zero, we have very large errors in $n$.
-Figure \ref{fig:nfrontal} looks best, but is still unacceptable.
-Around the location of the $z$-axis, where the angles and displacements approach zero, the errors are very large.
-The entire figure should have a constant value of $n = 1.333$.
-This is not the case.
-
-Equations (\ref{eq:dexcon2}) and (\ref{eq:invdexcon2}) reveal a problem when determining $n$: When the angle $\theta_x$ goes to zero, (\ref{eq:dexcon2}) shows $\Delta x$ goes to zero.
-Then the numerator in the fraction in (\ref{eq:invdexcon2}) goes to zero, while the two terms in the denominator both go to zero.
-So we get large errors in the magnitude of $n$ since we are dividing $0/0$ and we get possibly negative values of $n$ since both terms in the denominator can go to zero.
-In any measurement we have noise, resulting in uncertainties in $\Delta x$ and $\theta_x$.
-These uncertainties have a large effect on the value of $n$ since the expected values of $\Delta x$ and $\theta_x$ are small.
-%The Signal-to-Noise Ratio is very bad because our signal is very small.
-
-To solve this, we want $\theta_x$ to not approach zero.
-Then, according to (\ref{eq:dexcon2}), $\Delta x$ does not approach zero and our calculation of $n$ is not plagued by a fraction that approaches $0/0$.
-To achieve this, we place our camera at an angle $\alpha$ with respect to the water tank.
-The angle $\theta_x$ is replaced by $\alpha+\phi_x$, where $\phi_x$ is the angle of the light ray relative to the principal axis of the camera, which is at an angle $\alpha$.
-%For example, we position our camera at an angle of $\alpha=30^\circ$ relative to the tank.
-The camera has a viewing range of $[-4,4]^\circ$.
-Then $\phi_x$ varies from $-4^\circ$ to $4^\circ$.
-
-\begin{figure}[hpbt]
-	\includegraphics[width=\textwidth, keepaspectratio]{dndx.png}
-	\caption{Derivative of $n$ with respect to $\Delta x / L_t$ as a function of $\theta_x$.}	
-	\label{fig:dndx}
-\end{figure}
-
-\begin{figure}[hpbt]
-	\includegraphics[width=\textwidth, keepaspectratio]{dndt.png}
-	\caption{Derivative of $n$ with respect to $\theta_x$ as a function of $\theta_x$.}		
-	\label{fig:dndt}
-\end{figure}
-
-We want $\Delta x$ to vary with $n$ as much as possible.
-So, we want $n$ to vary with $\Delta x$ as little as possible.
-To find the best angle $\theta_x$ to achieve this, we take the derivative of (\ref{eq:invdexcon2}) with respect to $\Delta x/L_t$ \cite{nemoto1992measurement}.
-Figure \ref{fig:dndx} show this derivative: $\partial n/\partial (\Delta x/L_t)$ decreases with increasing $\theta_x$.
-The worst possible angle to measure $\Delta x$ is $0^\circ$.
-
-Since there is also an uncertainty in the angle, we want $n$ to vary with $\theta_x$ as little as possible.
-Figures \ref{fig:dndt} show this derivative.
-The magnitude of this derivative $\left|\partial n/\partial \theta_x\right|$ first decreases with increasing $\theta_x$, reaches a minimum, then increases again.
-The worst possible angles to measure at are $0^\circ$ and $90^\circ$.
-The minimum is reached at $31^\circ$.
-Any angle between $15^\circ$ and $55^\circ$ yields approximately the same sensitivity of $n$.
-
-Viewing at too large an angle (e.g. $70^\circ$) makes it hard to see through the water tank. 
-%As an example, we take an index of refraction $n=1.333$, an index of refraction $n_0 = 1$, a tank width $L_t=0.2[m]$ and an angle $\theta_x=30^\circ$.
-(\ref{eq:dexcon2}) yields a $\Delta x = 0.0345[m]$.
-From Figure (\ref{fig:dndx}), $\partial n/\partial (\Delta x/L_t) = 2.831$  at $\theta_x = 30^\circ$.
-Hence an error of $1[mm]$ in $\Delta x$ causes an error of $0.014$ in $n$.
-From Figure (\ref{fig:dndt}), $\partial n/\partial \theta_x = -1.466$  at $\theta_x = 30^\circ$.
-Hence an error of $0.1^\circ$ in $\theta_x$ causes an error of $-0.15$ in $n$.
-
-%To perform accurate measurements we want to determine $n$ with at least 5 significant digits.
-To achieve this, we place our camera under an angle to minimize the effect of errors in $\Delta x$ and $\theta_x$ on the index of refraction.
-
-Concluding, Figures \ref{fig:dndx} and \ref{fig:dndt} indicate that the worst angles to measure are close to zero. Angles between $15^\circ$ and $55^\circ$ result in small errors in $n$.
-
-\section{Forward Model}
-\label{sec:formod}
-In this section we build a forward model, relating an index of refraction field $n$, position on the ccd-sensor $\underline{x}$ and parameters $\underline{\alpha}$ to the coordinates $\underline{X}$ where the light rays hits the screen.
-We seek a model $\underline{X}(n, \underline{\alpha}, \underline{x})$.
-
-In Subsection \ref{subsec:rayequ} we derive the equations governing 3-dimensional ray optics in an inhomogeneous medium.
-In Subsection \ref{subsec:RayPath} give a mathematical description of all the objects our light rays encounter.
-In Subsection \ref{subsec:dis} we construct the full ray path from the camera through the tank to the screen
-
 \subsection{Ray Equation} 
@@
 We apply a Runge–Kutta fourth-order method to solve this system. %Appendix \ref{app:RKS} gives the details.
-
-\subsection{Mathematical description of Geometrical Objects}
-\label{subsec:RayPath}
-To give our method flexibility and not making assumption on the relative configuration in our experimental setup, we model the light rays as traversing in a three-dimensional space and allow the different elements in the experimental setup to have any alignments.
-
-We place our origin again at the pinhole.
-The $z$-axis aligns with the optical axis of the camera, i.e.
-the viewing direction of the camera.
-All the light entering the camera travels through the pinhole and falls on the ccd-sensor.
-The $x$- and $y$-axes span a plane through the origin parallel to this ccd-sensor.
-
-\subsubsection{Plane Definition}
-The mathematical definition of a plane is
-\begin{equation}
-	\label{def:plane}
-	\underline{\hat{n}} \cdot (\underline{x}-\underline{x}_0) = 0,
-\end{equation}
-where $\underline{\hat{n}} = (a,b,c)$ is the unit normal vector of the plane, $\underline{x}$ a random vector within the plane and $\underline{x}_0=(x_0, y_0, z_0)$ a random point on the plane.
-Expanding (\ref{def:plane}) yields
-%\begin{equation}
-%	a(x-x_0) + b(y-y_0) + c(z-z_0) = 0, 
-%\end{equation}
-%or 
-\begin{equation}
-	\label{eq:planedef2}
-	ax+by+cz + d = 0 \qquad \mbox{ with } \qquad d = - a x_0 - b y_0 - c z_0.
-\end{equation}
-For each of the planes 2 to 6 in Figure \ref{fig:schviepalira}, we can write an equation of the form (\ref{eq:planedef2}).
-We assume all planes are parallel to each other.
-Then the parameters $a$, $b$ and $c$ are the same for each plane; only $d$ changes.
-The distances in the normal direction of each plane are known, e.g.
-$L_s$, $L_g$, etc.
-Given the equation describing plane 6, with $d=d_6$,
-%\begin{equation}
-%\label{eq:planedef6}
-%	a x + b y + c z + d = 0,
-%\end{equation}
-we can compute the equations describing the other planes
-\begin{align}
-a x + b y + c z + d_i = 0, \qquad  
-& d_5 = d + (a+b+c) L_s, \nonumber \\
-& ..., \nonumber \\ 
-& d_2 = d + (a+b+c) (L_s+2L_g+L_t), \nonumber \\
-\label{eq:planedef1}
-& d_1 = d + (a+b+c) (L_s+2L_g+L_t+L_c) = 0 
-\end{align}
-
-\subsubsection{Direction Cosines}
-Each pixel in our image corresponds to a physical location on the ccd-sensor with coordinates $\underline{x} = (x,y, -L_f)$, where $L_f$ is the distance from the ccd-sensor to the pinhole in the $z$-direction.
-We calculate this distance with the thin lens equation
-\begin{equation}
- \frac{1}{L_f} + \frac{1}{L_m} = \frac{1}{f},
-\end{equation}
-where $f$ is the focal length of the camera and $L_m$ is the distance from the pinhole to screen (plane 6) along the $z$-axis.
-This distance is found from (\ref{eq:planedef2}) for $x=y=0$.
-Then $d = - c L_m$.
-
-The physical coordinates $x$ and $y$ are obtained from the pixel locations $x_p, y_p$  and the physical size of each pixel on the ccd-sensor.
-Assuming each pixel on the ccd-sensor is square, we call the physical size of each sensor $S_p^2$.
-$S_p$ has units $\mu m/pixel$.
-The physical coordinates are then found from the pixel locations by
-\begin{equation}
-	x = S_p (x_p-x_p^0), \qquad  y = S_p (y_p-y_p^0),
-\end{equation}
-where $x_p^0$ and $y_p^0$ are the pixel locations at $(x,y)=(0,0)$.
-
-Each light ray travels in a straight line from these coordinates $\underline{x}$, through the pinhole, to the experimental setup.
-We describe each of these light rays with direction cosines: the cosines of the angles between the light ray and the three coordinate axes:
-\begin{align}
-\label{eq:directioncosines}
-	\alpha = \cos \theta_x = \frac{x}{\sqrt{x^2+y^2+L_f^2}} &\qquad
-	\beta = \cos \theta_y = \frac{y}{\sqrt{x^2+y^2+L_f^2}} \\
-	\gamma = \cos \theta_z = &\frac{L_f}{\sqrt{x^2+y^2+L_f^2}} \nonumber
-\end{align}
-At the pinhole, all light rays pass through the origin and have coordinates (0,0,0). Each light ray has direction cosines $(\alpha, \beta, \gamma)$.
-
-\subsubsection{Intersection Light Rays and Planes: Homogeneous medium}
-The equation governing light rays in homogeneous media is
-\begin{equation}
-	\label{eq:linedef}
-   \underline{p} = \underline{s} + \underline{I} l,
-\end{equation}
-where $\underline{s} = (s_x, s_y, s_z)$ is the initial position, $\underline{I} = (\alpha, \beta, \gamma)$ the direction cosines, $p = (p_x, p_y, p_z)$ the final position and $l$ the length traveled along the light ray.
-%This is the extension of (\ref{eq:simpleline}) in three-dimensions.
-
-To intersect with a plane, the final position $\underline{p}$ must lie on that plane. Substituting (\ref{eq:planedef2}) into (\ref{eq:linedef}) and solving for $l$ yields 
-\begin{equation}
-	l = - \frac{d + a s_x + b s_y + c s_z}{a \alpha + b \beta + c \gamma}
-\end{equation}
-Substituting this $l$ into (\ref{eq:linedef}) yields the location where each light rays intersects with the plane.
-
-\subsubsection{Snell's Law}
-To find the angle of incidence, $\theta_I$, between the incoming light ray and the plane, we compute
-\begin{equation}
-	\cos \theta_I = \underline{\hat{n}} \cdot \underline{I}.
-\end{equation}
-We apply Snell's law (\ref{eq:snellslaw}) to find the angle of refraction, $\theta_T$.
-The index of refraction of the medium through which the incoming ray travels is $n_I$, the index of refraction of the medium through wich the outgoing ray travels is $n_T$.
-To find the direction cosines of the outgoing ray, $\underline{T}$, we calculate
-\begin{align}
-	S = \sign \cos \theta_I, &\qquad
-	\sin \theta_T = \frac{n_I}{n_T} \sqrt{1-\cos^2 \theta_I}, \\
-	\cos \theta_T = \sqrt{1-\left(\frac{n_I}{n_T}\right)^2(1-\cos^2 \theta_I)} &\qquad
-	\underline{T} = \frac{n_I}{n_T} \underline{I} + \left(\frac{n_I}{n_T} \cos \theta_I - S \cos\theta_T\right)\underline{\hat{n}},	
-\end{align}
-where $S$, the sign of $\cos\theta_I$ ensures we stay in the right quadrant.
-
-\subsection{Displacements}
-\label{subsec:dis}
-Previous subsections combine to give the forward model: $\underline{X}(n,\underline{\alpha}, \underline{x})$.
-Given an index of refraction field $n$, parameters $\underline{\alpha}$ and coordinates $\underline{x} = (x,y)$, we can calculate the location on the screen where the light rays end up.
-$\underline{\alpha}$ are the parameters that define the planes $a$, $b$, $c$ and the distance to the screen $L_m$.
-We use $L_m$ instead of $d$ since we want our parameters to be (linearly) independent.
-Also, $L_m$ has a clear geometric meaning.
-
-We take our forward model twice, once for a known index of refraction (typically constant) $n_0$ and once for an unknown index of refraction field $n$.
-The light rays originating from the same location on the screen end up on different locations on the ccd sensor:
-\begin{equation}
-\label{eq:ForwardModel}
-	 \underline{X}(n, \underline{\alpha}, \underline{x}+\underline{\Delta x}) - \underline{X}(n_0, \underline{\alpha}, \underline{x}) = 0, \qquad \underline{X} = (X, Y, Z).
-\end{equation}
-This equation holds for each measured displacement $\underline{\Delta x} = (\Delta x, \Delta y)$.
-From (\ref{eq:directioncosines}) we see that light rays with different locations on the ccd-sensor have different angles with which they leave the camera.
-Due to the different index of refraction in the tank, they do end up in the same location on the screen.
-
-\section{Calibration}
-\label{sec:cal}
-In our forward model in Section \ref{subsec:RayPath}, we have used the parameters $\underline{\alpha}$.
-However, when setting up a new experiment, these are not known.
-To obtain these, we perform a calibration step.
-This calibration determines the parameters very precisely and gives us a lot of experimental freedom.
-For example, we do not have to align the camera, or even measure the position of the camera relative to the water tank.
-We use calibration for this.
-
-The calibration consists of performing one extra measurement (two in total): we take a reference image, the tank without water (filled with air) and a deformed image, the tank filled with water with a known index of refraction.
-The easiest is water without any salts.
-Performing DIC yields us the displacements $\underline{\Delta x}$.
-This allows us to determine the parameters $\underline{\alpha}.$
-
-Looking at our Forward Model (\ref{eq:ForwardModel}), we know
-\begin{enumerate}
-	\item $n=n_0$ and $n=n_1$, the index of refraction of the reference image (filled with air) and the deformed image (filled with water); 
-	\item $\underline{x}$, the coordinates on our ccd-sensor; 
-	\item $\underline{\Delta x}$, the measured displacement (after DIC). 
-\end{enumerate}
-The unknowns are the parameters $\underline{\alpha} = (a, b, c, L_m)$.
-Since we have only four parameters to estimate and many measurements (each grid point yields a separate equation), we have an over-determined system.
-We use least-squares to find those $\underline{\alpha}$ that minimize the sum of squares of the residuals.
-The forward model depends nonlinearly on the parameters $\underline{\alpha}$ and the measurements $\underline{\Delta x}$.
-For each measurement $\underline{\Delta x}$ we have a measure of reliability, the correlation coefficient, which we use as a weight $w$ in the least squares procedure
-\begin{equation}
-\label{eq:calmin} 
-	 \min_{\underline{\alpha}} \sum_i w_i \left(X_{j}(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i)\right)^2, 
-\end{equation}
-with constraints (1) $L_c > 0$ and (2) $L_m \geq L_c + 2 L_g + L_t + L_s$, the experimental setup is in front of the camera; (3) $c < 0$, the unit normal vector of the planes points in the negative $z$-axis.
-Combining these constraints implies $d>0$.
-The sum is over all measured displacements.We use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal.
-% The weights $w_i$ are $0$ when $CC < 0.8$ and $1$ otherwise.
-
-The distance $L_c$ between the camera and the front of water tank (plane 2) along the $\underline{\hat{n}}$ direction is obtained from the total distance $d$ between the camera and the screen along the $z$-direction and the distances $L_g, L_t$ and $L_s$.
-This ensures internal consistency in our model.
-We obtain $L_c$ from (\ref{eq:planedef1}).
-
-We use the Levenberg-Marquardt(LM) algorithm to solve (\ref{eq:calmin}).
-Generally, (\ref{eq:calmin}) has one minimum that satisfies the constraints.
-When the initial condition satisfies these constraints, the LM algorithm will find this minimum.
-
-%\begin{figure}[htbp]
-%		\centering \includegraphics[width = \textwidth]{leastsquaresab.png}
-%		\caption{$\log_{10}S(a,b)$}\label{fig:Sab}
-%\end{figure}
-%\begin{figure}[htbp]
-%		\centering \includegraphics[width = \textwidth]{leastsquaresac.png}
-%		\caption{$\log_{10}S(a,c)$}\label{fig:Sac}
-%\end{figure}
-%\begin{figure}[htbp]
-%		\centering \includegraphics[width = \textwidth]{leastsquaresad.png}
-%		\caption{$\log_{10}S(a,d)$}\label{fig:SaLm}
-%\end{figure}
-%\begin{figure}[htbp]
-%		\centering \includegraphics[width = \textwidth]{leastsquaresbc.png}
-%		\caption{$\log_{10}S(b,c)$}\label{fig:Sbc}
-%\end{figure}
-%\begin{figure}[htbp]
-%		\centering \includegraphics[width = \textwidth]{leastsquaresbd.png}
-%		\caption{$\log_{10}S(b,d)$}\label{fig:SbLm}
-%\end{figure}
-%\begin{figure}[htbp]
-%		\centering \includegraphics[width = \textwidth]{leastsquarescd.png}
-%		\caption{$\log_{10}S(c,d)$}\label{fig:ScLm}
-%\end{figure}
-
-\section{Digital Image Correlation}
-\label{sec:DIC}
-Digital Image Correlation (DIC) is a well known technique \cite{sutton2009image} to obtain deformation maps from images.
-We use second-order shape functions \cite{lu2000deformation} to handle large nonlinear deformations.
-To attain sub-pixel accuracy we interpolate our images with B-splines \cite{thevenaz2000interpolation, unser1999splines}.
-To obtain the deformations we optimize a Correlation Coefficient, the ZNSSD \cite{sutton2009image}.
-We solve this nonlinear least-squares problem  by (1) providing an initial guess and (2) solving an iterative scheme.
-As an initial guess we perform Template Matching \cite{lewis1995industrial,opencv_library} on a limited set of points to obtain rigid deformations with pixel accuracy.
-After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{pan2012incremental} with a propagation function \cite{zhou2012propagation} to determine the initial guesses.
-As iterative scheme we use the LM algorithm.
-
-\begin{table}[htbp]
-\caption{Digital Image Correlation parameters.}
-\label{tab:esterrmagn}
-\centering
-\begin{tabular}{ll}
-Noise & \\
-Subset Size & \\
-Grid Size 	& 5 \\
-Measurements Points & \\
-Total Number of Images & \\
-Number of Averaged Images & \\
-Displacements & \\
-\qquad Spatial Resolution & x pixels, x mm \\
-\qquad Resolution & 0.0105 pixels (x mm) \\
-Index of Refraction & \\
-\qquad Smoothing Method & \\
-\qquad Resolution & x \\
-\end{tabular}
-\end{table}
-
-Table \ref{tab:esterrmagn} shows the typical DIC parameters used in our experiments. Additionally, the accuracy of the obtained displacements is given.
-
-\section{Experimental}
-\label{sec:exp}
-Best practices to get good quality images \cite{sutton2009image}
-
-random dot pattern -> grey -> histogram no over/under saturation
-
-\section{Inverse Model}
-\label{sec:invmod}
-Looking at our Forward Model (\ref{eq:ForwardModel}), we know
-\begin{enumerate}
-	\item $\underline{\alpha}$, the parameters of our experimental setup (after calibration), 
-	\item $\underline{x}$, the coordinates on our ccd-sensor, 
-	\item $\underline{\Delta x}$, the measured displacement (after DIC), 
-	\item $n_0$, the index of refraction of the reference state.
-\end{enumerate}
-The unknown is the index of refraction field $n$.
-Unlike the simple model (\ref{eq:invdexcon2}), we cannot invert the forward model to obtain an expression for the index of refraction $n$.
-We treat the problem of finding $n$ as an optimization problem:
-\begin{equation}
-\label{eq:nmin} 
-	\min_{n_i} (X_{j}(n_i, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i))^2, 
-\end{equation}
-with constraints $1.333 \leq n_i \leq 1.4$.
-For each measurement $\underline{\Delta x}_i$ we solve (\ref{eq:nmin}) to find $n_i$.
-We solve (\ref{eq:nmin}) with the LM algorithm.
-(\ref{eq:nmin}) has one minimum in the range $1.333 \leq n_i \leq 1.4$.
-Picking an initial condition in this range ensures LM finds this minimum.
-
-Since we are working with liquids we use the Lorentz-Lorenz equation to relate the index of refraction $n$ to the density $\rho$ \cite{lorentz1916theory, tan2015dependence},
-\begin{equation}
- 	\frac{n^2-1}{n^2+2} \frac{1}{\rho} = \mbox{ constant}.
-\end{equation}
-We use our calibration measurement to determine the constant: $\rho=1$ for $n=1.333$.
-\section{Results}
-In this section we show three applications of the new method: (1) A static two-layer fluid with large nonlinear deformations, (2) A static stratified fluid and (3) a dynamic fluid/flow?
-with wave attractor.
-
-In the first application, Figure \ref{fig:0side}, we measured the background density of a two-layer fluid system.
-We filled the bottom half of a tank with Wadden Sea water (with an index of refraction of 1.338)\footnote{Measured by a refractometer: The Atago Urine Specific Gravity Refractometer with a refractive index range of 1.333-1.356 and a resolution of 0.0005.} and the upper half of the tank with tap water (with an index of refraction of 1.333).
-We kept the interface between the two layers sharp by filling the upper half of the tank through a sponge.
-The observed deformations of the dot pattern through this interface are large.
-Through the use of the second-order shape functions in the DIC procedure, we can still determine these deformations.
-Figure \ref{fig:ndeformed0side} shows the index of refraction field $n$.
-The expected theoretical density profile is an error function.
-We see this in Figure \ref{fig:ndeformed0side}.
-
-\begin{figure}[htbp]
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Reference Image: Filled with air}\label{fig:air0side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-	\subcaption{Calibration Image Image: Filled with water with known $n$}\label{fig:fresh0side}
-\end{subfigure}\\
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:twolayer0side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-	\subcaption{Index of Refraction $n$ for Calibration Image}\label{fig:ncalibration0side}
-\end{subfigure}\\
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{$\Delta x$ from DIC}\label{fig:dx0side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{$\Delta y$ from DIC}\label{fig:dy0side}
-\end{subfigure}\\
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Index of Refraction $n$ for Deformed Image}\label{fig:ndeformed0side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Correlation Coefficient from DIC}\label{fig:C0side}
-\end{subfigure} \\
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{$n$ profiles for Calibration and Deformed Images}\label{fig:nprofiles0side}
-\end{subfigure}
-\caption{The procedure for obtaining the index of refraction field $n$.
-We obtain three images: one Reference Image (\ref{fig:air0side}) filled with air, one Calibration Image (\ref{fig:fresh0side}) filled with water without salts and one Deformed Image (\ref{fig:twolayer0side}) filled with water with an unknown $n$-field.
-Applying DIC between the Reference Image and the Correlation image, we find the displacements $D=(\Delta x, \Delta y)$.
-Using these displacements $D$ in (\ref{eq:calmin}), we obtain the parameters $\underline{\alpha}$.
-After calibration, the resulting $n$-field is uniform (\ref{fig:ncalibration0side}).
-Applying DIC between the Reference Image and the Deformed Image, we find the displacements $\Delta x$ (\ref{fig:dx0side}) and $\Delta y$ (\ref{fig:dy0side}) with corresponding Correlation Coefficient (\ref{fig:C0side}).
-Using these displacements in (\ref{eq:nmin}), we obtain the unknown index of refraction field $n$ (\ref{fig:ndeformed0side}).
-Horizontally averaging the index of refraction fields $n$ yields the profiles in \ref{fig:nprofiles0side}.}
-\label{fig:0side}
-\end{figure}
-
-\begin{table}[htbp]
-\caption{Angles $\beta$ of internal wave beams as a function of the forcing frequency $\omega$. These were determined by a Synthetic Schlieren setup.}
-\label{tab:SSintwav}
-\centering
-\begin{tabular}{llllll}
-$\omega$ & 1 & 1 & 1 & 1 & 1  \\
-$\beta$  & 1 & 1 & 1 & 1 & 1
-\end{tabular}
-\end{table}
-
-In the second application, Figure \ref{fig:0side}, we measured the background density of a continuously stratified fluid.
-We filled a tank through the double bucket method.
-After taking a Reference Image, a Calibration Image and a Deformed Image, we repositioned the camera for a Synthetic Schlieren measurement.
-After oscillating the tank, we measured the angles of the internal waves propagating in the fluid.
-Table \ref{tab:SSintwav} shows the forcing frequencies $\omega$ and angles $\beta$.
-Through
-\begin{equation}
-	N = \omega \cos \beta
-\end{equation}
-we determined the buoyancy frequency $N$. Through
-\begin{equation}
-	N^2 = - \frac{g}{\rho_0}\frac{d \rho_0}{d z}
-\end{equation}
-we determined the buoyancy frequency $N$, obtained from our new method.
-
-\begin{figure}[htbp]
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:strat0side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Correlation Coefficient from DIC}\label{fig:stratC0side}
-\end{subfigure} \\
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{$\Delta x$ from DIC}\label{fig:stratdx0side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{$\Delta y$ from DIC}\label{fig:stratdy0side}
-\end{subfigure}\\
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Index of Refraction $n$ for Deformed Image}\label{fig:stratndeformed0side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Background Density $\rho_0$ for Deformed Image}\label{fig:stratrho0deformed0side}
-\end{subfigure} 
-\caption{Determining the background density for a continuously stratified fluid.
-After taking three images, with the Deformed Image \ref{fig:strat0side}, we obtain the displacements $\Delta x$ in Figure \ref{fig:stratdx0side} and $\Delta y$ in Figure \ref{fig:stratdy0side} from DIC.
-After calibration we obtain the index of refraction field $n$ in Figure \ref{fig:stratndeformed0side}.
-Using the Lorentz-Lorenz relation we obtain the density profile \ref{fig:stratrho0deformed0side} with buoyancy frequency $N$ of NUMBER.
-}
-\label{figs:strat0side}
-\end{figure}
-
-In the third application, we measured the density field of a wave attractor \cite{maas1997observation}.
-Figure \ref{figs:WA0side} shows the measured density fields over one period of a (1,1) Wave Attractor.
-\begin{figure}[htbp]
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{0}\label{fig:WA0side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{P/6}\label{fig:WA6side}
-\end{subfigure} \\
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{P/3}\label{fig:WA3side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{P/2}\label{fig:WA2side}
-\end{subfigure} \\
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{2P/3}\label{fig:WA23side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{5P/6}\label{fig:WA56side}
-\end{subfigure} 
-\caption{Density Fields over one period of a Wave Attractor. The forcing frequency was NUMBER. }
-\label{figs:WA0side}
-\end{figure}
-
-\section{Discussion}
-
-definition planes -> doesn't have to be parallel. in particular 6th plane can be different, extra parameters to estimate in $\alpha$ (calibration). 
-non plane water tank: measure without tank, with tank with air -> (calibration) shape of tank, field $L_t$
--> doesn't even have to be planes
-
-Same experimental equipment as BOS or SS - Can apply this method. All complexity is in the image analysis.
-
-Need to say something about paraxial approximation
-
-The two novel critical steps are: (1) To view the experimental setup under an angle and (2) To calibrate our model.
-
-Horizontal viewing $\Rightarrow \Delta x, \theta_x$ large. Use $X \Rightarrow \frac{\partial n}{\partial x} = 0$ in static situation.
-\begin{acknowledgements}
-If you'd like to thank anyone, place your comments here
-\end{acknowledgements}
-
-\section*{Funding}
-NWO
-
-\section*{Availability of data and material}
-
-\section*{Code availability}
-
-% Authors must disclose all relationships or interests that 
-% could have direct or potential influence or impart bias on 
-% the work: 
-%
- \section*{Conflict of interest}
- The authors declare that they have no conflict of interest.
-
-\printbibliography[heading=bibintoc]
-% BibTeX users please use one of
-%\bibliographystyle{spbasic}      % basic style, author-year citations
-%\bibliographystyle{spmpsci}      % mathematics and physical sciences
-%\bibliographystyle{spphys}       % APS-like style for physics
-%\bibliography{}   % name your BibTeX data base
-
-% Non-BibTeX users please use
-%\begin{thebibliography}{}
-%
-% and use \bibitem to create references. Consult the Instructions
-% for authors for reference list style.
-%
-%\bibitem{RefJ}
-% Format for Journal Reference
-%Author, Article title, Journal, Volume, page numbers (year)
-% Format for books
-%\bibitem{RefB}
-%Author, Book title, page numbers. Publisher, place (year)
-% etc
-%\end{thebibliography}
-
-\end{document}
-% end of file template.tex

### 2020-02-13 Article/experimentsInFluids.tex
Der Simple n Combined

@@
 %
-\documentclass[draft]{svjour3}                     % onecolumn (standard format)
+\documentclass{svjour3}                     % onecolumn (standard format)
 %\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
@@
              NIOZ Royal Netherlands Institute for Sea Research and Utrecht University, P.O. Box 59, 1790 AB Texel, The Netherlands \\
-             \emph{Present address:} Netherlands Defence Academy, The Netherlands  %  if needed
+             \emph{Present address:} Faculty of Military Sciences, Netherlands Defence Academy, \\
+             P.O. Box 10000, 1780 CA Den Helder, The Netherlands  %  if needed
            \and
@@
 
-\begin{figure}[hpbt]
-	\includegraphics[width=\textwidth, keepaspectratio]{dndx.png}
-	\caption{Derivative of $n$ with respect to $\Delta x / L_t$ as a function of $\theta_x$.}	
-	\label{fig:dndx}
-\end{figure}
+%\begin{figure}[hpbt]
+%	\includegraphics[width=\textwidth, keepaspectratio]{dndx.png}
+%	\caption{Derivative of $n$ with respect to $\Delta x / L_t$ as a function of $\theta_x$.}	
+%	\label{fig:dndx}
+%\end{figure}
+%
+%\begin{figure}[hpbt]
+%	\includegraphics[width=\textwidth, keepaspectratio]{dndt.png}
+%	\caption{Derivative of $n$ with respect to $\theta_x$ as a function of $\theta_x$.}		
+%	\label{fig:dndt}
+%\end{figure}
 
 \begin{figure}[hpbt]
-	\includegraphics[width=\textwidth, keepaspectratio]{dndt.png}
-	\caption{Derivative of $n$ with respect to $\theta_x$ as a function of $\theta_x$.}		
-	\label{fig:dndt}
+	\includegraphics[width=\textwidth, keepaspectratio]{diffnsimple.png}
+	\caption{Derivative of $n$ with respect to $\Delta x / L_t$ and $\theta_x$ as a function of $\theta_x$.}		
+	\label{fig:diffnsimple}
 \end{figure}
@@
 To find the best angle $\theta_x$ to achieve this, we take the derivative of (\ref{eq:invdexcon2}) with respect to $\Delta x/L_t$ \cite{nemoto1992measurement}.
-Figure \ref{fig:dndx} show this derivative: $\partial n/\partial (\Delta x/L_t)$ decreases with increasing $\theta_x$.
+Figure \ref{fig:diffnsimple} shows this derivative: $\partial n/\partial (\Delta x/L_t)$ decreases with increasing $\theta_x$.
 The worst possible angle to measure $\Delta x$ is $0^\circ$.
@@
 Since there is also an uncertainty in the angle, we want $n$ to vary with $\theta_x$ as little as possible.
-Figures \ref{fig:dndt} show this derivative.
+Figure \ref{fig:diffnsimple} also shows this derivative.
 The magnitude of this derivative $\left|\partial n/\partial \theta_x\right|$ first decreases with increasing $\theta_x$, reaches a minimum, then increases again.
@@
 
-Viewing at too large an angle (e.g. $70^\circ$) makes it hard to see through the water tank. 
+%Viewing at too large an angle (e.g. $70^\circ$) makes it hard to see through the water tank. 
 %As an example, we take an index of refraction $n=1.333$, an index of refraction $n_0 = 1$, a tank width $L_t=0.2[m]$ and an angle $\theta_x=30^\circ$.
@@
 
-Concluding, Figures \ref{fig:dndx} and \ref{fig:dndt} indicate that the worst angles to measure are close to zero. Angles between $15^\circ$ and $55^\circ$ result in small errors in $n$.
+%Concluding, Figures \ref{fig:dndx} and \ref{fig:dndt} indicate that the worst angles to measure are close to zero. Angles between $15^\circ$ and $55^\circ$ result in small errors in $n$.
 
@@
 \label{sec:formod}
-In this section we build a forward model, relating an index of refraction field $n$, position on the ccd-sensor $\underline{x}$ and parameters $\underline{\alpha}$ to the coordinates $\underline{X}$ where the light rays hits the screen.
+In this section we build a forward model, relating an index of refraction field $n$, position on the ccd-sensor $\underline{x}$ and parameters $\underline{\alpha}$ to the coordinates $\underline{X} = (X,Y,Z)$ where the light rays hits the screen.
 We seek a model $\underline{X}(n, \underline{\alpha}, \underline{x})$.
-
-In Subsection \ref{subsec:rayequ} we derive the equations governing 3-dimensional ray optics in an inhomogeneous medium.
+To give our method flexibility and not making assumption on the relative configuration in our experimental setup, we model the light rays as traversing in a three-dimensional space and allow the different elements in the experimental setup to have any alignments.
+%In Subsection \ref{subsec:rayequ} we discuss the ray equation used in our model.
 In Subsection \ref{subsec:RayPath} give a mathematical description of all the objects our light rays encounter.
@@
 
-\subsection{Ray Equation} 
-\label{subsec:rayequ}
-In this section we derive equations describing the paths light rays follow in inhomogeneous media. Inhomogeneous media have a index of refraction $n$ that varies with position.
-
-A curved ray path is a space curve, which we can describe by a parametric representation, $\underline{r}(\sigma) = ( x(\sigma), y(\sigma), z(\sigma))$, where $\sigma$ is an arbitrary parameter.
-The two most used parameters are (1) the path length long the ray $s$ and (2) the axial position $z$.
-We denote derivatives with respect to the parameter by dots, so $\dot{\underline{x}}(\sigma) = d\underline{x}(\sigma)/d\sigma$.
-All parameters are functions of $s$.
-
-The optical length $\mathcal{A}$ of a path $\underline{r}(s)$ taken by a ray of light passing from point $A$ to point $B$ in three-dimensional space is defined by
-\begin{equation}
-	\label{eq:defAA}
-	\mathcal{A} = \int_A^B \! n(\underline{r}(s)) \, \mathrm{d}s,
-\end{equation}
-where $n(\underline{r})$ is the index of refraction at the spatial point $\underline{r} \in \mathbb{R}^3$.
-We choose the element of arc length $\mathrm{d}s$ along the ray path $\underline{r}(s)$ through that point as $\mathrm{d}s^2 = \mathrm{d}\underline{r}(s) \cdot \mathrm{d}\underline{r}(s)$, so that $|\dot{\underline{r}}|=1$.
-
-Applying Fermat's principle \cite{holm2011geometric} yields the eikonal equation for ray optics
-\begin{equation}
-	\label{eq:axialrayequation}
-	\frac{\partial n}{\partial \underline{r}} = \frac{d}{ds} \left(n(\underline{r}) \frac{\mathrm{d}\underline{r}}{\mathrm{d} s} \right).
-\end{equation}
-%Another way to write this ray equation is
-%\begin{equation}
-	%\label{eq:axialrayequationvector}
-	%\nabla n = n \ddot{\underline{r}} + (\nabla n \cdot \dot{\underline{r}}) \dot{\underline{r}}
-%\end{equation}
-Only two of the component equations are independent, since $|\dot{\underline{r}}| = 1$.
-
-To find the equations used in Synthetic Schlieren \cite{weyl1954analysis,dalziel2000whole}, we first derive the axial eikonal equation.
-Most optical instruments are designed to posses a line of sight (or primary direction of propagation of light) called the optical axis.
-In Synthetic Schlieren this optical axis coincides with the direction in which the refractive index $n$ does not vary.
-Choosing a Cartesian coordinate system such that the $z$-axis coincides with this optical axis, expresses the arc-length $\mathrm{d}s$ in terms of the increment along the optical axis, $\mathrm{d}z$.
-Our parametric description is now in terms of $z$: $\underline{r}(z) = (x(z), y(z), z)$.
-From our definition of $\mathrm{d}s$
-\begin{equation}
-	\mathrm{d}s(z) = \sqrt{dx^2(z) + dy^2(z) + dz^2} = \sqrt{1+\dot{x}^2 +\dot{y}^2} d z = \frac{1}{\gamma} d z,
-\end{equation}
-where $\dot{x} = d x / dz$ and $\dot{y} = dy/dz$ and 
-\begin{equation}
-	\label{eq:gamma}
-	\gamma = \frac{d z}{d s} = \frac{1}{\sqrt{1+\dot{x}^2+\dot{y}^2}} = \cos \theta\leq 1,
-\end{equation}
-where $\theta$ is the angle the ray makes with the $z$-axis.
-Using (\ref{eq:gamma}) in (\ref{eq:axialrayequation}) yields the axial eikonal equation %The position of a ray at a fixed value of $z$ is denoted by $[x,y]^T$.
-\begin{equation}
-	\gamma \frac{d}{dz} \left(n(\underline{r}(z)) \gamma \frac{d \underline{r}(z)}{d z} \right)  = \frac{\partial n(\underline{r}(z))}{\partial \underline{r}}.
-\end{equation}
-This yields three equations, one for each coordinate direction,
-\begin{equation}
-	\label{eq:axraycoord}
-	\begin{aligned}
-		\ddot{x}  = \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial x} - \dot{x} \frac{\partial n}{\partial z} \right), \quad
-		\ddot{y} = \frac{1}{\gamma^2} \frac{1}{n} \left(\frac{\partial n}{\partial y} - \dot{y} \frac{\partial n}{\partial z} \right), \quad
-		\frac{\partial n}{\partial z} = \gamma \frac{d}{dz}\left(n  \gamma\right).
-	\end{aligned}
-\end{equation}	
-Indeed, this system of equations shows that only two equations are independent.
-In Synthetic Schlieren the variation in $n$ in the $z$-direction, the optical axis, is assumed to be zero.
-Then (\ref{eq:axraycoord}) reduce to
-\begin{equation}
-	\label{eq:SSeq}
-		\ddot{x} = \left(1+\dot{x}^2+\dot{y}^2\right) \frac{1}{n} \frac{\partial n}{\partial x}, \qquad
-		\ddot{y} = \left(1+\dot{x}^2+\dot{y}^2\right) \frac{1}{n} \frac{\partial n}{\partial y},
-\end{equation}
-which are the starting point for the derivation of Synthetic Schlieren in \cite{dalziel2000whole}.
-\footnote{The third equation in (\ref{eq:axraycoord}) reduces to $n \gamma = constant$.
-To integrate (\ref{eq:SSeq}) we do not need to assume $\dot{x}$ and $\dot{y}$ are small.
-Experimentally, this means we can apply Synthetic Schlieren even when the angles of the light rays are large.
-}
-
-In the application presented in this paper, the optical axis does not coincide with the direction in which the refractive index $n$ does not vary.
-Our parametric description is in the arc-length $s$ and not in $z$.
-We cannot solve (\ref{eq:axialrayequation}) analytically, so we solve it numerically.
-We first write our system of three second-order differential equations as a system of 6 first-order differential equations by introducing a quantity $\underline{T}$ \cite{southwell1982ray} such that (\ref{eq:axialrayequation}) becomes
-\begin{equation}
-	\label{eq:sys6foeq}
-		\frac{d \underline{r}}{d s} = \frac{\underline{T}}{n}, \qquad
-		\frac{d \underline{T}}{d s} = \nabla n.
-\end{equation}
-We apply a Runge–Kutta fourth-order method to solve this system. %Appendix \ref{app:RKS} gives the details.
-
-\subsection{Mathematical description of Geometrical Objects}
-\label{subsec:RayPath}
-To give our method flexibility and not making assumption on the relative configuration in our experimental setup, we model the light rays as traversing in a three-dimensional space and allow the different elements in the experimental setup to have any alignments.
+In our experimental setup, static fluids are homogeneous or stratified in the direction of gravity.
+Then $\partial n / \partial x = 0$.
+When we relate the horizontal displacements $\Delta x$ to the refractive index $n$, we assume the light rays travel in straight lines.
+When viewing the experimental setup under an angle, we obtain large horizontal displacements $\Delta x$, while keeping the vertical displacements $\Delta y$ small.
 
@@
 
-\subsubsection{Plane Definition}
+\subsection{Plane Definition}
 The mathematical definition of a plane is
@@
 
-\subsubsection{Direction Cosines}
+\subsection{Direction Cosines}
 Each pixel in our image corresponds to a physical location on the ccd-sensor with coordinates $\underline{x} = (x,y, -L_f)$, where $L_f$ is the distance from the ccd-sensor to the pinhole in the $z$-direction.
@@
 
-\subsubsection{Intersection Light Rays and Planes: Homogeneous medium}
+\subsection{Intersection Light Rays and Planes: Homogeneous medium}
 The equation governing light rays in homogeneous media is
@@
 
-\subsubsection{Snell's Law}
+\subsection{Snell's Law}
 To find the angle of incidence, $\theta_I$, between the incoming light ray and the plane, we compute
@@
 We apply Snell's law (\ref{eq:snellslaw}) to find the angle of refraction, $\theta_T$.
-The index of refraction of the medium through which the incoming ray travels is $n_I$, the index of refraction of the medium through wich the outgoing ray travels is $n_T$.
+The index of refraction of the medium through which the incoming ray travels is $n_I$ and $n_T$ for the outgoing ray.
 To find the direction cosines of the outgoing ray, $\underline{T}$, we calculate
@@
 \end{align}
-where $S$, the sign of $\cos\theta_I$ ensures we stay in the right quadrant.
+where $S$, the sign of $\cos\theta_I$, ensures we stay in the right quadrant.
 
@@
 \label{sec:cal}
-In our forward model in Section \ref{subsec:RayPath}, we have used the parameters $\underline{\alpha}$.
+In our forward model in (\ref{eq:ForwardModel}), we have used the parameters $\underline{\alpha}$.
 However, when setting up a new experiment, these are not known.

### 2020-02-16 calculateN.cpp
Calibration
Removed one calibration parameter.
norm n = 1

@@ -804,76 +804,457 @@ extern PositionDirection calculateIntersectionConstantRefraction(const PositionD
 
 }*/
 /*--------------------------------------------------------------------------*/
-/*namespace {
-      // define y(x) = Poly(a, x) in the empty namespace
-      template <class Type>
-      Type Poly(const std::vector<double> &a, const Type &x)
-      {     size_t k  = a.size();
-            Type y   = 0.;  // initialize summation
-            Type x_i = 1.;  // initialize x^i
-            size_t i;
-            for(i = 0; i < k; i++)
-            {     y   += a[i] * x_i;  // y = y + a_i * x^i
-                  x_i *= x;           // x_i = x_i * x
-            }
-            return y;
-      }
-}*/
-/*--------------------------------------------------------------------------*/
-// main program
-/*extern int poly_test(void)
+extern void CalibrationFigures2(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const cv::Mat &CorrelationCoefficient, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const double &n_0, const double &n_1, const double &n, const std::string &path)
 {
-	std::cout << "test poly " << std::endl;
-	using CppAD::AD;           	 // use AD as abbreviation for CppAD::AD
-      size_t i;                  // a temporary index
+	//double L_c = Lengths[0];
+	double L_g = Lengths[1];
+	double L_t = Lengths[2];
+	double L_s = Lengths[3];
 
-      // vector of polynomial coefficients
-      size_t k = 5;              // number of polynomial coefficients
-      std::vector<double> a(k);       // vector of polynomial coefficients
-      for(i = 0; i < k; i++)
-            a[i] = 1.;           // value of polynomial coefficients
-	std::cout << "test poly 1" << std::endl;
[…]

### 2020-02-16 calculateN.hpp

@@ -47,6 +47,8 @@ extern PositionDirection calculateIntersectionConstantRefraction(const PositionD
 /*--------------------------------------------------------------------------*/
 extern void CalibrationFigures(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const cv::Mat &CorrelationCoefficient, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const double &n_0, const double &n_1, const double &n, const std::string &path);
 /*--------------------------------------------------------------------------*/
+extern void CalibrationFigures2(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const cv::Mat &CorrelationCoefficient, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const double &n_0, const double &n_1, const double &n, const std::string &path);
+/*--------------------------------------------------------------------------*/
 //static std::vector<cv::Mat> ForwardModelConstantn(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const std::vector<double> &PlaneDefinition, const double &n_0, const double &n_1, const double &n);
 /*--------------------------------------------------------------------------*/
 extern std::vector<double> Calibration(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const cv::Mat &CorrelationCoefficient, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const double &n_0, const double &n_1, const double &n, const std::string &path, const double &corr_cut_off);

### 2020-02-17 Article/LaTeX_DL_468198_240419/calibration_parameters.tex
Calibration Updated

\documentclass{standalone}
\usepackage{tikz}
%\usetikzlibrary{patterns}
\usetikzlibrary{calc}
%\usepackage{graphicx}

\tikzset{
    right angle quadrant/.code={
        \pgfmathsetmacro\quadranta{{1,1,-1,-1}[#1-1]}     % Arrays for selecting quadrant
        \pgfmathsetmacro\quadrantb{{1,-1,-1,1}[#1-1]}},
    right angle quadrant=1, % Make sure it is set, even if not called explicitly
    right angle length/.code={\def\rightanglelength{#1}},   % Length of symbol
    right angle length=2ex, % Make sure it is set...
    right angle symbol/.style n args={3}{
        insert path={
            let \p0 = ($(#1)!(#3)!(#2)$) in     % Intersection
                let \p1 = ($(\p0)!\quadranta*\rightanglelength!(#3)$), % Point on base line
                \p2 = ($(\p0)!\quadrantb*\rightanglelength!(#2)$) in % Point on perpendicular line
                let \p3 = ($(\p1)+(\p2)-(\p0)$) in  % Corner point of symbol
            (\p1) -- (\p3) -- (\p2)
        }
    }
}

\begin{document}
\def\s{9}
\def\c{3}
\begin{tikzpicture}[font=\large]
\coordinate (CL) at (0,\c);
\coordinate (CR) at (\c,0);
\coordinate (CC) at (\c/2,\c/2);
\coordinate (P) at (\c,\c);
\coordinate (HL) at (0, \s);
\coordinate (HR) at (15,\s);
\coordinate(HC) at (\s,\s);
\coordinate (N) at (\c,\s);
\coordinate (TLF) at (0.75*\c, 0.5*\c);

\draw(CL)--(CR);
\draw(CC)--(P) node [midway, above left] {$L_f$};
\node[circle,fill,inner sep=1pt, label={below left:$(x_p^0, y_p^0)$}] at (CC) {};
\node[circle,fill,inner sep=1pt, label={right:$P$}] at (P) {};
\draw(P)--(HC) node [midway, above left] {$L_m$};
\draw[thick](HL)--(HR);
\draw[dashed](N)--(P);
\node[label={[align=left]below:$ax+by+cz+d = 0$\\$d = - c L_m$ }] at (HR) {};

\draw[thick,->](N)--(\c,\s-1);
\node[label={right:$\underline{\hat{n}} = (a, b, c)$}] at (\c,\s-0.5) {};

\node[label={right:$\frac{1}{f}= \frac{1}{L_m} + \frac{1}{L_f}$}] at (TLF)  {};

\draw [right angle quadrant=2,right angle symbol={HL}{HR}{P}];
\draw [right angle quadrant=1,right angle symbol={CL}{CR}{P}];
\end{tikzpicture}

\end{document}

### 2020-02-17 Article/experimentsInFluids.tex
Calibration Updated

@@
 
+\usepackage{siunitx}
 %\usepackage{xcolor}
@@
 \usepackage{footnote}
+
 %%%
@@
 \usetikzlibrary{decorations.pathreplacing}
+\usetikzlibrary{calc}
+\tikzset{
+    right angle quadrant/.code={
+        \pgfmathsetmacro\quadranta{{1,1,-1,-1}[#1-1]}     % Arrays for selecting quadrant
+        \pgfmathsetmacro\quadrantb{{1,-1,-1,1}[#1-1]}},
+    right angle quadrant=1, % Make sure it is set, even if not called explicitly
+    right angle length/.code={\def\rightanglelength{#1}},   % Length of symbol
+    right angle length=2ex, % Make sure it is set...
+    right angle symbol/.style n args={3}{
+        insert path={
+            let \p0 = ($(#1)!(#3)!(#2)$) in     % Intersection
+                let \p1 = ($(\p0)!\quadranta*\rightanglelength!(#3)$), % Point on base line
+                \p2 = ($(\p0)!\quadrantb*\rightanglelength!(#2)$) in % Point on perpendicular line
+                let \p3 = ($(\p1)+(\p2)-(\p0)$) in  % Corner point of symbol
+            (\p1) -- (\p3) -- (\p2)
+        }
+    }
+}
 
@@
 
-In a typical BOS or SS application, perturbations (waves) in a fluid contained in a tank are imaged.
+In a typical SS application, perturbations (waves) in a fluid contained in a tank are imaged.
 Two or more images are compared using Digital Image Correlation (DIC) \cite{sutton2009image}.
@@
 We take images of static situations:  (1) before filling a tank in the experimental setup with (stratified) fluids, (2) after filling the tank with a calibration fluid and (3) after filling the tank with (stratified) fluids.
-Then we take images of the dynamic situations: we image, as in BOS or SS, the perturbations, or waves, traveling through a fluid.
-We perform DIC to obtain displacements between the static images.
+Then we take images of the dynamic situations: we image, as in SS, the perturbations, or waves, traveling through a fluid.
+We perform DIC to obtain displacements between the images.
 Using a ray tracing model we relate these displacements to the index of refraction.
-These static images give us the background index of refraction.
-We follow the same procedure for the dynamic images.
+The static images give us the background density.
+The dynamic images give us the dynamic density field.
 
@@
 We also want to preserve the experimental simplicity of the BOS or SS method.
-In Section \ref{sec:simmod} we perform a naive application of the BOS or SS technique to try to measure the index of refraction of homogeneous water.
+In Section \ref{sec:simmod} we perform a naive application of the SS technique to try to measure the index of refraction of homogeneous water.
 We analyze a simple ray tracing model to determine why our naive approach failed.
@@
 We also provide information about our settings for a typical DIC calculation.
-In Section \ref{sec:exp} we briefly discuss the experimental setup.
-We also discuss best practices to get the most out of our experiments.
+We discuss best practices to get the most out of our experiments.
 In Section \ref{sec:invmod} we discuss how to solve our inverse model: how to obtain the index of refraction from the experimentally obtained displacements and our forward model.
+Section \ref{sec:res} shows three applications of our new method.
+In Section \ref{sec:dis} we summarize the main strengths and weaknesses of our method.
 
@@
 Light rays travel from a camera, through a water tank onto a background with a random dot pattern.
-We describe the camera as a pinhole camera.
-We place the origin of the Cartesian coordinate system at the pinhole, the location where all light rays falling on the ccd sensor pass through.
+We describe the camera as a pinhole camera with an image sensor.
+We place the origin of a Cartesian coordinate system at the pinhole, the location where all light rays falling on the image sensor pass through.
 The $z$-axis is perpendicular to the experimental setup, i.e.
 such that a light ray traveling along the z-axis will not be refracted by the set-up.
-We want to determine the position where the light rays ends up, $x_6$.
+We want to determine the position where the light rays end up, $x_6$.
 The light ray exits the camera with a position $x_1 = 0$ and an angle $\theta_x$.
@@
 
-\begin{figure}[hpbt]
+\begin{figure}[htbp]
 	\includestandalone[width=\textwidth]{schematicsetupangle}
@@
 The light ray in the reference state is indicated by a solid line, the light ray after filling the tank with water by a dashed line.
-The numbers indicate the planes through which the light ray propagates: 0, the ccd sensor inside the camera; 1, the camera pinhole; 2, the start of the first glass plate; 3, the end of the first glass plate; 4, the start of the second glass plate; 5, the end of the second glass plate; 6, the screen from which the light rays originate.
+The numbers indicate the planes through which the light ray propagates: 0, the image sensor inside the camera; 1, the camera pinhole; 2, the start of the first glass plate; 3, the end of the first glass plate; 4, the start of the second glass plate; 5, the end of the second glass plate; 6, the screen from which the light rays originate.
 $n_0$, $n_1$ and $n_2$ are the index of refraction of, respectively, air, material of the tank and the fluid.
@@
 where $x_i$ is the $x$-position of the light ray at the start of each section and $\theta_i$ is the angle between the direction the ray is propagating and the $z$-axis.
-When encountering a discontinuous change in refractive index (when passing between the sections), we invoke Snell's laws
+When encountering a discontinuous change in refractive index (when passing between the sections), we invoke Snell's law
 \begin{equation}
@@
 \end{equation}
-The displacement $\Delta x$ is the difference in position $x_6$ between the constant reference state, $n_2 = n_0$, and the unknown state $n_2=n$, 
+In this simple model, the displacement $\Delta x$ is the difference in position $x_6$ between the constant reference state, $n_2 = n_0$, and the unknown state $n_2=n$, 
 %\begin{align}
@@
 \end{equation}
-The angle $\theta_x$, the displacement $\Delta x$ and unknown index of refraction $n$ are functions of the coordinate $x$. % Equation (\ref{eq:invdexcon2}) holds for each point.
+%The angle $\theta_x$, the displacement $\Delta x$ and unknown index of refraction $n$ are functions of the coordinate $x$. % Equation (\ref{eq:invdexcon2}) holds for each point.
 
@@
 Using (\ref{eq:invdexcon2}) we can compute the index of refraction $n$.
-Figure \ref{fig:nfromdxsimplefrontal} shows $n$ obtained from the horizontal displacements $\Delta x$.
-Figure \ref{fig:nfromdysimplefrontal} shows $n$ obtained from the vertical displacements $\Delta y$.
-In Figure \ref{fig:nfrontal} we combine the horizontal and vertical displacements to obtain $n$.
+Figures \ref{fig:nfromdxsimplefrontal}, \ref{fig:nfromdysimplefrontal} and \ref{fig:nfrontal} show $n$ computed from, respectively, the horizontal displacements $\Delta x$, the vertical displacements $\Delta y$ and the combined displacements.
 
@@
 \begin{subfigure}{.45\linewidth}
-	\centering \includegraphics[width = \textwidth]{CCsimplefrontal}
-	\subcaption{Correlation Coefficient from DIC}\label{fig:CCsimplefrontal}
+	\centering \includegraphics[width = \textwidth,keepaspectratio]{CCsimplefrontal}
+	\subcaption{Correlation coefficient from DIC}\label{fig:CCsimplefrontal}
 \end{subfigure}%
@@
 \caption{Simple Model Result.
-Applying DIC to the Reference Image in \ref{fig:air0simplefrontal} and the Deformed Image \ref{fig:fresh0simplefrontal} yields the Correlation Coefficient in \ref{fig:CCsimplefrontal}, the horizontal displacements in \ref{fig:DXsimplefrontal} and the vertical displacements in \ref{fig:DYsimplefrontal}.
+Applying DIC to the Reference Image in \ref{fig:air0simplefrontal} and the Deformed Image \ref{fig:fresh0simplefrontal} yields the correlation coefficient in \ref{fig:CCsimplefrontal}, the horizontal displacements in \ref{fig:DXsimplefrontal} and the vertical displacements in \ref{fig:DYsimplefrontal}.
 Using (\ref{eq:invdexcon2}) the index of refraction $n$ in \ref{fig:nfromdxsimplefrontal}, \ref{fig:nfromdysimplefrontal} and \ref{fig:nfrontal} are obtained.
@@
 \label{fig:simmod}
-\end{figure}
+\end{figure} %Around the location of the $z$-axis, where the angles and displacements approach zero, the errors are large.
+and we get possibly negative values of $n$ since both terms in the denominator can go to zero
 
-We see that when the displacements approach zero, we have very large errors in $n$.
-Figure \ref{fig:nfrontal} looks best, but is still unacceptable.
-Around the location of the $z$-axis, where the angles and displacements approach zero, the errors are very large.
-The entire figure should have a constant value of $n = 1.333$.
+We see that when the displacements approach zero, we have large errors in $n$.
+Figure \ref{fig:nfrontal} looks best, but is still unacceptable.The entire figure should have a constant value of $n = 1.333$.
 This is not the case.
@@
 Then the numerator in the fraction in (\ref{eq:invdexcon2}) goes to zero, while the two terms in the denominator both go to zero.
-So we get large errors in the magnitude of $n$ since we are dividing $0/0$ and we get possibly negative values of $n$ since both terms in the denominator can go to zero.
+So we get large errors in the magnitude of $n$ since we are dividing $0/0$.
 In any measurement we have noise, resulting in uncertainties in $\Delta x$ and $\theta_x$.
@@
 
-We want $\Delta x$ to vary with $n$ as much as possible.
-So, we want $n$ to vary with $\Delta x$ as little as possible.
-To find the best angle $\theta_x$ to achieve this, we take the derivative of (\ref{eq:invdexcon2}) with respect to $\Delta x/L_t$ \cite{nemoto1992measurement}.
-Figure \ref{fig:diffnsimple} shows this derivative: $\partial n/\partial (\Delta x/L_t)$ decreases with increasing $\theta_x$.
-The worst possible angle to measure $\Delta x$ is $0^\circ$.
+We want $\Delta x$ and $\theta_x$ to vary with $n$ as much as possible.
+So, we want $n$ to vary with $\Delta x$ and $\theta_x$ as little as possible.
+To find the best angle $\theta_x$ to achieve this, we take the derivative of (\ref{eq:invdexcon2}) with respect to $\Delta x/L_t$ and $\theta_x$ \cite{nemoto1992measurement}.
+Figure \ref{fig:diffnsimple} shows these derivatives: $\partial n/\partial (\Delta x/L_t)$ decreases with increasing $\theta_x$.
+$\left|\partial n/\partial \theta_x\right|$ first decreases with increasing $\theta_x$, reaches a minimum, then increases again.
+The worst possible angle to measure is $0^\circ$.
 
-Since there is also an uncertainty in the angle, we want $n$ to vary with $\theta_x$ as little as possible.
+%Since there is also an uncertainty in the angle, we want $n$ to vary with $\theta_x$ as little as possible.
 Figure \ref{fig:diffnsimple} also shows this derivative.
@@
 \label{sec:formod}
-In this section we build a forward model, relating an index of refraction field $n$, position on the ccd-sensor $\underline{x}$ and parameters $\underline{\alpha}$ to the coordinates $\underline{X} = (X,Y,Z)$ where the light rays hits the screen.
+In this section we build a forward model, relating an index of refraction field $n$, position on the image sensor $\underline{x}$ and parameters $\underline{\alpha}$ to the coordinates $\underline{X} = (X,Y,Z)$ where the light rays hits the screen.
 We seek a model $\underline{X}(n, \underline{\alpha}, \underline{x})$.
-To give our method flexibility and not making assumption on the relative configuration in our experimental setup, we model the light rays as traversing in a three-dimensional space and allow the different elements in the experimental setup to have any alignments.
+To give our method flexibility, we model the light rays as traversing in a three-dimensional space and allow the different elements in the experimental setup to have any alignments.
 %In Subsection \ref{subsec:rayequ} we discuss the ray equation used in our model.
@@
 Then $\partial n / \partial x = 0$.
-When we relate the horizontal displacements $\Delta x$ to the refractive index $n$, we assume the light rays travel in straight lines.
-When viewing the experimental setup under an angle, we obtain large horizontal displacements $\Delta x$, while keeping the vertical displacements $\Delta y$ small.
+When viewing the experimental setup under a horizontal angle, we obtain large horizontal displacements $\Delta x$, while keeping the vertical displacements $\Delta y$ small.
+When we relate these horizontal displacements $\Delta x$ to the refractive index $n$, we assume the light rays travel in straight lines.
 
@@
 the viewing direction of the camera.
-All the light entering the camera travels through the pinhole and falls on the ccd-sensor.
-The $x$- and $y$-axes span a plane through the origin parallel to this ccd-sensor.
+All the light entering the camera travels through the pinhole and falls on the image sensor.
+The $x$- and $y$-axes span a plane through the origin parallel to this image sensor.
 
@@
 \label{eq:planedef1}
-& d_1 = d + (a+b+c) (L_s+2L_g+L_t+L_c) = 0 
+& d_1 = d + (a+b+c) (L_s+2L_g+L_t+L_c) = 0.
 \end{align}
@@
 \subsection{Direction Cosines}
-Each pixel in our image corresponds to a physical location on the ccd-sensor with coordinates $\underline{x} = (x,y, -L_f)$, where $L_f$ is the distance from the ccd-sensor to the pinhole in the $z$-direction.
+Each pixel in our image corresponds to a physical location on the image sensor with coordinates $\underline{x} = (x,y, -L_f)$, where $L_f$ is the distance from the image sensor to the pinhole in the $z$-direction.
 We calculate this distance with the thin lens equation
@@
 \end{equation}
-where $f$ is the focal length of the camera and $L_m$ is the distance from the pinhole to screen (plane 6) along the $z$-axis.
+where $f$ is the focal length of the camera and $L_m$ is the distance from the pinhole to the screen (plane 6) along the $z$-axis.
 This distance is found from (\ref{eq:planedef2}) for $x=y=0$.
@@
 
-The physical coordinates $x$ and $y$ are obtained from the pixel locations $x_p, y_p$  and the physical size of each pixel on the ccd-sensor.
-Assuming each pixel on the ccd-sensor is square, we call the physical size of each sensor $S_p^2$.
-$S_p$ has units $\mu m/pixel$.
-The physical coordinates are then found from the pixel locations by
+The physical coordinates $x$ and $y$ are obtained from the pixel locations $x_p, y_p$  and the physical size of each pixel on the image sensor.
+Assuming each pixel on the image sensor is square, we call the physical size of each sensor $S_p^2$.
+$S_p$ has units \si[per-mode=symbol]{\micro\metre\per pixel}.
+The physical coordinates are then found from the pixel locations by %  $\mu m/pixel$
 \begin{equation}
@@
 \label{eq:directioncosines}
-	\alpha = \cos \theta_x = \frac{x}{\sqrt{x^2+y^2+L_f^2}} &\qquad
-	\beta = \cos \theta_y = \frac{y}{\sqrt{x^2+y^2+L_f^2}} \\
+	\alpha = \cos \theta_x = \frac{-x}{\sqrt{x^2+y^2+L_f^2}} &\qquad
+	\beta = \cos \theta_y = \frac{-y}{\sqrt{x^2+y^2+L_f^2}} \\
 	\gamma = \cos \theta_z = &\frac{L_f}{\sqrt{x^2+y^2+L_f^2}} \nonumber
 \end{align}
-At the pinhole, all light rays pass through the origin and have coordinates (0,0,0). Each light ray has direction cosines $(\alpha, \beta, \gamma)$.
+At the pinhole, all light rays pass through the origin and have coordinates (0,0,0). %Each light ray has direction cosines $(\alpha, \beta, \gamma)$.
 
@@
 Given an index of refraction field $n$, parameters $\underline{\alpha}$ and coordinates $\underline{x} = (x,y)$, we can calculate the location on the screen where the light rays end up.
-$\underline{\alpha}$ are the parameters that define the planes $a$, $b$, $c$ and the distance to the screen $L_m$.
-We use $L_m$ instead of $d$ since we want our parameters to be (linearly) independent.
-Also, $L_m$ has a clear geometric meaning.
-
 We take our forward model twice, once for a known index of refraction (typically constant) $n_0$ and once for an unknown index of refraction field $n$.
-The light rays originating from the same location on the screen end up on different locations on the ccd sensor:
+The light rays originating from the same location on the screen end up on different locations on the image sensor, due to the different indices of refraction:
 \begin{equation}
@@
 This equation holds for each measured displacement $\underline{\Delta x} = (\Delta x, \Delta y)$.
-From (\ref{eq:directioncosines}) we see that light rays with different locations on the ccd-sensor have different angles with which they leave the camera.
+%From (\ref{eq:directioncosines}) we see that light rays with different locations on the image sensor have different angles with which they leave the camera.
 Due to the different index of refraction in the tank, they do end up in the same location on the screen.
@@
 In our forward model in (\ref{eq:ForwardModel}), we have used the parameters $\underline{\alpha}$.
-However, when setting up a new experiment, these are not known.
+These are (1) the coefficients that define the plane $a$, $b$, $c$; (2) the distance to the screen $L_m$; and (3)  the pixel locations on the image sensor plane, $x_p^0$ and $y_p^0$.
+The straight line, perpendicular from the image sensor plane, from $(x_p^0, y_p^0, -L_f)$ to the origin at the pinhole defines the $z$-axis.
+We assumed a pinhole model for our camera.
+The pixel locations $x_p^0$ and $y_p^0$ determine the location of this pinhole.
+We use $L_m$ instead of $d$ since we want our parameters to be (linearly) independent.
+Also, $L_m$ has a clear geometric meaning.
+The focal length $f$ and sensor size $S_p$ are known quantities for a given camera.
+Figure \ref{fig:calpar} shows the parameters $\alpha$ in our model.
+
+\begin{figure}[hpbt]
+	\includestandalone[width=\textwidth, keepaspectratio]{calibration_parameters}
+	\caption{A schematic view of the parameters $\underline{\alpha}$.
+The location of the pinhole $P$ changes with the pixel locations on the image sensor plane $x_p^0$ and $y_p^0$.
+The orientation of the plane changes with $a$, $b$ and $c$.
+The distance from the pinhole to the plane changes with $L_m$.
+The numbers $0$ and $6$ correspond to the planes in Figure \ref{fig:schviepalira}.}
+\label{fig:calpar}	
+\end{figure}
+
+When setting up a new experiment, the parameters $\underline{\alpha}$ are not known.
 To obtain these, we perform a calibration step.
-This calibration determines the parameters very precisely and gives us a lot of experimental freedom.
+This calibration determines the parameters precisely and gives us a lot of experimental freedom.
 For example, we do not have to align the camera, or even measure the position of the camera relative to the water tank.
-We use calibration for this.
 
@@
 
-Looking at our Forward Model (\ref{eq:ForwardModel}), we know
+\noindent Looking at our forward model (\ref{eq:ForwardModel}), we know
 \begin{enumerate}
 	\item $n=n_0$ and $n=n_1$, the index of refraction of the reference image (filled with air) and the deformed image (filled with water); 
-	\item $\underline{x}$, the coordinates on our ccd-sensor; 
+	\item $\underline{x}$, the coordinates on our image sensor; 
 	\item $\underline{\Delta x}$, the measured displacement (after DIC). 
 \end{enumerate}
-The unknowns are the parameters $\underline{\alpha} = (a, b, c, L_m)$.
-Since we have only four parameters to estimate and many measurements (each grid point yields a separate equation), we have an over-determined system.
+The unknowns are the parameters $\underline{\alpha} = (a, b, c, L_m, x_p^0, y_p^0)$.
+We use the unit normal vector $\underline{\hat{n}}$ in our forward model; the parameters $a$, $b$ and $c$ are normalized.
+When optimizing we only need to know the ratio between these parameters since we normalize afterwards.
+We set $a=1$ and find those $b$ and $c$ that optimize our solution.
+
+Since we have only five parameters to estimate and many measurements (each grid point yields a separate equation), we have an over-determined system.
 We use least-squares to find those $\underline{\alpha}$ that minimize the sum of squares of the residuals.
@@
 \label{eq:calmin} 
-	 \min_{\underline{\alpha}} \sum_i w_i \left(X_{j}(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i)\right)^2, 
+	 \min_{\underline{\alpha}} \sum_i w_i \left(X(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X(n_0, \underline{\alpha}, \underline{x}_i)\right)^2, 
 \end{equation}
@@
 We use the Levenberg-Marquardt(LM) algorithm to solve (\ref{eq:calmin}).
-Generally, (\ref{eq:calmin}) has one minimum that satisfies the constraints.
+In our experiments, (\ref{eq:calmin}) has one minimum that satisfies the constraints.
 When the initial condition satisfies these constraints, the LM algorithm will find this minimum.
@@
 \label{sec:DIC}
-Digital Image Correlation (DIC) is a well known technique \cite{sutton2009image} to obtain deformation maps from images.
+Digital Image Correlation (DIC) is a technique \cite{sutton2009image} to obtain deformation maps from images.
 We use second-order shape functions \cite{lu2000deformation} to handle large nonlinear deformations.
@@
 
-\section{Experimental}
-\label{sec:exp}
-Best practices to get good quality images \cite{sutton2009image}
-
-random dot pattern -> grey -> histogram no over/under saturation
+For practical considerations for DIC we refer to \cite{sutton2009image}, in particular Chapter 10.
+What was most important for our application was ensuring that the histogram of gray values, from a typical measurement, showed no under- or oversaturation and filled the range of gray values.
+The under- or oversaturation was solved by changing the intensity of the (uniform) light source.
+Filling the entire range of gray values was ensured by using a high quality random dot pattern: No sharp edges from black to white, but gradual (gray) changes and having a high enough dot density to ensure a subset has enough information to accurately determine displacements.
+% Image Averaging $>$ Thermal Noise $>$ Static images
 
@@
 \label{sec:invmod}
-Looking at our Forward Model (\ref{eq:ForwardModel}), we know
+Looking at our forward model (\ref{eq:ForwardModel}), we know
 \begin{enumerate}
 	\item $\underline{\alpha}$, the parameters of our experimental setup (after calibration), 
-	\item $\underline{x}$, the coordinates on our ccd-sensor, 
+	\item $\underline{x}$, the coordinates on our image sensor, 
 	\item $\underline{\Delta x}$, the measured displacement (after DIC), 
@@
 The unknown is the index of refraction field $n$.
-Unlike the simple model (\ref{eq:invdexcon2}), we cannot invert the forward model to obtain an expression for the index of refraction $n$.
+Unlike the simple model, we cannot invert the forward model to obtain an expression for the index of refraction $n$.
 We treat the problem of finding $n$ as an optimization problem:
@@
 \label{eq:nmin} 
-	\min_{n_i} (X_{j}(n_i, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_{j}(n_0, \underline{\alpha}, \underline{x}_i))^2, 
+	\min_{n_i} (X(n_i, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X(n_0, \underline{\alpha}, \underline{x}_i))^2, 
 \end{equation}
 with constraints $1.333 \leq n_i \leq 1.4$.
-For each measurement $\underline{\Delta x}_i$ we solve (\ref{eq:nmin}) to find $n_i$.
-We solve (\ref{eq:nmin}) with the LM algorithm.
-(\ref{eq:nmin}) has one minimum in the range $1.333 \leq n_i \leq 1.4$.
+For each measurement $\underline{\Delta x}_i$ we solve (\ref{eq:nmin}) with the LM algorithm to find $n_i$.
+In our experiments, (\ref{eq:nmin}) has one minimum in the range $1.333 \leq n_i \leq 1.4$.
 Picking an initial condition in this range ensures LM finds this minimum.
@@
 We use our calibration measurement to determine the constant: $\rho=1$ for $n=1.333$.
+
 \section{Results}
+\label{sec:res}
 In this section we show three applications of the new method: (1) A static two-layer fluid with large nonlinear deformations, (2) A static stratified fluid and (3) a dynamic fluid/flow?
@@
 \section{Discussion}
+\label{sec:dis}
 

### 2020-02-18 Article/experimentsInFluids.tex
minor text

@@
 When optimizing we only need to know the ratio between these parameters since we normalize afterwards.
-We set $a=1$ and find those $b$ and $c$ that optimize our solution.
+We set $a = - 1$ and find those $b$ and $c$ that optimize our solution.
 
@@
 Combining these constraints implies $d>0$.
-The sum is over all measured displacements.We use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal.
+The sum is over all measured displacements.
+We use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal.
 % The weights $w_i$ are $0$ when $CC < 0.8$ and $1$ otherwise.

### 2020-02-18 DisplayImage.cpp
Scaling

@@ -34,15 +34,16 @@ int main(int argc, char** argv )
 	cv::Mat GridX = load_matrix(inputvariables.path, "GridX", 1);
 	cv::Mat GridY = load_matrix(inputvariables.path, "GridY", 1);
 	cv::Mat CC = load_matrix(inputvariables.path, "CorrelationCoefficient", 1);
-	std::cout << std::endl << "\033[1;32mLoading Matrices Completed\033[0m\n" << std::endl;   
+	std::cout << std::endl << "\033[1;32mLoading Matrices Completed\033[0m\n" << std::endl;
 	/*--------------------------------------------------------------------------*/
 	if (inputvariables.ordering==1)
 	{
 		DX = - DX;
 		DY = - DY;
 	}
-	DX = DX - 0.2;
-	DY = DY + 0.3;
+	/////DX = DX - 0.2;
+	/////DY = DY + 0.3;
+	//DY = DY + 0.6;
 	// Median Filter
 	/*
 	DispX.convertTo(DispX, CV_32F);
@@ -56,7 +57,7 @@ int main(int argc, char** argv )
 	GaussianBlur(DX, DX, Size(5, 5), 0);
 	GaussianBlur(DY, DY, Size(5, 5), 0);
 	// Store Again?
-	std::cout << std::endl << "\033[1;32mFiltering Completed\033[0m\n" << std::endl;  
+	std::cout << std::endl << "\033[1;32mFiltering Completed\033[0m\n" << std::endl;
 	/*--------------------------------------------------------------------------*/
 	auto tr3= std::chrono::high_resolution_clock::now();
 	ExperimentalSetupVariables experimentalsetupvariables;
@@ -87,6 +88,7 @@ int main(int argc, char** argv )
 	CalibrationValues calibrationValues;
 	if (inputvariables.CalibrationNeeded==1)
 	{
+		//std::vector<double> CalibrationNumbers = Calibration3(GridX, GridY, DX, DY, CC, experimentalsetupvariables.focal_length, Lengths, experimentalsetupvariables.Distance_From_Pixels_To_Meters, experimentalsetupvariables.n_0, experimentalsetupvariables.n_1, experimentalsetupvariables.n, inputvariables.path, corr_cut_off);
[…]

### 2020-02-18 calculateN.cpp

@@ -856,10 +856,10 @@ extern void CalibrationFigures2(const cv::Mat &GridX, const cv::Mat &GridY, cons
 
 	double Lc_ini = c/(a+b+c)*Lm-L_s-2.0*L_g-L_t;
 	double Lc = Lc_ini;
-	
+
 	std::vector<double> Lengthsnew(Lengths.begin(), Lengths.end());
 	Lengthsnew[0] = Lc;
-	
+
     std::ofstream myfile;
     myfile.open(path+"/SfilemeanGridXmeanGridY.csv");
     myfile << "meanGridX meanGridY Lm S Lc Ltot a b c"<< std::endl;
@@ -876,7 +876,7 @@ extern void CalibrationFigures2(const cv::Mat &GridX, const cv::Mat &GridY, cons
 	}
 	myfile.close();
 	std::cout << std::endl << "\033[1;32mmeanGridX meanGridY Calibration Complete\033[0m\n" << std::endl;
-	
+
 	meanGridY = meanGridY_ini;
     std::ofstream myfileXLm;
     myfileXLm.open(path+"/SfilemeanGridXLm.csv");
@@ -899,7 +899,7 @@ extern void CalibrationFigures2(const cv::Mat &GridX, const cv::Mat &GridY, cons
 	}
 	myfileXLm.close();
 	std::cout << std::endl << "\033[1;32mmeanGridX Lm Calibration Complete\033[0m\n" << std::endl;
-	
+
 	meanGridX = meanGridX_ini;
     std::ofstream myfileYLm;
     myfileYLm.open(path+"/SfilemeanGridYLm.csv");
@@ -922,7 +922,7 @@ extern void CalibrationFigures2(const cv::Mat &GridX, const cv::Mat &GridY, cons
 	}
 	myfileYLm.close();
 	std::cout << std::endl << "\033[1;32mmeanGridY Lm Calibration Complete\033[0m\n" << std::endl;
-	
+
 	meanGridY = meanGridY_ini;
 	Lm = Lm_ini;
     std::ofstream myfileXa;
@@ -949,7 +949,7 @@ extern void CalibrationFigures2(const cv::Mat &GridX, const cv::Mat &GridY, cons
 	}
 	myfileXa.close();
 	std::cout << std::endl << "\033[1;32mmeanGridX a Calibration Complete\033[0m\n" << std::endl;
-	
+
 	meanGridX = meanGridX_ini;
 	Lm = Lm_ini;
     std::ofstream myfileYa;
[…]

### 2020-02-18 calculateN.hpp

@@ -55,6 +55,8 @@ extern std::vector<double> Calibration(const cv::Mat &GridX, const cv::Mat &Grid
 /*--------------------------------------------------------------------------*/
 extern std::vector<double> Calibration2(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const cv::Mat &CorrelationCoefficient, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const double &n_0, const double &n_1, const double &n, const std::string &path, const double &corr_cut_off);
 /*--------------------------------------------------------------------------*/
+extern std::vector<double> Calibration3(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const cv::Mat &CorrelationCoefficient, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const double &n_0, const double &n_1, const double &n, const std::string &path, const double &corr_cut_off);
+/*--------------------------------------------------------------------------*/
 extern void calculateNFigures(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const cv::Mat &CorrelationCoefficient, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const std::vector<double> &	PlaneDefinition, const double &n_0, const double &n_1, const std::string &path);
 /*--------------------------------------------------------------------------*/
 extern void calculate_Displacements(const cv::Mat &GridX, const cv::Mat &GridY, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const std::vector<double> &PlaneDefinition, const double &n_0, const double &n_1, const double &n);
@@ -62,6 +64,8 @@ extern void calculate_Displacements(const cv::Mat &GridX, const cv::Mat &GridY, 
 extern cv::Mat CalculateN(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const std::vector<double> &PlaneDefinition, const double &n_0, const double &n_1, const std::string &path);
 /*--------------------------------------------------------------------------*/
[…]

### 2020-02-21 Article/experimentsInFluids.tex
Compensation

@@
 
+\section{Correction}
+\label{sec:cor}
+%\subsection{Permanent Compensation}
+Region of Compensation: Sightly similar to \cite{tian2018accuracy} and \cite{pan2013high}
+
 \section{Digital Image Correlation}
@@
 As an initial guess we perform Template Matching \cite{lewis1995industrial,opencv_library} on a limited set of points to obtain rigid deformations with pixel accuracy.
-After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{pan2012incremental} with a propagation function \cite{zhou2012propagation} to determine the initial guesses.
+After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{chen2009quality, pan2012incremental} with a propagation function \cite{zhou2012propagation} to determine the initial guesses.
 As iterative scheme we use the LM algorithm.
@@
 \begin{table}[htbp]
-\caption{Digital Image Correlation parameters.}
+\caption{Digital Image Correlation parameters corresponding to Figure \ref{fig:0side}.}
 \label{tab:esterrmagn}
@@
 \begin{tabular}{ll}
-Noise & \\
-Subset Size & \\
-Grid Size 	& 5 \\
-Measurements Points & \\
-Total Number of Images & \\
-Number of Averaged Images & \\
+Noise & \% \\
+Subset Size & 41 pixels \\
+Grid Size 	& 5 pixels \\
+Measurement Points & $735 \times 415$ pixels \\
+%Total Number of Images & \\
+Number of Averaged Images & 240 \\
 Displacements & \\
@@
 
-Since we are working with liquids we use the Lorentz-Lorenz equation to relate the index of refraction $n$ to the density $\rho$ \cite{lorentz1916theory, tan2015dependence},
-\begin{equation}
- 	\frac{n^2-1}{n^2+2} \frac{1}{\rho} = \mbox{ constant}.
-\end{equation}
-We use our calibration measurement to determine the constant: $\rho=1$ for $n=1.333$.
+We use the experimental data from \cite{tan2015dependence} to relate the measured index of refraction to the density.
 
@@
 \begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
+		\centering \includegraphics[width = \textwidth]{TL_air}
 		\subcaption{Reference Image: Filled with air}\label{fig:air0side}
@@
 \begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-	\subcaption{Calibration Image Image: Filled with water with known $n$}\label{fig:fresh0side}
+		\centering \includegraphics[width = \textwidth]{TL_fresh}
+	\subcaption{Calibration Image: Filled with water with known $n$}\label{fig:fresh0side}
 \end{subfigure}\\
 \begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
+		\centering \includegraphics[width = \textwidth]{TL_TL}
 		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:twolayer0side}
@@
 \begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
+	\centering \includegraphics[width = \textwidth]{Calibrationnsurf}
 	\subcaption{Index of Refraction $n$ for Calibration Image}\label{fig:ncalibration0side}
@@
 \begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
+		\centering \includegraphics[width = \textwidth]{TL_DX}
 		\subcaption{$\Delta x$ from DIC}\label{fig:dx0side}
@@
 \begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
+	\centering \includegraphics[width = \textwidth]{TL_DY}
 		\subcaption{$\Delta y$ from DIC}\label{fig:dy0side}
@@
 \begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
+		\centering \includegraphics[width = \textwidth]{TwoLayernSurf}
 		\subcaption{Index of Refraction $n$ for Deformed Image}\label{fig:ndeformed0side}
@@
 \begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Correlation Coefficient from DIC}\label{fig:C0side}
-\end{subfigure} \\
-\begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
+	\centering \includegraphics[width = \textwidth]{TwoLayerHorizontalAveraged}
 		\subcaption{$n$ profiles for Calibration and Deformed Images}\label{fig:nprofiles0side}
@@
 After calibration, the resulting $n$-field is uniform (\ref{fig:ncalibration0side}).
-Applying DIC between the Reference Image and the Deformed Image, we find the displacements $\Delta x$ (\ref{fig:dx0side}) and $\Delta y$ (\ref{fig:dy0side}) with corresponding Correlation Coefficient (\ref{fig:C0side}).
+Applying DIC between the Reference Image and the Deformed Image, we find the displacements $\Delta x$ (\ref{fig:dx0side}) and $\Delta y$ (\ref{fig:dy0side}).
 Using these displacements in (\ref{eq:nmin}), we obtain the unknown index of refraction field $n$ (\ref{fig:ndeformed0side}).
-Horizontally averaging the index of refraction fields $n$ yields the profiles in \ref{fig:nprofiles0side}.}
+Horizontally averaging the index of refraction field $n$ yields the profiles (\ref{fig:nprofiles0side}).}
 \label{fig:0side}
@@
 \begin{equation}
-	N = \omega \cos \beta
+	\omega = N \cos \beta
 \end{equation}
@@
 \begin{equation}
-	N^2 = - \frac{g}{\rho_0}\frac{d \rho_0}{d z}
+	N^2 = - \frac{g}{\rho^*}\frac{d \rho_0}{d z}
 \end{equation}
 we determined the buoyancy frequency $N$, obtained from our new method.
+From Figure \ref{fig:stratrho0deformed0side} we see that $d \rho_0 / d z =\SI{ - 0.2}{\gram\per\cubic\centi\metre\per\metre}$.
+Taking a mean reference density $\rho^*$ of $\SI{1}{\gram\per\cubic\centi\metre}$, we find a buoyancy frequency of $N = \SI{1.4}{\radian\per\second}$.
 
@@
 \begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
+\centering \includegraphics[width = \textwidth]{TL_strat}
 		\subcaption{Deformed Image: Filled with salt water with unknown $n$-field }\label{fig:strat0side}
@@
 \begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Correlation Coefficient from DIC}\label{fig:stratC0side}
+		\centering \includegraphics[width = \textwidth]{strat_DX}
+		\subcaption{$\Delta x$ from DIC}\label{fig:stratdx0side}
 \end{subfigure} \\
 \begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{$\Delta x$ from DIC}\label{fig:stratdx0side}
+	\centering \includegraphics[width = \textwidth]{strat_DY}
+		\subcaption{$\Delta y$ from DIC}\label{fig:stratdy0side}
 \end{subfigure}%
 \begin{subfigure}{.5\linewidth}
-%	\centering \includegraphics[width = \textwidth]{}
-		\subcaption{$\Delta y$ from DIC}\label{fig:stratdy0side}
-\end{subfigure}\\
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
-		\subcaption{Index of Refraction $n$ for Deformed Image}\label{fig:stratndeformed0side}
-\end{subfigure}%
-\begin{subfigure}{.5\linewidth}
-%		\centering \includegraphics[width = \textwidth]{}
+		\centering \includegraphics[width = \textwidth]{Strat_DensityProfile}
 		\subcaption{Background Density $\rho_0$ for Deformed Image}\label{fig:stratrho0deformed0side}
@@
 After taking three images, with the Deformed Image \ref{fig:strat0side}, we obtain the displacements $\Delta x$ in Figure \ref{fig:stratdx0side} and $\Delta y$ in Figure \ref{fig:stratdy0side} from DIC.
-After calibration we obtain the index of refraction field $n$ in Figure \ref{fig:stratndeformed0side}.
-Using the Lorentz-Lorenz relation we obtain the density profile \ref{fig:stratrho0deformed0side} with buoyancy frequency $N$ of NUMBER.
-}
+After calibration we obtain an index of refraction field $n$ and density field $\rho$.
+Horizontally averaging the density field we obtain the density profile \ref{fig:stratrho0deformed0side} with buoyancy frequency $N = \SI{1.4}{\radian\per\second}$.}
 \label{figs:strat0side}
@@
 
+\clearpage
 \section{Discussion}

### 2020-02-21 DisplayImage.cpp

@@ -44,6 +44,9 @@ int main(int argc, char** argv )
 	/////DX = DX - 0.2;
 	/////DY = DY + 0.3;
 	//DY = DY + 0.6;
+	// TwoLayer - Fresh Correction 2
+	//DX = DX-0.15;
+	//DY = DY+0.3;
 	// Median Filter
 	/*
 	DispX.convertTo(DispX, CV_32F);
@@ -54,8 +57,8 @@ int main(int argc, char** argv )
 	DispY.convertTo(DispY, CV_64F);
 	 * */
 	// Gaussian Filter
-	GaussianBlur(DX, DX, Size(5, 5), 0);
-	GaussianBlur(DY, DY, Size(5, 5), 0);
+	///GaussianBlur(DX, DX, Size(5, 5), 0);
+	///GaussianBlur(DY, DY, Size(5, 5), 0);
 	// Store Again?
 	std::cout << std::endl << "\033[1;32mFiltering Completed\033[0m\n" << std::endl;
 	/*--------------------------------------------------------------------------*/
@@ -70,8 +73,8 @@ int main(int argc, char** argv )
 	// Lengths Small Tank
 	experimentalsetupvariables.L_c = 1e4;
 	experimentalsetupvariables.L_g = 0.8/100;//0.004; //0.01
-	experimentalsetupvariables.L_t = 0.168;//0.191;//15.0/100-2*experimentalsetupvariables.L_g;//13.8/100-2*experimentalsetupvariables.L_g;//0.168;//
-	experimentalsetupvariables.L_s = 0.0;//0.523;
+	experimentalsetupvariables.L_t = 0.191;//15.0/100-2*experimentalsetupvariables.L_g;//13.8/100-2*experimentalsetupvariables.L_g;//0.168;//0.168;//
+	experimentalsetupvariables.L_s = 0.523;0.0;//
 	//experimentalsetupvariables.Lengths{experimentalsetupvariables.L_c, experimentalsetupvariables.L_t, experimentalsetupvariables.L_g, experimentalsetupvariables.L_s};
 	// Lengths Full Tank
 	/*
@@ -88,8 +91,7 @@ int main(int argc, char** argv )
 	CalibrationValues calibrationValues;
 	if (inputvariables.CalibrationNeeded==1)
 	{
[…]

### 2020-02-21 DisplayImage.hpp

@@ -27,6 +27,7 @@
 #include "ExperimentalSetupVariables.hpp"
 #include "CalibrationValues.hpp"
 #include "calculateN.hpp"
+#include "csvload.hpp"
 
 extern "C" {
 #include "coeff.h"
@@ -36,103 +37,6 @@ using namespace cv;
 /*--------------------------------------------------------------------------*/
 static void store_matrix(std::string path, std::string filename, cv::Mat Matrix_To_Be_Stored);
 /*--------------------------------------------------------------------------*/
-static cv::Mat load_matrix(std::string path, std::string filename, const int &skiplines);
-/*--------------------------------------------------------------------------*/
 static bool sort_by_C_value (const Points_With_Value &lhs, const Points_With_Value &rhs);
-/*--------------------------------------------------------------------------*/
-class CSVRow
-{
-    public:
-        std::string const& operator[](std::size_t index) const
-        {
-            return m_data[index];
-        }
-        std::size_t size() const
-        {
-            return m_data.size();
-        }
-        void readNextRow(std::istream& str)
-        {
-            std::string         line;
-            std::getline(str, line);
-
-            std::stringstream   lineStream(line);
-            std::string         cell;
-
-            m_data.clear();
-            while(std::getline(lineStream, cell, ','))
-            {
-                m_data.push_back(cell);
-            }
-            // This checks for a trailing comma with no data after it.
-            if (!lineStream && cell.empty())
-            {
-                // If there was a trailing comma then add an empty element.
-                m_data.push_back("");
-            }
-        }
-    private:
-        std::vector<std::string>    m_data;
-};
-
-std::istream& operator>>(std::istream& str, CSVRow& data)
-{
-    data.readNextRow(str);
-    return str;
-}   
-/*--------------------------------------------------------------------------*/
-class CSVIterator
-{   
-    public:
-        typedef std::input_iterator_tag     iterator_category;
-        typedef CSVRow                      value_type;
-        typedef std::size_t                 difference_type;
-        typedef CSVRow*                     pointer;
-        typedef CSVRow&                     reference;
-
-        CSVIterator(std::istream& str)  :m_str(str.good()?&str:NULL) { ++(*this); }
-        CSVIterator()                   :m_str(NULL) {}
-
-        // Pre Increment
[…]

### 2020-02-21 InputOut.cpp

@@ -109,7 +109,7 @@ extern int readinput(unsigned int argc, char *argv[], InputVariables &inputvaria
 	}
 	inputvariables.yStart = yStart;
 	inputvariables.yEnd = yEnd;
-	
+
     unsigned int offset = 2*((SplineDegree+1)/2) > 5 ? 2*((SplineDegree+1)/2) : 5;
 	//std::cout << " offset = " << offset << std::endl;
     offset = GridLength > (SubsetLength/2+offset) ? GridLength-SubsetLength/2 : offset;
@@ -348,40 +348,65 @@ extern int checkinput(unsigned int argc, char *argv[], std::string &pathname_str
 /*--------------------------------------------------------------------------*/
 extern int readImageDataFromFile(cv::Mat &img, cv::Mat &img1, InputVariables &inputvariables)
 {
+    // First see if a SubFolder 'Averaged' exists
+    // If it does, load the csv files from 'Averaged'
+    // Otherwise, load the tif files from Folder in path
+    std::vector<cv::Mat> data;
+    bool readimagesfromcurrentpath = 0;
+
     std::vector<cv::String> filenames;
-	cv::String path1;
-	path1 = inputvariables.path+"/*.tif";
+    cv::String path1;
+    path1 = inputvariables.path+"/Averaged/*.csv";
     cv::glob(path1,filenames,true); // recurse
-	// Read First Image to Determine Size
-	{
-		cv::Mat im = cv::imread(filenames[0] , IMREAD_GRAYSCALE );
-		if (im.empty())
-		{
-			std::cout << "No Images Found" << std::endl;
-			return -1;
-		}
-		else
-		{
-			if (inputvariables.xEnd > static_cast<unsigned int>(im.cols) || inputvariables.yEnd > static_cast<unsigned int>(im.rows))
-			{
-				std::cout << "Region of Interest (ROI) larger than Image" << std::endl;
-				std::cout << "Image Size = " << im.size() << std::endl;
-				return -1;
-			}
-		}
-	}
-	std::vector<cv::Mat> data;
-	// Read all tif files in folder
-    for (size_t k=0; k<filenames.size(); ++k)
+
+    if (!filenames.empty())
     {
-         cv::Mat im = cv::imread(filenames[k] , IMREAD_GRAYSCALE );
-         if (im.empty()) continue; //only proceed if sucsessful
-		 // Change Here
[…]

### 2020-02-21 InputOut.hpp

@@ -10,6 +10,7 @@
 #include <thread>
 #include <sys/stat.h>
 #include "InputVariables.hpp"
+#include "csvload.hpp"
 
 #include <opencv2/opencv.hpp>
 using namespace cv;

### 2020-02-21 calculateN.cpp

@@ -3521,6 +3521,98 @@ extern cv::Mat CalculateN2(const cv::Mat &GridX, const cv::Mat &GridY, const dou
 
 }
 /*--------------------------------------------------------------------------*/
+extern cv::Mat CalculateN3(const cv::Mat &GridX, const cv::Mat &GridY, const double &meanGridX, const double &meanGridY, const cv::Mat &Dx, const cv::Mat &Dy, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const std::vector<double> &PlaneDefinition, const double &n_0, const double &n_1, const std::string &path, const cv::Mat &ndiff)
+{
+	double abs_tolerance_threshold = 1e-12;
+	double rel_tolerance_threshold = 1e-12;
+	double max_val_nu = 1e7;
+	unsigned int max_iterations = 1e4;
+
+	double n_ini = 1.333;
+	double n_lower_bound = 1.3;
+	double n_upper_bound = 1.4;
+
+	cv::Mat n_field(GridX.size(), CV_64FC1, Scalar(0));
+	double outputcount = 1;
+
+	for( int i = 0; i < GridX.rows; ++i)
+	{
+		for( int j = 0; j < GridX.cols; ++j)
+		{
+			unsigned int iterations = 1;
+			double abs_tolerance = 1;
+			double rel_tolerance = 1;
+			double nu = 2.0;
+			double lambda = 1e-10;
+			cv::Mat GX(1, 1, CV_64F, GridX.at<double>(i,j));
+			cv::Mat GY(1, 1, CV_64F, GridY.at<double>(i,j));
+			cv::Mat dx(1, 1, CV_64F, Dx.at<double>(i,j));
+			cv::Mat dy(1, 1, CV_64F, Dy.at<double>(i,j));
+			cv::Mat W(1, 1, CV_64FC1, Scalar(1));
+			double diffn = -ndiff.at<double>(i,j);
+			double Sold = calculateS2(GX, GY, meanGridX, meanGridY, dx, dy, W, focal_length, Lengths, Distance_From_Pixels_To_Meters, PlaneDefinition, n_0, n_1, n_ini+diffn);
+			double Snew= Sold;
+			double n = n_ini;
+			double nnew = n_ini;
+			cv::Mat Hessian;
+			cv::Mat Jacobian;
[…]

### 2020-02-21 calculateN.hpp

@@ -65,6 +65,8 @@ extern cv::Mat CalculateN(const cv::Mat &GridX, const cv::Mat &GridY, const cv::
 /*--------------------------------------------------------------------------*/
 extern cv::Mat CalculateN2(const cv::Mat &GridX, const cv::Mat &GridY, const double &meanGridX, const double &meanGridY, const cv::Mat &Dx, const cv::Mat &Dy, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const std::vector<double> &PlaneDefinition, const double &n_0, const double &n_1, const std::string &path);
 /*--------------------------------------------------------------------------*/
+extern cv::Mat CalculateN3(const cv::Mat &GridX, const cv::Mat &GridY, const double &meanGridX, const double &meanGridY, const cv::Mat &Dx, const cv::Mat &Dy, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const std::vector<double> &PlaneDefinition, const double &n_0, const double &n_1, const std::string &path, const cv::Mat &ndiff);
+/*--------------------------------------------------------------------------*/
 extern cv::Mat CalculateLsi(const cv::Mat &GridX, const cv::Mat &GridY, const double &meanGridX, const double &meanGridY, const cv::Mat &Dx, const cv::Mat &Dy, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const std::vector<double> &PlaneDefinition, const double &n_0, const double &n_1, const double &n, const std::string &path);
 /*--------------------------------------------------------------------------*/
 extern std::vector<double> CalibrationExtended(const cv::Mat &GridX, const cv::Mat &GridY, const cv::Mat &Dx, const cv::Mat &Dy, const cv::Mat &CorrelationCoefficient, const double &focal_length, const std::vector<double> &Lengths, const double &Distance_From_Pixels_To_Meters, const double &n_0, const double &n_1, const double &n, const std::string &path);

### 2020-02-21 csvload.cpp

@@ -1,0 +1,109 @@
+#include "csvload.hpp"
+/*--------------------------------------------------------------------------*/
+static void removeCharsFromString( std::string &str, char* charsToRemove ) {
+   for ( unsigned int i = 0; i < strlen(charsToRemove); ++i ) {
+      str.erase( remove(str.begin(), str.end(), charsToRemove[i]), str.end() );
+   }
+}
+/*--------------------------------------------------------------------------*/
+class CSVRow
+{
+    public:
+        std::string const& operator[](std::size_t index) const
+        {
+            return m_data[index];
+        }
+        std::size_t size() const
+        {
+            return m_data.size();
+        }
+        void readNextRow(std::istream& str)
+        {
+            std::string         line;
+            std::getline(str, line);
+
+            std::stringstream   lineStream(line);
+            std::string         cell;
+
+            m_data.clear();
+            while(std::getline(lineStream, cell, ','))
+            {
+                m_data.push_back(cell);
+            }
+            // This checks for a trailing comma with no data after it.
+            if (!lineStream && cell.empty())
+            {
+                // If there was a trailing comma then add an empty element.
+                m_data.push_back("");
+            }
+        }
+    private:
+        std::vector<std::string> m_data;
+};
+/*--------------------------------------------------------------------------*/
+std::istream& operator>>(std::istream& str, CSVRow& data)
+{
+    data.readNextRow(str);
+    return str;
+}
+/*--------------------------------------------------------------------------*/
+class CSVIterator
+{
+    public:
+        typedef std::input_iterator_tag     iterator_category;
+        typedef CSVRow                      value_type;
+        typedef std::size_t                 difference_type;
+        typedef CSVRow*                     pointer;
+        typedef CSVRow&                     reference;
+
+        CSVIterator(std::istream& str)  :m_str(str.good()?&str:NULL) { ++(*this); }
+        CSVIterator()                   :m_str(NULL) {}
+
+        // Pre Increment
+        CSVIterator& operator++()               {if (m_str) { if (!((*m_str) >> m_row)){m_str = NULL;}}return *this;}
+        // Post increment
+        CSVIterator operator++(int)             {CSVIterator    tmp(*this);++(*this);return tmp;}
[…]

### 2020-02-21 csvload.hpp

@@ -1,0 +1,7 @@
+#ifndef CSVImage
+#define CSVImage
+#include <opencv2/opencv.hpp>
+/*--------------------------------------------------------------------------*/
+extern cv::Mat load_matrix(std::string path, std::string filename, const int &skiplines);
+/*--------------------------------------------------------------------------*/
+#endif

### 2020-02-24 Article/experimentsInFluids.tex
Comments Leo 1

@@
 \title{Whole-field total density measurements by Digital Image Correlation
-\thanks{Grants or other notes
-about the article that should go on the front page should be
-placed here. }
+%\thanks{Grants or other notes
+%about the article that should go on the front page should be
+%placed here. }
 }
@@
            Leo R.M. Maas \at
-              Imau, Inst. for Marine and Atmospheric research Utrecht, Utrecht University, Princetonplein 5, 3584 CC, Utrecht, The Netherlands
+           Inst. for Marine and Atmospheric research Utrecht, Utrecht University, Princetonplein 5, 3584 CC, Utrecht, The Netherlands
 }
@@
 \cite{tan2015dependence}), by the Gladstone-Dale relation for gases \cite{born2013principles} or by the Lorentz-Lorenz equation for liquids \cite{lorentz1916theory}.
-The density field is sometimes obtained from the gradients of the density perturbations by solving a Poisson equation \cite{venkatakrishnan2004density, verso2015background}.
+The density field is sometimes obtained from the gradients of the density perturbations by solving a Poisson equation \cite{venkatakrishnan2004density, hazewinkel2011comparison,verso2015background}.
 
@@
 We show that light rays, traveling from the background through the fluid to the camera, should not travel in nearly straight lines (as in BOS or SS) but should have large deflections.
-We should either rotate the fluid tank or rotate (and move) our camera.
-We should not be placing our camera right in front of the fluid tank.
+To achieve this, either the fluid tank or the camera can be rotated.
+When placing the camera right in front of the fluid tank the errors due to noise are largest.
 
@@
 We call this our forward model: given an index of refraction field and experimental parameters, we can compute the displacement field of our experimental setup.
-This ray tracing model is a 3D model that allows the camera to be placed under an angle with respect to the fluid tank.
+This ray tracing model is a 3D model that allows the camera to be placed under any angle with respect to the fluid tank.
 In Section \ref{sec:cal} we describe our calibration procedure.
@@
 Applying DIC to the Reference Image in \ref{fig:air0simplefrontal} and the Deformed Image \ref{fig:fresh0simplefrontal} yields the correlation coefficient in \ref{fig:CCsimplefrontal}, the horizontal displacements in \ref{fig:DXsimplefrontal} and the vertical displacements in \ref{fig:DYsimplefrontal}.
-Using (\ref{eq:invdexcon2}) the index of refraction $n$ in \ref{fig:nfromdxsimplefrontal}, \ref{fig:nfromdysimplefrontal} and \ref{fig:nfrontal} are obtained.
+Using (\ref{eq:invdexcon2}) the index of refraction $n$ in \ref{fig:nfromdxsimplefrontal}, \ref{fig:nfromdysimplefrontal} and \ref{fig:nfrontal} is obtained.
 When the displacements $\Delta x$ and $\Delta y$ approach zero, large errors in $n$ appear.
@@
 We see that when the displacements approach zero, we have large errors in $n$.
-Figure \ref{fig:nfrontal} looks best, but is still unacceptable.The entire figure should have a constant value of $n = 1.333$.
+Figure \ref{fig:nfrontal} looks best, but is still unacceptable.
+The entire figure should have a constant value of $n$, the refraction coefficient of pure water $n= 1.333$.
 This is not the case.
 
-Equations (\ref{eq:dexcon2}) and (\ref{eq:invdexcon2}) reveal a problem when determining $n$: When the angle $\theta_x$ goes to zero, (\ref{eq:dexcon2}) shows $\Delta x$ goes to zero.
+Equations (\ref{eq:dexcon2}) and (\ref{eq:invdexcon2}) reveal a problem when determining $n$: When the angle $\theta_x$ goes to zero, (\ref{eq:dexcon2}) shows $\Delta x$ goes to zero too.
 Then the numerator in the fraction in (\ref{eq:invdexcon2}) goes to zero, while the two terms in the denominator both go to zero.
@@
 
-To solve this, we want $\theta_x$ to not approach zero.
+To solve this, we want $\theta_x$ to stay away from zero.
 Then, according to (\ref{eq:dexcon2}), $\Delta x$ does not approach zero and our calculation of $n$ is not plagued by a fraction that approaches $0/0$.
 To achieve this, we place our camera at an angle $\alpha$ with respect to the water tank.
-The angle $\theta_x$ is replaced by $\alpha+\phi_x$, where $\phi_x$ is the angle of the light ray relative to the principal axis of the camera, which is at an angle $\alpha$.
+The angle $\theta_x$ is replaced by $\alpha+\phi_x$, where $\phi_x$ is the angle of the light ray relative to the principal axis of the camera, which is at an angle $\alpha$,  relative to the along-screen x-direction.
 %For example, we position our camera at an angle of $\alpha=30^\circ$ relative to the tank.
@@
 So, we want $n$ to vary with $\Delta x$ and $\theta_x$ as little as possible.
-To find the best angle $\theta_x$ to achieve this, we take the derivative of (\ref{eq:invdexcon2}) with respect to $\Delta x/L_t$ and $\theta_x$ \cite{nemoto1992measurement}.
-Figure \ref{fig:diffnsimple} shows these derivatives: $\partial n/\partial (\Delta x/L_t)$ decreases with increasing $\theta_x$.
+To find the best angle $\theta_x$ to achieve this, we take the derivative of (\ref{eq:invdexcon2}) with respect to $\xi \equiv \Delta x/L_t$ and $\theta_x$ \cite{nemoto1992measurement}.
+Figure \ref{fig:diffnsimple} shows these derivatives: $\partial n/\partial \xi$ decreases with increasing $\theta_x$.
 $\left|\partial n/\partial \theta_x\right|$ first decreases with increasing $\theta_x$, reaches a minimum, then increases again.
-The worst possible angle to measure is $0^\circ$.
+The worst possible angle to measure is $0^\circ$, the classical front view.
 
@@
 \label{sec:formod}
-In this section we build a forward model, relating an index of refraction field $n$, position on the image sensor $\underline{x}$ and parameters $\underline{\alpha}$ to the coordinates $\underline{X} = (X,Y,Z)$ where the light rays hits the screen.
+In this section we build a forward model, relating an index of refraction field $n(\underline{x})$, position on the image sensor $\underline{x}$ and parameters $\underline{\alpha}$ to the coordinates $\underline{X} = (X,Y,Z)$ where the light rays hit the screen.
 We seek a model $\underline{X}(n, \underline{\alpha}, \underline{x})$.
@@
 \end{align}
+Here the equivalence $d_1=0$ in the last equation expresses that the pinhole lies in plane 1.
 
@@
 \end{equation}
-Substituting this $l$ into (\ref{eq:linedef}) yields the location where each light rays intersects with the plane.
+Substituting this $l$ into (\ref{eq:linedef}) yields the location where each light ray intersects with the plane.
 
@@
 The calibration consists of performing one extra measurement (two in total): we take a reference image, the tank without water (filled with air) and a deformed image, the tank filled with water with a known index of refraction.
-The easiest is water without any salts.
+The easiest is water without salt.
 Performing DIC yields us the displacements $\underline{\Delta x}$.
@@
 \label{eq:calmin} 
-	 \min_{\underline{\alpha}} \sum_i w_i \left(X(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X(n_0, \underline{\alpha}, \underline{x}_i)\right)^2, 
+	 \min_{\underline{\alpha}} \sum_i w_i \left(X_j(n_1, \underline{\alpha}, \underline{x}_i+\underline{\Delta x}_i) - X_j(n_0, \underline{\alpha}, \underline{x}_i)\right)^2, \qquad X_j = X \mbox{ or } Y
 \end{equation}
-with constraints (1) $L_c > 0$ and (2) $L_m \geq L_c + 2 L_g + L_t + L_s$, the experimental setup is in front of the camera; (3) $c < 0$, the unit normal vector of the planes points in the negative $z$-axis.
+with constraints (1) $L_c > 0$ and (2) $L_m \geq L_c + 2 L_g + L_t + L_s$, the experimental setup is in front of the camera; (3) $c < 0$, the unit normal vector of the planes points in the negative $z$-direction.
 Combining these constraints implies $d>0$.
 The sum is over all measured displacements.
-We use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal.
+Since plane 6 is a plane, we do not calibrate over one of the directions.
+When only viewing under an horizontal angle, we use only the displacements in the $x$-direction, since that is the direction with the largest angles and thus largest signal.
 % The weights $w_i$ are $0$ when $CC < 0.8$ and $1$ otherwise.
@@
 
-We use the Levenberg-Marquardt(LM) algorithm to solve (\ref{eq:calmin}).
+We use the Levenberg-Marquardt(LM) \cite{fletcher1971modified} algorithm to solve (\ref{eq:calmin}).
 In our experiments, (\ref{eq:calmin}) has one minimum that satisfies the constraints.
@@
 Digital Image Correlation (DIC) is a technique \cite{sutton2009image} to obtain deformation maps from images.
-We use second-order shape functions \cite{lu2000deformation} to handle large nonlinear deformations.
+We use second-order shape functions \cite{lu2000deformation} to handle large nonlinear deformations, especially relevant for sharp interfaces in the fluid.
 To attain sub-pixel accuracy we interpolate our images with B-splines \cite{thevenaz2000interpolation, unser1999splines}.
-To obtain the deformations we optimize a Correlation Coefficient, the ZNSSD \cite{sutton2009image}.
+To obtain the deformations we optimize a Correlation Coefficient, the zero-mean normalized sum of squared differences (ZNSSD) \cite{sutton2009image}.
 We solve this nonlinear least-squares problem by (1) providing an initial guess and (2) solving an iterative scheme.
-As an initial guess we perform Template Matching \cite{lewis1995industrial,opencv_library} on a limited set of points to obtain rigid deformations with pixel accuracy.
+To obtain an initial guess we perform Template Matching (TM) \cite{lewis1995industrial,opencv_library} on a limited set of points.
+In TM a template (a small subset from one image) is compared to a displaced copy in another image.
+TM yields rigid deformations with pixel accuracy.
 After applying DIC to obtain sub-pixel deformations, we use reliability guided DIC \cite{chen2009quality, pan2012incremental} with a propagation function \cite{zhou2012propagation} to determine the initial guesses.
@@
 Figure \ref{fig:ndeformed0side} shows the index of refraction field $n$.
-The expected theoretical density profile is an error function.
+%The expected theoretical density profile is an error function.
 We see this in Figure \ref{fig:ndeformed0side}.
@@
 	\centering \includegraphics[width = \textwidth]{TwoLayerHorizontalAveraged}
-		\subcaption{$n$ profiles for Calibration and Deformed Images}\label{fig:nprofiles0side}
+		\subcaption{$n$ profile for Calibration and Deformed Images}\label{fig:nprofiles0side}
 \end{subfigure}
@@
 We obtain three images: one Reference Image (\ref{fig:air0side}) filled with air, one Calibration Image (\ref{fig:fresh0side}) filled with water without salts and one Deformed Image (\ref{fig:twolayer0side}) filled with water with an unknown $n$-field.
-Applying DIC between the Reference Image and the Correlation image, we find the displacements $D=(\Delta x, \Delta y)$.
+Applying DIC on the area of the red rectangle between the Reference Image and the Correlation image, we find the displacements $D=(\Delta x, \Delta y)$.
 Using these displacements $D$ in (\ref{eq:calmin}), we obtain the parameters $\underline{\alpha}$.
@@
 
-In the second application, Figure \ref{fig:0side}, we measured the background density of a continuously stratified fluid.
-We filled a tank through the double bucket method.
+In the second application, Figure \ref{fig:strat0side}, we measured the background density of a continuously stratified fluid.
+We filled a tank such that the buoyancy frequency was constant .
 After taking a Reference Image, a Calibration Image and a Deformed Image, we repositioned the camera for a Synthetic Schlieren measurement.
@@
 
-In the third application, we measured the density field of a wave attractor \cite{maas1997observation}.
-Figure \ref{figs:WA0side} shows the measured density fields over one period of a (1,1) Wave Attractor.
+In the third application, we measured the spatially and temporally varying density field of a wave attractor \cite{maas1997observation}.
+Figure \ref{figs:WA0side} shows the measured density fields during one period of a (1,1) Wave Attractor.
 \begin{figure}[htbp]
